---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: 'Statistical report - mixed-effects models in adults'
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: 'Open code'
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
fontcolor: "#C4C4C4"
monobackgroundcolor: "#3B3B3B"
bibliography: references.bib
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Analysis

## Import initiation file

```{r}
source('368_initiation.R')
```


## Mixed models


Adults models will be adjusted for the effect of `aAGE`, `SEX`. Relevant supplementation for vitamins and biogenic elements will be added as covariates.

```{r}
AIC_adult <- data.frame(outcome = NA,
                            estimand = NA,
                            aAGE = NA,
                            aSEX = NA,
                            other_cov = NA,
                            diet = NA,
                            family = NA)

diet_adult <- data.frame(outcome = NA,
                         estimand = NA,
                         VN_OM_diff = NA, 
                         VN_OM_P = NA,
                         VG_OM_diff = NA, 
                         VG_OM_P = NA,
                         VN_VG_diff = NA, 
                         VN_VG_P = NA)

i = 1
j = 1
ni= 5
```

### aBMI

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on body mass index, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aWHR

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on waist-to-hip ratio, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aHEIGHT

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on body height, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aMASS

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on body mass, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aHG

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on hand grip, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aPFAT

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on body fat percentage, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aFAT

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(body fat weight), estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aFFM

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on free fat mass, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aSBP

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on systolic blood pressure, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aDBP

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on diastolic blood pressure, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aGLY

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on glucose level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aTC

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(total cholesterole) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aHDL

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on HDL cholesterol level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aLDL

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on LDL cholesterol level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aTG

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(Triglyceride), estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aCa

Data selection

```{r, fig.height=7, fig.width=7}


column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Ca')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum calcium level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Ca'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Ca'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Ca'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Ca'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Ca'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aP

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum phosphorous level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Ca'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aMg

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Mg)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Mg')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum magnesium level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Mg'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Mg'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Mg'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Mg'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Mg'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aSe

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Se')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum selenium level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Se'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Se'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Se'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Se'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Se'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aZn

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Zn')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum log2(zinc) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}



### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Zn'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Zn'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Zn'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Zn'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Zn'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aFE

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum Fe level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Fe'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Fe'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aVKFE

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum log2(ferritin Fe binding capacity), estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Fe'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Fe'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aFERR

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum log2(ferritin) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Fe'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Fe'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aTRF

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum log2(transferin) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Fe'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Fe'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aSATTRF

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on transferin saturation, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Fe'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Fe'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aTRFINDEX

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(sTfR index - ratio), estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Fe'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Fe'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aSTRF

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(soluble transferon receptor), estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Fe'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Fe'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aHGB

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on hemoglobin level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aMCV

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on mean corpuscular volume, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aPTH

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on parathormone level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aCros

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca), 
         !is.na(aSUP_D)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Ca', 'aSUP_D')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(beta-CrossLaps) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Ca', 'aSUP_D'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Ca', 'aSUP_D'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Ca', 'aSUP_D'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Ca', 'aSUP_D'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Ca', 'aSUP_D'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```


### aP1NP

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca), 
         !is.na(aSUP_D)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_Ca', 'aSUP_D')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(procollagen type I) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_Ca', 'aSUP_D'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Ca', 'aSUP_D'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_Ca', 'aSUP_D'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Ca', 'aSUP_D'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_Ca', 'aSUP_D'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aUI

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on urinary iodine level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aUREA

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(urea) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aCREA

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(creatinine) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aUA

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on uric acid level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aVIT_AKTB12

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSup_B12')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(vitamin B12) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSup_B12'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSup_B12'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSup_B12'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSup_B12'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSup_B12'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aHCY

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(homocystain), estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aMMA

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult'),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(methylmalonic acid) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult')

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
  type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
  type = 'adult')

### model without other
mod_other_cov <- NA

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aVIT_D

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_D)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_D')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(vitamin D) level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_D'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_D'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_D'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_D'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_D'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aFOLAT

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_FOL)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = FALSE,
       type = 'adult',
       include = c('aSUP_FOL')),
  
  path = paste0('gitignore/run/mod_adult_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on folat level, estimated with a robust linear mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme( 
  remove_random = FALSE,
  type = 'adult',
  include = c('aSUP_FOL'))

### model  without random effect
mod_nonran <- rlme(
  remove_random = TRUE,
  type = 'adult',
  include = c('aSUP_Fe'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 include = c('aSUP_FOL'),
                 type = 'adult')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_FOL'),
                  type = 'adult')

### model without other
mod_other_cov <- rlme(type = 'adult')

### model without age
mod_age <- rlme(exclude = c('aAGE'),
                include = c('aSUP_FOL'),
                type = 'adult')
```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)

i = i+1
```

### aAL_adult

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_adult)[i+ni]
column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Main model

```{r, fig.height=5, fig.width=5}

mod_main <- glmer(
  outcome ~ 
    SEX + 
    GRP +
    aAGE +
    (1|FAM),
  family = binomial(link = 'logit'),
  data = dat_mod)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on the likelihood of food allergy, estimated with a logistic mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

### model  without random effect
mod_nonran <- glm(
  outcome ~ 
    SEX + 
    GRP +
    aAGE,
  family = binomial(link = 'logit'),
  data = dat_mod)

### model without sex
mod_nsex <- glmer(
  outcome ~ 
    GRP +
    aAGE +
    (1|FAM),
  family = binomial(link = 'logit'),
  data = dat_mod)

### model without diet groups
mod_ndiet <- glmer(
  outcome ~ 
    SEX + 
    aAGE +
    (1|FAM),
  family = binomial(link = 'logit'),
  data = dat_mod)

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_age <- glmer(
  outcome ~ 
    SEX + 
    GRP +
    (1|FAM),
  family = binomial(link = 'logit'),
  data = dat_mod)
```

Putting key results together

```{r}

## AIC

AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)
diet_adult$estimand[i+1] <- 'log(OR)'

i = i+1
```


### aBREAKS

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- 'aBREAKS'
column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Main model

```{r, fig.height=5, fig.width=5}

mod_main <- glmer(
  outcome ~ 
    SEX + 
    GRP +
    aAGE +
    (1|FAM),
  family = binomial(link = 'logit'),
  data = dat_mod)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on the likelihood of having experience of bone break, estimated with a logistic mixed-effects model in adults. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

### model  without random effect
mod_nonran <- glm(
  outcome ~ 
    SEX + 
    GRP +
    aAGE,
  family = binomial(link = 'logit'),
  data = dat_mod)

### model without sex
mod_nsex <- glmer(
  outcome ~ 
    GRP +
    aAGE +
    (1|FAM),
  family = binomial(link = 'logit'),
  data = dat_mod)

### model without diet groups
mod_ndiet <- glmer(
  outcome ~ 
    SEX + 
    aAGE +
    (1|FAM),
  family = binomial(link = 'logit'),
  data = dat_mod)

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_age <- glmer(
  outcome ~ 
    SEX + 
    GRP +
    (1|FAM),
  family = binomial(link = 'logit'),
  data = dat_mod)
```

Putting key results together

```{r}

## AIC

AIC_adult <- add_AIC_adult(AIC_adult, mixef = TRUE)

diet_adult <- add_eff(diet_adult, res, mixef = TRUE)
diet_adult$estimand[i+1] <- 'log(OR)'
```

### Saving tables

```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_adult_mixeff.xlsx') == FALSE){
  diet_adult <- diet_adult[-1,]
  
  diet_adult$VN_OM_P_adj <- NA
  diet_adult$VG_OM_P_adj <- NA
  diet_adult$VN_VG_P_adj <- NA
  
for (i in seq(1, nrow(diet_adult))) {
  padj <- p.adjust(c(
    diet_adult$VN_OM_P[i], 
    diet_adult$VG_OM_P[i],
    diet_adult$VN_VG_P[i]), 
    method = 'hochberg')
  
  diet_adult$VN_OM_P_adj[i] <- padj[1]
  diet_adult$VG_OM_P_adj[i] <- padj[2]
  diet_adult$VN_VG_P_adj[i] <- padj[3]
}
  
  diet_adult <- diet_adult %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) %>% 
    mutate(across(.cols = c(VN_OM_P, VG_OM_P, VN_VG_P,
                            VN_OM_P_adj, VG_OM_P_adj, VN_VG_P_adj), ~ round(.x, 5)))

  write.xlsx(diet_adult, 'gitignore/data/diet_adult_mixeff.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_adult_mixeff.xlsx') == FALSE){
  AIC_adult <- AIC_adult[-1,]
  write.xlsx(AIC_adult, 'gitignore/data/AIC_adult_mixeff.xlsx')
  }
```

# Reproducibility

```{r}
sessionInfo()
```
