---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: "Statistical report - quantile regression summary"
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: "Open code"
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
fontcolor: "#C4C4C4"
monobackgroundcolor: "#3B3B3B"
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

------------------------------------------------------------------------

{{< include README.md >}}

# Import initiation file

```{r}
source('368_initiation.R')
```


# All children

## Diet effects

### Unstandardized effects

```{r}
diet_child_all <- read.xlsx("gitignore/data/diet_child_all.xlsx")%>% 
  mutate(outcome = clean_outcome_names(outcome))  %>%
  mutate(outcome = case_when(
    outcome == 'FOLAT' ~ 'FOLATE',
    outcome == 'VKFE' ~ 'TIBC',
    outcome == 'Cros' ~ 'CTX',
    outcome == 'log2_Cros' ~ 'log2_CTX',
    outcome == 'VIT_AKTB12' ~ 'HOLOTC',
    outcome == 'log2_VIT_AKTB12' ~ 'log2_HOLOTC',
    TRUE ~ outcome
  ))

diet_child_all2 <- diet_child_all %>%   
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))


table1 <- kbl(diet_child_all2, caption = 
      "Table 1. Differences between diet groups across outcomes in all children, based on quantile regression modelling") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 

table1
```

### Standardized effects by 1SD

```{r}
ids <- 11:46
inde <- min(ids)-1
ids <- ids-inde

sds <- vector("double", max(ids))
meds <- diet_child_all %>% filter(estimand == 'median')

for(i in seq_along(ids)){
  sds[i] <- ifelse(grepl("log2",meds[(i),1]),
                   sd(log2(dat_child_all[,(i+inde)]), na.rm=TRUE),
                   sd(dat_child_all[,(i+inde)], na.rm=TRUE))
}

sds <- c(rep(sds, each = 3))

diet_child_all_Z <- diet_child_all %>% 
  mutate(SD = sds) %>% 
  mutate(
    VN_OM_diff = VN_OM_diff/SD,
    VG_OM_diff = VG_OM_diff/SD,
    VN_VG_diff = VN_VG_diff/SD) %>% 
  select(-c(SD)) %>% 
  mutate(across(.cols = c(VG_OM_diff, VN_OM_diff, VN_VG_diff), ~ round(.x, 2)))


table2 <- kbl(diet_child_all_Z, caption = 
      "Table 2. Standardized differences between diet groups across outcomes in all children, based on quantile regression modelling (A) 20th quantile, (B) median and (C) 80th quantile") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 

table2
```

## Vulcano plots

### VN vs OM

```{r}
#| fig.cap: 'Figure 1. Vulcano plot showing standardized differences between VN and OM across clinical outcomes in all children'


color_map <- c('OM+' = '#C97F00', 
               'VN+' = '#137000', 
               'VG+' = '#103CC9',
               'P>0.05' = 'grey50')

plotac <- 'fig1'

path = paste0('gitignore/figures/',plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_all_Z %>% 
           filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VN_OM_P_adj,
             pv_raw = VN_OM_P,
             b_coe = VN_OM_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VN+', 
                 'OM+'))) %>%
           
           mutate(
             rescat = factor(rescat, 
                             levels = c('OM+', 'VN+', 'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>%
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.5, 
             size = 3,
             seed = 17) +
           
           labs(x = 'Standardized difference', y = '-log10 (P-value)') +
           scale_color_manual(values=color_map, name = '') + 
           ggtitle('VN vs. OM, all children') +
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}

```

### VG vs OM
```{r}
#| fig.cap: 'Figure 2. Vulcano plot showing standardized differences between VG and OM across clinical outcomes in all children'


plotac <- 'fig2'

path = paste0('gitignore/figures/',plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_all_Z %>% 
           filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VG_OM_P_adj,
             pv_raw = VG_OM_P,
             b_coe = VG_OM_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VG+', 
                 'OM+'))) %>%
           
           mutate(
             rescat = factor(rescat, 
                             levels = c('OM+', 'VG+', 'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>% 
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha=1, 
             box.padding = 0.5,
             size = 3,
             seed = 17) +
           
           labs(x = 'Standardized difference', y = '-log10 (P-value)') +
           scale_color_manual(values = color_map, name = '') +  
           ggtitle('VG vs. OM, all children') +
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}
 
```

### VN vs VG

```{r}
#| fig.cap: 'Figure 3. Vulcano plot showing standardized differences between VG and VN across clinical outcomes in all children'
plotac <- 'fig3'

path = paste0('gitignore/figures/', plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_all_Z %>% 
             filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VN_VG_P_adj,
             pv_raw = VN_VG_P,
             b_coe = VN_VG_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VN+', 
                 'VG+'))) %>%
           
           
           mutate(
             rescat = factor(rescat, 
                             levels=c('VG+', 
                                      'VN+', 
                                      'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>% 
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.5,
             size = 3,
             seed = 16) +
           
           labs(x = 'Standardized difference', 
                y = '-log10 (P-value)') +
           
           scale_color_manual(values = color_map, name = '') + 
           ggtitle('VN vs VG, all children') +
           
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}

```

## Covariates importance

### Table

```{r}
AIC_child_all <- read.xlsx("gitignore/data/AIC_child_all.xlsx") %>% 
  mutate(across(where(is.numeric), ~round(., 1)))

plotac <- 'table3'

  assign(plotac, kbl(AIC_child_all, caption = 
      "Table 3. Decrease of The Akaike information criterion (AIC) after addition of given outcome to quantile regression model, all children. The change of AIC indicate out-of-sample predictive accuracy of the models and was bounded to -30 (large importance of a covariate, blue) and 0 (no to negliable importance, red).") %>% 
  kable_styling("striped",full_width = T) %>% 
  column_spec(1, width_min = '1.5in'))
  get(plotac)
```

### Heatmap

```{r, fig.height=6, fig.width=8}
#| fig.cap: 'Figure 4. Heatmap showing the extend of decrase of the Akaike information criterion (AIC) after addition of given outcome to quantile regression model, all children. The change of AIC indicate out-of-sample predictive accuracy of the models and was bounded to -30 (large importance of a covariate, blue) and 0 (no to negliable importance, red).'

heat_map(AIC_child_all)
```

# Young children

## Diet effects

### Unstandardized effects

```{r}

diet_child_young <- read.xlsx("gitignore/data/diet_child_young.xlsx") %>% 
  mutate(outcome = clean_outcome_names(outcome)) %>%
  mutate(outcome = case_when(
    outcome == 'FOLAT' ~ 'FOLATE',
    outcome == 'VKFE' ~ 'TIBC',
    outcome == 'Cros' ~ 'CTX',
    outcome == 'log2_Cros' ~ 'log2_CTX',
    outcome == 'VIT_AKTB12' ~ 'HOLOTC',
    outcome == 'log2_VIT_AKTB12' ~ 'log2_HOLOTC',
    TRUE ~ outcome
  ))

diet_child_young2 <- diet_child_young %>%   
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))

kbl(diet_child_young2, caption = 
      "Table 4. Differences between diet groups across outcomes in children < 3 years of age, based on quantile regression modelling") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in')
```

### Standardized effects by 1SD

```{r}

ids <- 11:46
inde <- min(ids)-1
ids <- ids-inde

sds <- vector("double", max(ids))
meds <- diet_child_young %>% filter(estimand=='median')

for(i in seq_along(ids)){
  sds[i] <- ifelse(grepl("log2",meds[(i),1]),
                   sd(log2(dat_child_young[,(i+inde)]), na.rm=TRUE),
                   sd(dat_child_young[,(i+inde)], na.rm=TRUE))
}

sds <- c(rep(sds, each=3))

diet_child_young_Z <- diet_child_young %>% 
  mutate(SD = sds) %>% 
  mutate(VN_OM_diff = VN_OM_diff/SD,
         VG_OM_diff = VG_OM_diff/SD,
         VN_VG_diff = VN_VG_diff/SD) %>% 
  select(-SD) %>% 
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))


kbl(diet_child_young_Z, caption = 
      "Table 5. Standardized differences between diet groups across outcomes in children < 3 years of age, based on quantile regression modelling") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 
```

## Vulcano plots

### VN vs. OM
```{r}
#| fig.cap: 'Figure 5. Vulcano plot showing standardized differences between OM and VG across clinical outcomes in children < 3 years'
cole <- c('grey50', 'red3', 'blue2')


plotac <- 'fig5'

path = paste0('gitignore/figures/',plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_young_Z %>% 
           filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VN_OM_P_adj,
             pv_raw = VN_OM_P,
             b_coe = VN_OM_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VN+', 
                 'OM+'))) %>%
           
           mutate(
             rescat = factor(rescat, 
                             levels = c('OM+', 'VN+', 'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>%
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.5, 
             size = 3,
             seed = 17) +
           
           labs(x = 'Standardized difference', y = '-log10 (P-value)') +
           scale_color_manual(values = color_map, name = '') + 
           ggtitle('VN vs. OM, children < 3 years') +
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}
```

### VG vs OM

```{r}
#| fig.cap: 'Figure 6. Vulcano plot showing standardized differences between OM and VN across clinical outcomes in children < 3 years.'
#| 
plotac <- 'fig6'

path = paste0('gitignore/figures/',plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_young_Z %>% 
           filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VG_OM_P_adj,
             pv_raw = VG_OM_P,
             b_coe = VG_OM_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VG+', 
                 'OM+'))) %>%
           
           mutate(
             rescat = factor(rescat, 
                             levels = c('OM+', 'VG+', 'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>%
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.5, 
             size = 3,
             seed = 17) +
           
           labs(x = 'Standardized difference', y = '-log10 (P-value)') +
           scale_color_manual(values = color_map, name = '') + 
           ggtitle('VG vs. OM, young children') +
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}
```

### VN vs VG

```{r}
#| fig.cap: 'Figure 7. Vulcano plot showing standardized differences between VN and VG across clinical outcomes in children < 3 years.'

plotac <- 'fig7'

path = paste0('gitignore/figures/', plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_young_Z %>% 
             filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VN_VG_P_adj,
             pv_raw = VN_VG_P,
             b_coe = VN_VG_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VN+', 
                 'VG+'))) %>%
           
           
           mutate(
             rescat = factor(rescat, 
                             levels=c('VG+', 
                                      'VN+', 
                                      'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>% 
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.5,
             size = 3,
             seed = 16) +
           
           labs(x = 'Standardized difference', 
                y = '-log10 (P-value)') +
           
           scale_color_manual(values = color_map, name = '') + 
           ggtitle('VN vs VG, children < 0.05') +
           
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}
```

## Covariates importance

### Table

```{r}
AIC_child_young <- read.xlsx("gitignore/data/AIC_child_young.xlsx") %>% 
  mutate(across(where(is.numeric), ~round(., 1)))


plotac <- 'table6'

  assign(plotac,kbl(AIC_child_young, caption = 
      "Table 6. Decrease of The Akaike information criterion (AIC) after addition of given outcome to quantile regression model, children under 3 years. The change of AIC indicate out-of-sample predictive accuracy of the models and was bounded to -30 (large importance of a covariate) and 0 (no to negliable importance)") %>% 
  kable_styling("striped",full_width = T) %>% 
  column_spec(1, width_min = '1.5in'))
  get(plotac)

```

### Heatmap

```{r, fig.height=6, fig.width=8}
#| fig.cap: 'Figure 8. Heatmap showing the extend of decrase of the Akaike information criterion (AIC) after addition of given outcome to quantile regression model, children < 3 years. The change of AIC indicate out-of-sample predictive accuracy of the models and was bounded to -30 (large importance of a covariate, blue) and 0 (no to negliable importance, red).'

heat_map(AIC_child_young)
```

# Old children

## Diet effects 

### Unstandardized effects

```{r}

diet_child_old <- read.xlsx("gitignore/data/diet_child_old.xlsx") %>% 
  mutate(outcome = clean_outcome_names(outcome)) %>%
  mutate(outcome = case_when(
    outcome == 'FOLAT' ~ 'FOLATE',
    outcome == 'VKFE' ~ 'TIBC',
    outcome == 'Cros' ~ 'CTX',
    outcome == 'log2_Cros' ~ 'log2_CTX',
    outcome == 'VIT_AKTB12' ~ 'HOLOTC',
    outcome == 'log2_VIT_AKTB12' ~ 'log2_HOLOTC',
    TRUE ~ outcome
  ))

diet_child_old <- diet_child_old %>%   
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2))) %>% 
  filter(!is.na(VN_OM_diff))

table7 <- kbl(diet_child_old, caption = 
      "Table 7. Differences between diet groups across outcomes in children > 3 years of age, based on quantile regression modelling") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 

table7
```

### Standardized effects by 1SD

```{r}

ids <- 11:46
inde <- min(ids)-1
ids <- ids-inde

sds <- vector("double", max(ids))
meds <- diet_child_old %>% filter(estimand=='median')

for(i in seq_along(ids)){
  sds[i] <- ifelse(grepl("log2",meds[(i),1]),
                   sd(log2(dat_child_old[,(i+inde)]), na.rm=TRUE),
                   sd(dat_child_old[,(i+inde)], na.rm=TRUE))
}

sds <- c(rep(sds, each=3))

diet_child_old_Z <- diet_child_old %>% 
  mutate(SD = sds) %>% 
  mutate(VN_OM_diff = VN_OM_diff/SD,
         VG_OM_diff = VG_OM_diff/SD,
         VN_VG_diff = VN_VG_diff/SD) %>% 
  select(-SD) %>% 
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))

table8 <- kbl(diet_child_old_Z, caption = 
      "Table 8. Standardized differences between diet groups across outcomes in children > 3 years of age, based on quantile regression modelling") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 

table8
```

## Vulcano plot

### VN vs OM

```{r}
#| fig.cap: 'Figure 9. Vulcano plot showing standardized differences between OM and VG across clinical outcomes in children > 3 years.'
cole <- c('grey50', 'red3','blue2')

plotac <- 'fig9'

path = paste0('gitignore/figures/',plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_old_Z %>% 
           filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VN_OM_P_adj,
             pv_raw = VN_OM_P,
             b_coe = VN_OM_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VN+', 
                 'OM+'))) %>%
           
           mutate(
             rescat = factor(rescat, 
                             levels = c('OM+', 'VN+', 'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>%
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.5, 
             size = 3,
             seed = 17) +
           
           labs(x = 'Standardized difference', y = '-log10 (P-value)') +
           scale_color_manual(values = color_map, name = '') + 
           ggtitle('VN vs. OM, children > 3 years') +
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}

```

### VG vs OM

```{r}
#| fig.cap: 'Figure 10. Vulcano plot showing standardized differences between OM and VN across clinical outcomes in children > 3 years.'

plotac <- 'fig10'

path = paste0('gitignore/figures/',plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_old_Z %>% 
           filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VG_OM_P_adj,
             pv_raw = VG_OM_P,
             b_coe = VG_OM_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VG+', 
                 'OM+'))) %>%
           
           mutate(
             rescat = factor(rescat, 
                             levels = c('OM+', 'VG+', 'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>% 
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha=1, 
             box.padding = 0.5,
             size = 3,
             seed = 17) +
           
           labs(x = 'Standardized difference', y = '-log10 (P-value)') +
           scale_color_manual(values = color_map, name = '') +  
           ggtitle('VG vs. OM, children > 3 years') +
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}
```

### VN vs VG

```{r}
#| fig.cap: 'Figure 11. Vulcano plot showing standardized differences between VG and VN across clinical outcomes in children <>3 years.'
cole <- c( 'grey50', 'blue2', 'red3')

plotac <- 'fig11'

path = paste0('gitignore/figures/', plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_child_old_Z %>% 
             filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VN_VG_P_adj,
             pv_raw = VN_VG_P,
             b_coe = VN_VG_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VN+', 
                 'VG+'))) %>%
           
           
           mutate(
             rescat = factor(rescat, 
                             levels=c('VG+', 
                                      'VN+', 
                                      'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>% 
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.5,
             size = 3,
             seed = 16) +
           
           labs(x = 'Standardized difference', 
                y = '-log10 (P-value)') +
           
           scale_color_manual(values = color_map, name = '') + 
           ggtitle('VN vs VG, children > 3 years') +
           
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}

```

## Covariates importance

### Table

```{r}
AIC_child_old <- read.xlsx("gitignore/data/AIC_child_old.xlsx") %>% 
  mutate(across(where(is.numeric), ~round(., 1)))

table9 <- kbl(AIC_child_old, caption = 
      "Table 9. Decrease of The Akaike information criterion (AIC) after addition of given outcome to quantile regression model, children > 3 years. The change of AIC indicate out-of-sample predictive accuracy of the models and was bounded to -30 (large importance of a covariate) and 0 (no to negliable importance).") %>% 
  kable_styling("striped",full_width = T) %>% 
  column_spec(1, width_min = '1.5in') 

table9
```

### Heatmap

```{r, fig.height=6, fig.width=8}
#| fig.cap: 'Figure 12. Heatmap showing the extend of decrase of the Akaike information criterion (AIC) after addition of given outcome to quantile regression model, children > 3 years. The change of AIC indicate out-of-sample predictive accuracy of the models and was bounded to -30 (large importance of a covariate, blue) and 0 (no to negliable importance, red).'
heat_map(AIC_child_old)
```

# Adults

## Diet effects

### Unstandardized effects

```{r}

diet_adult <- read.xlsx("gitignore/data/diet_adult.xlsx") %>% 
  mutate(outcome = clean_outcome_names(outcome)) %>%
  mutate(outcome = case_when(
    outcome == 'FOLAT' ~ 'FOLATE',
    outcome == 'VKFE' ~ 'TIBC',
    outcome == 'Cros' ~ 'CTX',
    outcome == 'log2_Cros' ~ 'log2_CTX',
    outcome == 'VIT_AKTB12' ~ 'HOLOTC',
    outcome == 'log2_VIT_AKTB12' ~ 'log2_HOLOTC',
    TRUE ~ outcome
  ))

diet_adult2 <- diet_adult %>%   
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))

table10 <- kbl(diet_adult2, caption = 
      "Table 10. Differences between diet groups across outcomes in adults, based on quantile regression modelling") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 

table10
```

### Standardized effects by 1SD

```{r}

ids <- 6:46
inde <- min(ids)-1
ids <- ids-inde

sds <- vector("double", max(ids))
meds <- diet_adult %>% filter(estimand == 'median')

for(i in seq_along(ids)){
  sds[i] <- ifelse(grepl("log2", meds[(i), 1]),
                   sd(log2(dat_adult[,(i+inde)]), na.rm = TRUE),
                   sd(dat_adult[,(i+inde)], na.rm = TRUE))
}

sds <- c(rep(sds, each=3))

diet_adult_Z <- diet_adult %>% 
  mutate(SD = sds) %>% 
  mutate(VN_OM_diff = VN_OM_diff/SD,
         VG_OM_diff = VG_OM_diff/SD,
         VN_VG_diff = VN_VG_diff/SD) %>% 
  select(-SD) %>% 
  mutate(VG_OM_P = if_else(VG_OM_P < 1e-5, 1e-5, VG_OM_P)) %>% 
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))


table11 <- kbl(diet_adult_Z, caption = 
      "Table 11. Standardized differences between diet groups across outcomes in adults, based on quantile regression modelling") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 

table11
```

## Vulcano plots

### VN vs OM

```{r}
#| fig.cap: 'Figure 13. Vulcano plot showing standardized differences between VN adn OM across clinical outcomes in adults.'

plotac <- 'fig13'

path = paste0('gitignore/figures/',plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_adult_Z %>% 
           filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VN_OM_P_adj,
             pv_raw = VN_OM_P,
             b_coe = VN_OM_diff) %>% 
           
           mutate(
             pv_adj = VN_OM_P_adj,
             pv_raw = VN_OM_P,
             b_coe = VN_OM_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VN+', 
                 'OM+'))) %>%
           
           mutate(
             rescat = factor(rescat, 
                             levels = c('OM+', 'VN+', 'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>%
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.6, 
             size = 2.5,
             seed = 17) +
           
           labs(x = 'Standardized difference', y = '-log10 (P-value)') +
           scale_color_manual(values = color_map, name = '') + 
           ggtitle('VN vs. OM, adults') +
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
         )
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}
```


### VG vs OM

```{r}
#| fig.cap: 'Figure 14. Vulcano plot showing standardized differences between OM and VN across clinical outcomes in adults.'
cole <- c('blue2', 'red3', 'grey50')

set.seed(17)

plotac <- 'fig14'

path = paste0('gitignore/figures/',plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_adult_Z %>% 
           filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VG_OM_P_adj,
             pv_raw = VG_OM_P,
             b_coe = VG_OM_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VG+', 
                 'OM+'))) %>%
           
           mutate(
             rescat = factor(rescat, 
                             levels = c('OM+', 'VG+', 'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>% 
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha=1, 
             box.padding = 0.6,
             size = 2.5,
             seed = 17) +
           
           labs(x = 'Standardized difference', y = '-log10 (P-value)') +
           scale_color_manual(values = color_map, name = '') +  
           ggtitle('VG vs OM, adults') +
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
           ) 
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}
```

### VN vs VG

```{r}
#| fig.cap: 'Figure 15. Vulcano plot showing standardized differences between VN and OM across clinical outcomes in adults.'

plotac <- 'fig15'

path = paste0('gitignore/figures/', plotac, '.rds')

if(file.exists(path) == FALSE){
  assign(plotac, diet_adult_Z %>% 
             filter(estimand != 'OR') %>% 
           mutate(int = interaction(outcome, estimand)) %>%
           
           mutate(
             pv_adj = VN_VG_P_adj,
             pv_raw = VN_VG_P,
             b_coe = VN_VG_diff) %>% 
           
           mutate(
             m_ylab = -log10(pv_raw),
             m_xlab = b_coe,
             rescat = if_else(
               pv_raw >= 0.05, 
               'P>0.05', 
               if_else(
                 b_coe > 0, 
                 'VN+', 
                 'VG+'))) %>%
           
           
           mutate(
             rescat = factor(rescat, 
                             levels=c('VG+', 
                                      'VN+', 
                                      'P>0.05')),
             meta_labels = if_else(pv_raw < 0.05, int, '')) %>% 
           
           ggplot(aes(x = b_coe, 
                      y = m_ylab, 
                      color = rescat, 
                      alpha = rescat,
                      label = meta_labels)) +
           
           geom_point(size = 2, shape = 16, alpha = 0.6) + 
           
           geom_text_repel(aes(
             x = m_xlab,
             y = m_ylab), 
             show.legend = FALSE, 
             alpha = 1, 
             box.padding = 0.6,
             size = 2.5,
             seed = 16) +
           
           labs(x = 'Standardized difference', 
                y = '-log10 (P-value)') +
           
           scale_color_manual(values = color_map, name = '') + 
           ggtitle('VN vs VG, adults') +
           
           theme(legend.text = element_text(size = 11),
                 axis.title = element_text(size = 12))+
           coord_cartesian(ylim = c(0, 5),
                           xlim = c(-1.7, 1.7))
           ) 
  
  saveRDS(get(plotac), file = path)
  get(plotac)
  
} else {assign(plotac, readRDS(path))
    get(plotac)}
```

## Covariates importance

### Table

```{r}
if(file.exists("gitignore/data/AIC_adult.xlsx")==FALSE){
  AIC_adult <- AIC_adult[-1,]
  write.xlsx(AIC_adult, "gitignore/data/AIC_adult.xlsx")
  }

AIC_adult <- read.xlsx("gitignore/data/AIC_adult.xlsx") %>% 
  mutate(across(where(is.numeric), ~round(., 1)))

table12 <- kbl(AIC_adult, caption = 
      "Table 12. Decrease of The Akaike information criterion (AIC) after addition of given outcome to quantile regression model, for adults. The change of AIC indicate out-of-sample predictive accuracy of the models and was bounded to -30 (large importance of a covariate) and 0 (no to negliable importance).") %>% 
  kable_styling("striped",full_width = T) %>% 
  column_spec(1, width_min = '1.5in') 

table12
```

### Heatmap

```{r, fig.height=6, fig.width=8}
#| fig.cap: 'Figure 16. Heatmap showing the extend of decrase of the Akaike information criterion (AIC) after addition of given outcome to quantile regression model, for adults. The change of AIC indicate out-of-sample predictive accuracy of the models and was bounded to -30 (large importance of a covariate, blue) and 0 (no to negliable importance, red).'
heat_map(AIC_adult)
```

# Vulcano matrix

## Main matrix

### Prepare

```{r}
plotac <- 'fig17'
path = paste0('gitignore/figures/', plotac, '.rds')

if(file.exists(path) == FALSE){
  fig5 <- fig5 + theme(legend.position = 'none',
                       plot.title = element_blank())
  fig6 <- fig6+ theme(legend.position = 'none',
                      plot.title = element_blank())
  fig7 <- fig7 + theme(legend.position = 'none',
                       plot.title=element_blank())

  fig9 <- fig9 + theme(legend.position = 'none',
                       plot.title = element_blank())
  fig10 <- fig10+ theme(legend.position = 'none',
                      plot.title = element_blank())
  fig11 <- fig11 + theme(legend.position = 'none',
                       plot.title = element_blank())

  fig13 <- fig13 + theme(legend.position = 'bottom',
                       plot.title = element_blank())
  fig14 <- fig14 + theme(legend.position = 'bottom',
                      plot.title = element_blank())
  fig15 <- fig15 + theme(legend.position = 'bottom',
                       plot.title = element_blank())
  }
```


### Create subfigures

```{r, fig.height=10, fig.width=10, warning=FALSE}

if(file.exists(path) == FALSE){
  child_young_volc <- ggarrange(fig5 + 
                       theme(axis.text.x = element_blank(),
                             axis.ticks.x = element_blank(),
                             axis.title.x = element_blank()) , 
                   fig6 + 
                       theme(axis.text.y = element_blank(),
                             axis.ticks.y = element_blank(),
                             axis.title.y = element_blank(),
                             axis.text.x = element_blank(),
                             axis.ticks.x = element_blank(),
                             axis.title.x = element_blank()), 
                   
                   fig7 + 
                       theme(axis.text.y = element_blank(),
                             axis.ticks.y = element_blank(),
                             axis.title.y = element_blank(),
                             axis.text.x = element_blank(),
                             axis.ticks.x = element_blank(),
                             axis.title.x = element_blank()),
                   nrow = 1, 
                   ncol = 3,
                   widths = c(1.1, 1, 1),
                   labels = c('A', '', '')
                   )
  
  child_young_volc <- annotate_figure(
    child_young_volc,
    top = text_grob("Children < 3 years", face = "bold", size = 10))
                  
  
  child_old_volc <- ggarrange(

                   fig9 + 
                       theme(axis.text.x = element_blank(),
                             axis.ticks.x = element_blank(),
                             axis.title.x = element_blank()) , 
                   
                   fig10 + 
                       theme(axis.text.y = element_blank(),
                             axis.ticks.y = element_blank(),
                             axis.title.y = element_blank(),
                             axis.text.x = element_blank(),
                             axis.ticks.x = element_blank(),
                             axis.title.x = element_blank()), 
                   
                   fig11 + 
                       theme(axis.text.y = element_blank(),
                             axis.ticks.y = element_blank(),
                             axis.title.y = element_blank(),
                             axis.text.x = element_blank(),
                             axis.ticks.x = element_blank(),
                             axis.title.x = element_blank()),
                   nrow = 1, 
                   ncol = 3,
                   widths = c(1.1, 1, 1),
                   labels = c('B', '', '')
                   )
  child_old_volc <- annotate_figure(
    child_old_volc,
    top = text_grob("Children > 3 years", face = "bold", size = 10))              
                   
  adult_volc <- ggarrange(                   
                   fig13,
                   fig14 + 
                       theme(axis.text.y = element_blank(),
                             axis.ticks.y = element_blank(),
                             axis.title.y = element_blank() ), 
                   fig15 + 
                       theme(axis.text.y = element_blank(),
                             axis.ticks.y = element_blank(),
                             axis.title.y = element_blank()) ,
                   nrow = 1, 
                   ncol = 3,
                   widths = c(1.1, 1, 1),
                   labels = c('C', '', '')
                   )
  
  adult_volc <- annotate_figure(
    adult_volc,
    top = text_grob("Adults", face = "bold", size = 10))       
  }
```

### Figure

```{r, fig.height=10, fig.width=10, warning=FALSE}
#| fig.cap: 'Figure 17. Vulcano plot showing standardized differences between VN vs OM (*left*), VG vs OM (*middle*) and VN vs VG (*right*) across clinical outcomes in children younger 3 years (**A**, *top*), children older 3 years (**B**) and adults (**C**, *bottom*). Estimated effects are based on quantile regression.'

if(file.exists(path) == FALSE){
  assign(plotac,
       ggarrange(
         child_young_volc, 
         child_old_volc, 
         adult_volc,
         nrow = 3, 
         ncol = 1,
         heights = c(1, 1, 1.33))
       )
  
  saveRDS(get(plotac), file = path)
  get(plotac)} else {
    assign(plotac, readRDS(path))
    get(plotac)}


path <- paste0('gitignore/figures/', plotac, '.tiff')
if(file.exists(path) == FALSE){
  tiff(path, width = 10, height = 10, units = 'in', res = 400) 
  grid.draw(get(plotac))
  dev.off()
}

path <- paste0('gitignore/figures/', plotac, '.pdf')
if(file.exists(path) == FALSE){
  ggsave(path, 
         plot = get(plotac),
         width = 10, height = 10)
}
```


## All children matrix

Everything in at once

```{r, fig.height=5, fig.width=10, warning=FALSE}
#| fig.cap: 'Figure 18. Vulcano plot showing standardized differences between VN vs OM (*left*), VG vs OM (*middle*) and VN vs VG (*right*) across clinical outcomes in children of all ages. Estimated effects are based on quantile regression.'

plotac <- 'fig18'
path = paste0('gitignore/figures/', plotac, '.rds')

if(file.exists(path) == FALSE){
  fig1 <- fig1 + theme(legend.position = 'bottom',
                       plot.title = element_blank())
  fig2 <- fig2 + theme(legend.position = 'bottom',
                      plot.title = element_blank())
  fig3 <- fig3 + theme(legend.position = 'bottom',
                       plot.title = element_blank())
  
  child_all_volc <- ggarrange(
    fig1,
    fig2 + 
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.title.y = element_blank()), 
    
    fig3 +
      theme(axis.text.y = element_blank(),
            axis.ticks.y = element_blank(),
            axis.title.y = element_blank()),
    nrow = 1, 
    ncol = 3,
    widths = c(1.1, 1, 1))
  
   assign(plotac,
          annotate_figure(
            child_all_volc,
            top = text_grob("All children", 
                            face = "bold", 
                            size = 10)))
   
   saveRDS(get(plotac), file = path)
   get(plotac)
} else {
    assign(plotac, readRDS(path))
    get(plotac)}

```


# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
