---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: 'Statistical report - quantile regression in old children'
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: 'Open code'
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: '#2D2D31'
fontcolor: '#C4C4C4'
monobackgroundcolor: '#3B3B3B'
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Analysis

Import initiation file

```{r}
source('368_initiation.R')
```


Define number of bootstrap simulations per model

```{r}
nsim = 21000
quantils = c(0.2, 0.5, 0.8)
```

Old children models will be adjusted for the effect of `log2_age` (when applicable, i.e. not for age-adjusted Anthropometric data), `SEX`, `aBreastFeed_total_stopped`, and `aBreastFeed_full_duration` (the duration of the dependence on the breastfeeding). Additional covariates (relevant supplementation for vitamins and biogenic elements levels) or birth weight (anthropometric data) will be added as covariates.

```{r}
AIC_child_old <- data.frame(outcome = NA,
                            estimand = NA,
                            log2_age = NA,
                            aSEX = NA,
                            Breast_Feed = NA,
                            other_cov = NA,
                            diet = NA)

diet_child_old <- data.frame(outcome = NA,
                             estimand = NA,
                             VN_OM_diff = NA, 
                             VN_OM_P = NA,
                             VG_OM_diff = NA, 
                             VG_OM_P = NA,
                             VN_VG_diff = NA, 
                             VN_VG_P = NA)

i = 1
j = 1
ni= 10
```

## Individual outcomes models

### aMASS_Perc

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_old)[i+ni]

AIC_child_old$outcome[i] <- column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
     SEX + 
     GRP +
     aBiW +
     #s(log2_age)
     s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'child_old',
                  exclude = c('log2_age'),
                  include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aMASS_Perc_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_73 <- kbl(res, caption = 
      'Suppl. Table 73. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of body mass. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_73
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('log2_age', 'SEX'), 
                  include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c('log2_age',
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('log2_age', 'GRP'), 
                   include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(type = 'child_old',
                       exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA
  # rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aBiW')
```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aHEIGHT_Perc

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',
                  exclude = c('log2_age'),
                  include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aHEIGHT_Perc_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_74 <- kbl(res, caption = 
      'Suppl. Table 74. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of body height. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_74
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('log2_age', 'SEX'), 
                  include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c('log2_age',
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('log2_age', 'GRP'), 
                   include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(type = 'child_old',
                       exclude = c('log2_age'))


### model without log2_age
mod_log2_age <- NA
  # rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aBMI_PERC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    #s(log2_age)
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',
                  exclude = c('log2_age'),
                  include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aBMI_PERC_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_75 <- kbl(res, caption = 
      'Suppl. Table 75. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of BMI. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_75
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('log2_age', 'SEX'), 
                  include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c('log2_age',
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('log2_age', 'GRP'), 
                   include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(type = 'child_old',
                       exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA
  # rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aM_per_H_PERC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aM_per_H_PERC_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_76 <- kbl(res, caption = 
      'Suppl. Table 76. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of percentile of weight to height ratio. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')

suppl_table_76
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c('log2_age',
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(type = 'child_old',exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA
  # rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aBiW')
```

Putting key results together

```{r}
## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aGLY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aGLY_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_77 <- kbl(res, caption = 
      'Suppl. Table 77. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of glycemia. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_77
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c(
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',
                      exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aTC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aTC_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_78 <- kbl(res, caption = 
      'Suppl. Table 78. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of total cholesterol. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_78
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c(
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',
                      exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aHDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Diagnostic plot looks better now, but the difference in not huge. We will use original values to unify it with LDL analysis where transformation is unsuitable.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old', 
                  include = c())

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aHDL_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_79 <- kbl(res, caption = 
      'Suppl. Table10. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of HDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_79
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c(
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',
                      exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aLDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit, original was much better. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',
                  include = c())

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aLDL_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_80 <- kbl(res, caption = 
      'Suppl. Table 80. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of LDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_80
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c(
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',
                      exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aTG

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aTG_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_81 <- kbl(res, caption = 
      'Suppl. Table 81. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(TG cholecterol) levels. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_81
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aCa

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Ca'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aCa_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_82 <- kbl(res, caption = 
      'Suppl. Table 82. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of serum Ca level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_82
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Ca')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Ca')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Ca')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Ca')

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aP_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_83 <- kbl(res, caption = 
      'Suppl. Table 83. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of serum P level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_83
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aMg

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Mg)) 

```

\`

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Mg +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Mg'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aMg_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_84 <- kbl(res, caption = 
      'Suppl. Table 84. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of serum Mg level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_84
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Mg')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Mg')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Mg')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Mg')

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aSe

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Diagnostics does not show a sign of an improvement

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 

mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Se'))

## bootstrapping of main model

mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aSe_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_85 <- kbl(res, caption = 
      'Suppl. Table 85. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile serum Se level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_85

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Se')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Se')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Se')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Se')

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aZn

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Zn +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 

mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Zn'))

## bootstrapping of main model

mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aZn_boot', reuse=TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_86 <- kbl(res, caption = 
      'Suppl. Table 86. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Zn level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_86

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Zn')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Zn')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Zn')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Zn')

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aFe_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_87 <- kbl(res, caption = 
      'Suppl. Table 87. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Fe level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_87
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aVKFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aVKFE_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_88 <- kbl(res, caption = 
      'Suppl. Table 88. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum ferritin Fe binding capacity. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_88
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aFERR

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. It seems that the `aFERR` change in multiplicative, rather than additive way. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aFERR_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_89 <- kbl(res, caption = 
      'Suppl. Table 89. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(serum ferritin) levels. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_89
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_90 <- kbl(res, caption = 
      'Suppl. Table 90. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum transferin level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_90
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aSATTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aSATTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_91 <- kbl(res, caption = 
      'Suppl. Table 91. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of transferin saturation. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')

suppl_table_91
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aTRFINDEX

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}
gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aTRFINDEX_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_92 <- kbl(res, caption = 
      'Suppl. Table 92. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of sTfR index (log2-ratio). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_92
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aSTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}
gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation lightly improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aSTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_93 <- kbl(res, caption = 
      'Suppl. Table 93. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(soluble transferin receptor level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_93
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aHGB

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}
gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aHGB_boot', reuse=TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_94 <- kbl(res, caption = 
      'Suppl. Table 94. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of hemoglobin level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_94

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c('aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',
                      exclude = c('log2_age'))

```

Putting key results together

```{r}

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aMCV

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aMVC_boot', reuse=TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_95 <- kbl(res, caption = 
      'Suppl. Table 95. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of mean corpuscular volume. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_95

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aPTH

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aPTH_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_96 <- kbl(res, caption = 
      'Suppl. Table 96. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of parathormone level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_96
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aCros

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Ca', 'aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aCros_boot', reuse=TRUE)



## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_97 <- kbl(res, caption = 
      'Suppl. Table 97. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(beta cross laps). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_97
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = c('aSUP_Ca', 'aSUP_D'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = c('aSUP_Ca', 'aSUP_D'))

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = c('aSUP_Ca', 'aSUP_D'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aP1NP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_Ca', 'aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aP1NP_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_98 <- kbl(res, caption = 
      'Suppl. Table 98. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of procollagen type I level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_98

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = c('aSUP_Ca', 'aSUP_D'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = c('aSUP_Ca', 'aSUP_D'))

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = c('aSUP_Ca', 'aSUP_D'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aUI

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c())

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aUI_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_99 <- kbl(res, caption = 
      'Suppl. Table 99. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of urinary iodine level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_99

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without supplementation
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aUREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))  
  
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aUREA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_100 <- kbl(res, caption = 
      'Suppl. Table 100. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of urea level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_100
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c('aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old', exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old', exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aCREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aCREA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_101 <- kbl(res, caption = 
      'Suppl. Table 101. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(creatinine) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_101
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aUA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aUA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_102 <- kbl(res, caption = 
      'Suppl. Table 102. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of uric acid level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_102
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aVIT_AKTB12

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name),
         log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age_2) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age_2) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c('log2_age'),
                    include = c('aSup_B12', 'log2_age_2'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aVIT_AKTB12_boot', reuse=TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_103 <- kbl(res, caption = 
      'Suppl. Table 103. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(vitamin B12) serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_103

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX','log2_age'), 
                  include = c('aSup_B12', 'log2_age_2'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration','log2_age'),  
                 include = c('aSup_B12', 'log2_age_2'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP','log2_age'),
                   include = c('aSup_B12', 'log2_age_2'))

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',exclude=c('log2_age'), include=c('log2_age_2'))

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSup_B12')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aHCY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed = 17, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aHCY_boot', 
  reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20, res_tab_q50, res_tab_q80)
  
suppl_table_104 <- kbl(res, caption = 
      'Suppl. Table 104. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(homocysteine) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_104
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aMMA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. Even though it's not perfect we will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_old_aMMA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_105 <- kbl(res, caption = 
      'Suppl. Table 105. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(methylmalonic acid) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_105
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```

### aVIT_D

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_D)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Looks better

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',
                  include = c('aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aVIT_D_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20, res_tab_q50, res_tab_q80)
  
suppl_table_106 <- kbl(res, caption = 
      'Suppl. Table 106. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(vitamin D) serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_106
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_D')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_D')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_D')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_D')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aFOLAT

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name 

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_FOL))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_FOL +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'child_old',exclude = c(),
                    include = c('aSUP_FOL'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aFOLAT_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_107 <- kbl(res, caption = 
      'Suppl. Table 107. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of folate serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_107
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',exclude = c('SEX'), include = 'aSUP_FOL')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',exclude = c(
                             
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_FOL')

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',exclude = c('GRP'),include = 'aSUP_FOL')

### model without supplementation
mod_other_cov <- rqfit(type = 'child_old',)

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',exclude = c('log2_age'), include = 'aSUP_FOL')

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1 
```

### aIGF1

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Looks better

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(type = 'child_old',)

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_old_aIGF1_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_108 <- kbl(res, caption = 
      'Suppl. Table 108. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(growth factor) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_108
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'child_old',
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(type = 'child_old',
                 exclude = c(
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(type = 'child_old',
                   exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(type = 'child_old',
                      exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_old <- add_AIC(AIC_child_old)

diet_child_old <- add_eff(diet_child_old, res)

i = i+1
```


### Saving tables

```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_child_old.xlsx') == FALSE){
  diet_child_old <- diet_child_old[-1,]
  
  diet_child_old$VN_OM_P_adj <- NA
  diet_child_old$VG_OM_P_adj <- NA
  diet_child_old$VN_VG_P_adj <- NA
  
for (i in seq(1, nrow(diet_child_old), by = 3)) {
  padj <- p.adjust(c(
    diet_child_old$VN_OM_P[i], 
    diet_child_old$VN_OM_P[i+1],
    diet_child_old$VN_OM_P[i+2],
    
    diet_child_old$VG_OM_P[i],
    diet_child_old$VG_OM_P[i+1],
    diet_child_old$VG_OM_P[i+2],
    
    diet_child_old$VN_VG_P[i],
    diet_child_old$VN_VG_P[i+1],
    diet_child_old$VN_VG_P[i+2]), method = 'hochberg')
  
  diet_child_old$VN_OM_P_adj[i:(i+2)] <- padj[1:3]
  diet_child_old$VG_OM_P_adj[i:(i+2)] <- padj[4:6]
  diet_child_old$VN_VG_P_adj[i:(i+2)] <- padj[7:9]
}
  
  
  diet_child_old <- diet_child_old %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) %>% 
    mutate(across(.cols = c(VN_OM_P, VG_OM_P, VN_VG_P,
                            VN_OM_P_adj, VG_OM_P_adj, VN_VG_P_adj), ~ round(.x, 5)))

  write.xlsx(diet_child_old, 'gitignore/data/diet_child_old.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_child_old.xlsx') == FALSE){
  AIC_child_old <- AIC_child_old[-1,]
  write.xlsx(AIC_child_old, 'gitignore/data/AIC_child_old.xlsx')
  }
```

# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
