---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: "Statistical report - diet prediction (elastic net)"
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 4
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: "Open code"
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
bibliography: references.bib
fontcolor: '#C4C4C4'
monobackgroundcolor: "#3B3B3B"
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Import initiation file

```{r}
source('368_initiation.R')
```

# Data wrangling

## All children

```{r, collapse=TRUE}
dat_child_all <- read.table("data/dat_child_all.txt") %>% 
  mutate(log2_aTG = log2(aTG),
         log2_aFERR = log2(aFERR),
         log2_aTRFINDEX = log2(aTRFINDEX),
         log2_aSTRF = log2(aSTRF),
         log2_aCros = log2(aCros),
         log2_aVIT_AKTB12 = log2(aVIT_AKTB12),
         log2_aHCY  = log2(aHCY),
         log2_aMMA =  log2(aMMA),
         log2_aVIT_D = log2(aVIT_D),
         log2_aIGF1 = log2(aIGF1)
         ) %>% 
  mutate(aBreastFeed_full_duration = aBreastFeed_total_stopped*aBreastFeed_full,
         male = if_else(SEX == "M", 1,0),
         GRP = factor(GRP),
         FAM = factor(FAM)) %>% 
   select(-SEX, -aBreastFeed_full, -ID,
          -c(aSUP_VEG1:aSUP_OTH),
          -aTG, -aFERR, - aTRFINDEX,
          -aSTRF, -aCros, -aVIT_AKTB12, -aHCY,
          -aMMA, -aVIT_D, -aIGF1) 


summary(dat_child_all)
```

Removing rows with >1/4 of missing values

```{r}
dat_child_all <- dat_child_all %>%
  filter(rowMeans(is.na(.)) <= 0.25) %>% 
  mutate(FAM = factor(FAM))

summary(dat_child_all)
```



## Children > 3 y.o.

```{r}
dat_child_old <- dat_child_all %>% 
  filter(aAGE>3) %>% 
  mutate(GRP = factor(GRP),
         FAM = factor(FAM))
```

## Children < 3 y.o.

```{r}
dat_child_young <- dat_child_all %>% 
  filter(aAGE<=3) %>% 
  mutate(GRP = factor(GRP),
         FAM = factor(FAM))

summary(dat_child_young)
```

## Missing values and standardization

- Removing features with over 20% NA values.
- Replacing missing values with mean values, scaling numerical variables to zero mean and 0.5 SD. 

### Children all

```{r}
dat_child_all <- dat_child_all %>%
  select(where(~ mean(is.na(.)) <= 0.2)) %>% 
  mutate(across(where(is.numeric), ~ if_else(
    is.na(.), mean(., na.rm = TRUE), .))) %>%
  mutate(across(-aAGE & where(~is.numeric(.) && 
                                length(unique(.)) > 2), 
                arm::rescale))

summary(dat_child_all)
```


### Children young

```{r}
dat_child_young <- dat_child_young %>%
  select(where(~ mean(is.na(.)) <= 0.2)) %>% 
  mutate(across(where(is.numeric), ~ if_else(
    is.na(.), mean(., na.rm = TRUE), .))) %>%
  mutate(across(-aAGE & where(~is.numeric(.) && 
                                length(unique(.)) > 2), 
                arm::rescale))

summary(dat_child_young)
```


### Children old

```{r}
dat_child_old <- dat_child_old %>%
  select(where(~ mean(is.na(.)) <= 0.2)) %>% 
  mutate(across(where(is.numeric), ~ if_else(
    is.na(.), mean(., na.rm = TRUE), .))) %>%
  mutate(across(-aAGE & where(~is.numeric(.) && 
                                length(unique(.)) > 2), 
                arm::rescale))

summary(dat_child_old)
```


## Adults

```{r}
dat_adult <- read.table("data/dat_adult.txt") %>%  
  mutate(log2_aFAT = log2(aFAT),
         log2_aFFM = log2(aFFM),
         log2_aTC = log2(aTC),
         log2_aTG = log2(aTG),
         log2_aZn = log2(aZn),
         log2_aVKFE = log2(aVKFE),
         log2_aFERR = log2(aFERR),
         log2_aTRF = log2(aTRF),
         log2_aTRFINDEX = log2(aTRFINDEX),
         log2_aSTRF = log2(aSTRF),
         log2_aCros = log2(aCros),
         log2_aVIT_AKTB12 = log2(aVIT_AKTB12),
         log2_aUREA = log2(aUREA),
         log2_aHCY  = log2(aHCY),
         log2_aVIT_D  = log2(aVIT_D),
         log2_aMMA =  log2(aMMA)
         ) %>% 
  mutate(male = if_else(SEX == "M", 1,0),
         GRP = factor(GRP),
         FAM = factor(FAM)) %>% 
   select(-SEX, -ID,
          -c(aSUP_VEG1:aSUP_OTH),
          -c(aFAT, aFFM, aTC, aTG, aZn, aVKFE, aFERR, aTRF, aTRFINDEX, aSTRF,
             aCros, aVIT_AKTB12, aUREA, aHCY, aVIT_D, aMMA)) %>% 
  mutate_if(is.character, factor) 

summary(dat_adult)
```

Removing features with over 10% of missing values and removing rows with over 50% missing values

```{r}
dat_adult <- dat_adult %>%
  filter(rowMeans(is.na(.)) <= 0.25) %>%  
  select(where(~ mean(is.na(.)) <= 0.2)) 

summary(dat_adult)
```

Replacing missing values with mean values, scaling numerical variables to zero mean and 0.5 SD

```{r}
dat_adult <- dat_adult %>%
  mutate(across(where(is.numeric), ~ 
                  if_else(is.na(.), mean(., na.rm = TRUE), .))) %>%
  mutate(across(where(~is.numeric(.) && 
                        length(unique(.)) > 2), arm::rescale)) %>% 
  mutate(FAM = factor(FAM))

summary(dat_adult)
```

# Diet prediction

(OM, VN, VG determination)

All prediction models will account for the variable `FAM` as the grouping (block) variable, ensuring that all subject of a single family will be part of the same fold during each bootstrap iteration. 

## All children

### Baseline model

Following models will be trained to discriminate between two diets, based solely on `aAGE`, `SEX`, `aBreastFeed_total_stopped`, `aBreastFeed_full_stopped` and interaction `aBreastFeed_full_stopped : aBreastFeed_full`.


#### Prepare data

```{r}
dat_pred <- dat_child_all %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,  
         aBreastFeed_full_stopped, aBreastFeed_total_stopped, aBiW) 

nfam <- dat_pred$FAM %>% factor() %>% levels() %>% length()

dat_features <- dat_pred %>% select(-FAM, -GRP) %>% as.matrix
colnames(dat_features)

dat_outcome <- dat_pred %>% select(GRP) %>% as.matrix
```

#### VN vs OM


```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_all_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_all_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_all_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Complete model

Baseline + clinical characteristics 

#### Prepare data

```{r}

dat_pred <- dat_child_all %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,  
         aBreastFeed_full_stopped, aBreastFeed_total_stopped, 
         aBiW,
         aMASS_Perc:aFOLAT, log2_aTG:log2_aIGF1)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_all_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_all_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_all_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Reduced 

Baseline + clinical characteristics not affected with vitamins supplementation

#### Prepare data

```{r}

dat_pred <- dat_child_all %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,  
         aBreastFeed_full_stopped, aBreastFeed_total_stopped, 
         aBiW,
         aMASS_Perc:aUA, log2_aTG:log2_aCros)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_all_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_all_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_all_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

## Young children (\<3 years)


### Baseline model

Following models will be trained to discriminate the patients into one of the two groups, based solely on age, sex and breastfeed-related characteristics. 

#### Prepare data

```{r}
dat_pred <- dat_child_young %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,  
         aBreastFeed_full_stopped, aBreastFeed_total_stopped, aBiW) 

nfam <- dat_pred$FAM %>% factor() %>% levels() %>% length()

dat_features <- dat_pred %>% select(-FAM, -GRP) %>% as.matrix
colnames(dat_features)

dat_outcome <- dat_pred %>% select(GRP) %>% as.matrix
```

#### VN vs OM


```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_young_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_young_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_young_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Complete model

Baseline + clinical characteristics 

#### Prepare data

```{r}

dat_pred <- dat_child_young %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,  
         aBreastFeed_full_stopped, aBreastFeed_total_stopped, 
         aBiW,
         aMASS_Perc:aFOLAT, log2_aTG:log2_aIGF1)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_young_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_young_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_young_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```
### Reduced model

Baseline + clinical characteristics not affected with vitamin supplementation

#### Prepare data

```{r}

dat_pred <- dat_child_young %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,  
         aBreastFeed_full_stopped, aBreastFeed_total_stopped, 
         aBiW,
         aMASS_Perc:aUA, log2_aTG:log2_aCros)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_young_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_young_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_young_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```
## Old children (>3 years old)


### Baseline model

Following models will be trained to discriminate between two diet groups, based solely on `aAGE`, `SEX`, and interaction `aBreastFeed_full_stopped : aBreastFeed_full`.


#### Prepare data

```{r}
dat_pred <- dat_child_old %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,  
          aBiW) 

nfam <- dat_pred$FAM %>% factor() %>% levels() %>% length()

dat_features <- dat_pred %>% select(-FAM, -GRP) %>% as.matrix
colnames(dat_features)

dat_outcome <- dat_pred %>% select(GRP) %>% as.matrix
```


#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_old_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_old_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_old_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```



### Complete models

Baseline + clinical characteristics

#### Prepare data

```{r}

dat_pred <- dat_child_old %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,
         aBiW,
         aMASS_Perc:aFOLAT, log2_aTG:log2_aIGF1)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_old_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_old_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_old_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Reduced models

Baseline + clinical characteristics not affected with vitamin supplementation

#### Prepare data

```{r}

dat_pred <- dat_child_old %>% 
  select(GRP, FAM, log2_age, male, aBreastFeed_full_duration,
         aBiW,
         aMASS_Perc:aUA, log2_aTG:log2_aCros)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_old_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_old_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_old_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```


## Adults

### Baseline model

Following models will be trained to discriminate between two diets, based solely on `aAGE` and `SEX`. 


#### Prepare data

```{r}
dat_pred <- dat_adult %>% 
  select(GRP, FAM, aAGE, male) 

nfam <- dat_pred$FAM %>% factor() %>% levels() %>% length()

dat_features <- dat_pred %>% select(-FAM, -GRP) %>% as.matrix
colnames(dat_features)

dat_outcome <- dat_pred %>% select(GRP) %>% as.matrix
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_adult_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_adult_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_adult_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Complete model

Baseline + clinical characteristics

#### Prepare data

```{r}

dat_pred <- dat_adult %>% 
  select(GRP, FAM, aAGE, male,   
         aBMI:aFOLAT, log2_aFAT:log2_aMMA)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_adult_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_adult_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)


mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_adult_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Reduced model

Baseline + clinical characteristics not affected with vitamin supplementation

#### Prepare data

```{r}

dat_pred <- dat_adult %>% 
  select(GRP, FAM, aAGE, male,   
         aBMI:aUA, log2_aFAT:log2_aUREA)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_adult_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_adult_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)


mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_adult_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

## Models comaprison - complete vs baseline


### Prepare data 

```{r}
models_names <- c('pred_baseline_child_young_VN_OM',
                  'pred_baseline_child_young_VG_OM',
                  'pred_baseline_child_young_VN_VG',
                  'pred_complet_child_young_VN_OM',
                  'pred_complet_child_young_VG_OM',
                  'pred_complet_child_young_VN_VG',
                  'pred_baseline_child_old_VN_OM',
                  'pred_baseline_child_old_VG_OM',
                  'pred_baseline_child_old_VN_VG',
                  'pred_complet_child_old_VN_OM',
                  'pred_complet_child_old_VG_OM',
                  'pred_complet_child_old_VN_VG',
                  'pred_baseline_adult_VN_OM',
                  'pred_baseline_adult_VG_OM',
                  'pred_baseline_adult_VN_VG',
                  'pred_complet_adult_VN_OM',
                  'pred_complet_adult_VG_OM',
                  'pred_complet_adult_VN_VG'
                  )

tr <- get(models_names[1])$model_summary[
    c('auc_optimism_corrected', 
    'auc_optimism_corrected_CIL',
    'auc_optimism_corrected_CIU')]

for(i in 2:length(models_names)){
  tr <- dplyr::bind_rows(tr, get(models_names[i])$model_summary[
    c('auc_optimism_corrected', 
    'auc_optimism_corrected_CIL',
    'auc_optimism_corrected_CIU')])
  }

tr <- data.frame(models_names, 
                 y_pos = c(rep(0.9, 3), 
                           rep(0.84, 3),
                           rep(0.6, 3),
                           rep(0.54, 3),
                           rep(0.3, 3),
                           rep(0.24, 3)),
                 
                 age_group = c(rep('young_children', 6),
                               rep('old_children', 6),
                               rep('adults', 6)),
                 
                 contrast = str_sub(models_names, -5, -1),
                 model = str_sub(models_names, 6, 12),
                 tr)
```

### Models performance summary

```{r}
tr %>% 
  rename(`out of sample AUC` = `auc_optimism_corrected`,
         `CI_L` = `auc_optimism_corrected_CIL`,
         `CI_U` = `auc_optimism_corrected_CIU`) %>% 
  
  select(age_group : CI_U) %>%
  
  mutate(
    `out of sample AUC` = round(`out of sample AUC`, 2),
    `CI_L` = round(`CI_L`, 2),
    `CI_U` = round(`CI_U`, 2)) %>% 
  
  mutate(model = fct_recode(model,
                            baseline = "baselin",  
                            complet = "complet"))   %>% 
  
  kableExtra::kable()
```


### Comparison of baseline vs complet

```{r}

baseline <- tr %>% filter(model == 'baselin')
complet <- tr %>% filter(model == 'complet')

compmod <- compare_predmod(get(baseline$models_names[1]), 
                get(complet$models_names[1]))

comp_table <- data.frame(
  age_group = baseline$age_group[1],
  contrast = baseline$contrast[1],
  auc_gain = compmod[1],
  CI_L = compmod[2],
  CI_U = compmod[3],
  P = compmod[4]
)

for(i in 2:nrow(baseline)){
  
  compmod <- compare_predmod(get(baseline$models_names[i]), 
                get(complet$models_names[i]))
  
  comp_table_tmp <- data.frame(
    age_group = baseline$age_group[i],
    contrast = baseline$contrast[i],
    auc_gain = compmod[1],
    CI_L = compmod[2],
    CI_U = compmod[3],
    P = compmod[4])
  
  comp_table <- dplyr::bind_rows(comp_table, comp_table_tmp)
  
  i = i+1
}

comp_table[, 3:6] <- round(comp_table[, 3:6], 3)

kableExtra::kable(comp_table)
```


### Visualize

```{r, fig.width=6, fig.height=4}
p1 <- tr %>%
  mutate(contrast = factor(contrast, levels = c("VN_OM", "VG_OM", "VN_VG"))) %>%
  ggplot(aes(y = y_pos, group = model, color = model)) + 
  
  geom_point(aes(x = auc_optimism_corrected, 
                 y = y_pos),
             size = 5, 
             shape = 18) + 
  
  geom_segment(aes(y = y_pos, yend = y_pos,
                   x = auc_optimism_corrected_CIL,
                   xend = auc_optimism_corrected_CIU),
               linewidth = 1.1) + 
  
  coord_cartesian(xlim = c(0.1, 1), ylim = c(0.1,1)) +
  ggplot2::geom_vline(xintercept = 0.5, linetype = 'dashed') + 
  
  facet_wrap(~contrast, 
             labeller = labeller(
               contrast = c("VN_OM" = "VN vs OM", 
                            "VG_OM" = "VG vs OM", 
                            "VN_VG" = "VN vs VG"))) +
  
  scale_y_continuous(breaks = c(0.87, 0.57, 0.27), 
                     labels = c("Ch < 3 yrs", "Ch > 3 yrs", "Adults")) +
  
  theme(axis.title.y = element_blank(),
         legend.position = "bottom") +
  
  labs(x = "Out-of-sample AUC",  
       color = "Model") +  
  
  scale_color_manual(values = c("baselin" = "grey50", "complet" = "red"), 
                     labels = c("baselin" = "Baseline", "complet" = "complet"))

p1


```


## Models comaprison - reduced vs baseline

### Prepare data 

```{r}
models_names <- c('pred_baseline_child_young_VN_OM',
                  'pred_baseline_child_young_VG_OM',
                  'pred_baseline_child_young_VN_VG',
                  'pred_complex_child_young_VN_OM',
                  'pred_complex_child_young_VG_OM',
                  'pred_complex_child_young_VN_VG',
                  'pred_baseline_child_old_VN_OM',
                  'pred_baseline_child_old_VG_OM',
                  'pred_baseline_child_old_VN_VG',
                  'pred_complex_child_old_VN_OM',
                  'pred_complex_child_old_VG_OM',
                  'pred_complex_child_old_VN_VG',
                  'pred_baseline_adult_VN_OM',
                  'pred_baseline_adult_VG_OM',
                  'pred_baseline_adult_VN_VG',
                  'pred_complex_adult_VN_OM',
                  'pred_complex_adult_VG_OM',
                  'pred_complex_adult_VN_VG'
                  )

tr <- get(models_names[1])$model_summary[
    c('auc_optimism_corrected', 
    'auc_optimism_corrected_CIL',
    'auc_optimism_corrected_CIU')]

for(i in 2:length(models_names)){
  tr <- dplyr::bind_rows(tr, get(models_names[i])$model_summary[
    c('auc_optimism_corrected', 
    'auc_optimism_corrected_CIL',
    'auc_optimism_corrected_CIU')])
  }

tr <- data.frame(models_names, 
                 y_pos = c(rep(0.9, 3), 
                           rep(0.84, 3),
                           rep(0.6, 3),
                           rep(0.54, 3),
                           rep(0.3, 3),
                           rep(0.24, 3)),
                 
                 age_group = c(rep('young_children', 6),
                               rep('old_children', 6),
                               rep('adults', 6)),
                 
                 contrast = str_sub(models_names, -5, -1),
                 model = str_sub(models_names, 6, 12),
                 tr)

```

### Models performance summary

```{r}
tr %>% 
  rename(`out of sample AUC` = `auc_optimism_corrected`,
         `CI_L` = `auc_optimism_corrected_CIL`,
         `CI_U` = `auc_optimism_corrected_CIU`) %>% 
  
  select(age_group : CI_U) %>%
  
  mutate(
    `out of sample AUC` = round(`out of sample AUC`, 2),
    `CI_L` = round(`CI_L`, 2),
    `CI_U` = round(`CI_U`, 2)) %>% 
  
  mutate(model = fct_recode(model,
                            baseline = "baselin",  
                            complex = "complex"))   %>% 
  
  kableExtra::kable()
```

### Comparison of baseline vs reduced

```{r}

baseline <- tr %>% filter(model == 'baselin')
complex <- tr %>% filter(model == 'complex')

compmod <- compare_predmod(get(baseline$models_names[1]), 
                get(complex$models_names[1]))

comp_table <- data.frame(
  age_group = baseline$age_group[1],
  contrast = baseline$contrast[1],
  auc_gain = compmod[1],
  CI_L = compmod[2],
  CI_U = compmod[3],
  P = compmod[4]
)

for(i in 2:nrow(baseline)){
  
  compmod <- compare_predmod(get(baseline$models_names[i]), 
                get(complex$models_names[i]))
  
  comp_table_tmp <- data.frame(
    age_group = baseline$age_group[i],
    contrast = baseline$contrast[i],
    auc_gain = compmod[1],
    CI_L = compmod[2],
    CI_U = compmod[3],
    P = compmod[4])
  
  comp_table <- dplyr::bind_rows(comp_table, comp_table_tmp)
  
  i = i+1
}

comp_table[, 3:6] <- round(comp_table[, 3:6], 3)

kableExtra::kable(comp_table)
```


### Visualize
```{r, fig.width=6, fig.height=4}
p2 <- tr %>%
  mutate(contrast = factor(contrast, levels = c("VN_OM", "VG_OM", "VN_VG"))) %>%
  ggplot(aes(y = y_pos, group = model, color = model)) + 
  
  geom_point(aes(x = auc_optimism_corrected, 
                 y = y_pos),
             size = 5, 
             shape = 18) + 
  
  geom_segment(aes(y = y_pos, yend = y_pos,
                   x = auc_optimism_corrected_CIL,
                   xend = auc_optimism_corrected_CIU),
               linewidth = 1.1) + 
  
  coord_cartesian(xlim = c(0.1, 1), ylim = c(0.1,1)) +
  ggplot2::geom_vline(xintercept = 0.5, linetype = 'dashed') + 
  
  facet_wrap(~contrast, 
             labeller = labeller(
               contrast = c("VN_OM" = "VN vs OM", 
                            "VG_OM" = "VG vs OM", 
                            "VN_VG" = "VN vs VG"))) +
  
  scale_y_continuous(breaks = c(0.87, 0.57, 0.27), 
                     labels = c("Ch < 3 yrs", "Ch > 3 yrs", "Adults")) +
  
  theme(axis.title.y = element_blank(),
         legend.position = "bottom") +
  
  labs(x = "Out-of-sample AUC",  
       color = "Model") +  
  
  scale_color_manual(values = c("baselin" = "grey50", "complex" = "red"), 
                     labels = c("baselin" = "Baseline", "complex" = "Complex"))

p2
```

# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
