---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: 'Statistical report - quantile regression in children'
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: 'Open code'
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: '#2D2D31'
fontcolor: '#C4C4C4'
monobackgroundcolor: '#3B3B3B'
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Analysis

## Import initiation file

```{r}
source('368_initiation.R')
```


Define number of bootstrap simulations per model

```{r}
nsim = 21000
quantils = c(0.2, 0.5, 0.8)
```


All children models will be adjusted for the effect of `log2_age` (when applicable, i.e. not for age-adjusted Anthropometric data), `SEX`, `aBreastFeed_full_stopped`, `aBreastFeed_total_stopped`, and `aBreastFeed_full_duration` (the interaction of the latter with duration of the dependence on the breastfeeding). Additional covariates (relevant supplementation for vitamins and biogenic elements levels) or birth weight (anthropometric data) will be added as covariates.

```{r}
AIC_child_all <- data.frame(outcome = NA,
                            estimand = NA,
                            log2_age = NA,
                            aSEX = NA,
                            Breast_Feed = NA,
                            other_cov = NA,
                            diet = NA)

diet_child_all <- data.frame(outcome = NA,
                             estimand = NA,
                             VN_OM_diff = NA, 
                             VN_OM_P = NA,
                             VG_OM_diff = NA, 
                             VG_OM_P = NA,
                             VN_VG_diff = NA, 
                             VN_VG_P = NA)

i = 1
j = 1
ni= 10
```

## Quantile regression

### aMASS_Perc

Data selection

```{r, fig.height=7, fig.width=7}

## data selection
column_name <- names(dat_child_all)[i+ni]

AIC_child_all$outcome[i] <- column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
     SEX + 
     GRP +
     aBiW +
     #s(log2_age)
     s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aMASS_Perc_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_1 <- kbl(res, caption = 
      'Suppl. Table 1. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of body mass. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_1
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA
  # rqfit(exclude = c('log2_age'), include = 'aBiW')
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aHEIGHT_Perc

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    #s(log2_age)
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aHEIGHT_Perc_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_2 <- kbl(res, caption = 
      'Suppl. Table 2. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of body height. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_2
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(exclude = c('log2_age'))


### model without log2_age
mod_log2_age <- NA
  # rqfit(exclude = c('log2_age'), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aBMI_PERC

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    #s(log2_age)
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aBMI_PERC_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_3 <- kbl(res, caption = 
      'Suppl. Table 3. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of BMI. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_3
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA
  # rqfit(exclude = c('log2_age'), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aM_per_H_PERC`

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    #s(log2_age)
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aM_per_H_PERC_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_4 <- kbl(res, caption = 
      'Suppl. Table 4. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of percentile of weight to height ratio. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_4
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA
  # rqfit(exclude = c('log2_age'), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aGLY`

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aGLY_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_5 <- kbl(res, caption = 
      'Suppl. Table 5. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of glycemia. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_5
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aTC`

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aTC_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_6 <- kbl(res, caption = 
      'Suppl. Table 6. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of total cholesterol. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_6
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aHDL

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Diagnostic plot looks better now, but the difference in not huge. We will use original values to unify it with LDL analysis where transformation is unsuitable.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aHDL_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_7 <- kbl(res, caption = 
      'Suppl. Table 7. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of HDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_7
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aLDL

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aLDL_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_8 <- kbl(res, caption = 
      'Suppl. Table 8. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of LDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_8
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aTG

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aTG_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_9 <- kbl(res, caption = 
      'Suppl. Table 9. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(TG cholecterol) levels. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_9
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aCa

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca)) 


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Ca'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aCa_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_10 <- kbl(res, caption = 
      'Suppl. Table 10. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Ca level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_10
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Ca')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Ca')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Ca')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Ca')

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aP

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aP_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_11 <- kbl(res, caption = 
      'Suppl. Table 11. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum P level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_11
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aMg

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Mg)) 

```


GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Mg +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Mg'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aMg_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_12 <- kbl(res, caption = 
      'Suppl. Table 12. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Mg level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_12
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Mg')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Mg')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Mg')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Mg')

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aSe

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]


dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Diagnostics does not show a sign of an improvement

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 

mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Se'))

## bootstrapping of main model

mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aSe_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_13 <- kbl(res, caption = 
      'Suppl. Table 13. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile serum Se level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_13

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Se')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Se')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Se')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Se')

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aZn

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn)) 


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Zn +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 

mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Zn'))

## bootstrapping of main model

mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aZn_boot', reuse = TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_14 <- kbl(res, caption = 
      'Suppl. Table 14. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Zn level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_14

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Zn')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Zn')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Zn')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Zn')

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aFE

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aFe_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_15 <- kbl(res, caption = 
      'Suppl. Table 15. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Fe level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_15
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aVKFE

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aVKFE_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_16 <- kbl(res, caption = 
      'Suppl. Table 16. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum ferritin Fe binding capacity. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_16
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aFERR

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. It seems that the `aFERR` change in multiplicative, rather than additive way. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aFERR_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_17 <- kbl(res, caption = 
      'Suppl. Table 17. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(serum ferritin) levels. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_17
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aTRF

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aTRF_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_18 <- kbl(res, caption = 
      'Suppl. Table 18. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum transferin level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_18
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aSATTRF

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aSATTRF_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_19 <- kbl(res, caption = 
      'Suppl. Table 19. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of transferin saturation. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')

suppl_table_19
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aTRFINDEX

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aTRFINDEX_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_20 <- kbl(res, caption = 
      'Suppl. Table 20. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of sTfR index (log2-ratio). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_20
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aSTRF

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation slightly improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aSTRF_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_21 <- kbl(res, caption = 
      'Suppl. Table 21. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(soluble transferin receptor level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_21
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aHGB

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aHGB_boot', reuse = TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_22 <- kbl(res, caption = 
      'Suppl. Table 22. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of hemoglobin level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_22

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aMCV

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aMVC_boot', reuse = TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_23 <- kbl(res, caption = 
      'Suppl. Table 23. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of mean corpuscular volume. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_23

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aPTH

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aPTH_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_24 <- kbl(res, caption = 
      'Suppl. Table 24. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of parathormone level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_24
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aCros

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D)) 


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Ca', 'aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aCros_boot', reuse = TRUE)



## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_25 <- kbl(res, caption = 
      'Suppl. Table 25. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(beta cross laps). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_25
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = c('aSUP_Ca', 'aSUP_D'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = c('aSUP_Ca', 'aSUP_D'))

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = c('aSUP_Ca', 'aSUP_D'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aP1NP

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Ca', 'aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aP1NP_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_26 <- kbl(res, caption = 
      'Suppl. Table 26. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of procollagen type I level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_26

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = c('aSUP_Ca', 'aSUP_D'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = c('aSUP_Ca', 'aSUP_D'))

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = c('aSUP_Ca', 'aSUP_D'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aUI

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c())

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aUI_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_27 <- kbl(res, caption = 
      'Suppl. Table 27. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of urinary iodine level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_27

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without supplementation
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aUREA

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name),
         log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome))  
  
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(include = 'log2_age_2')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aUREA_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_28 <- kbl(res, caption = 
      'Suppl. Table 28. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of urea level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_28
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = c('log2_age_2'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),
                 include = c('log2_age_2'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),
                   include = c('log2_age_2'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aCREA

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aCREA_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_29 <- kbl(res, caption = 
      'Suppl. Table 29. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(creatinine) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_29
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aUA

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aUA_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_30 <- kbl(res, caption = 
      'Suppl. Table 30. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of uric acid level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_30
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aVIT_AKTB12

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name),
         log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12)) 


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age_2) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age_2) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aSup_B12', 'log2_age_2'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aVIT_AKTB12_boot', reuse = TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_31 <- kbl(res, caption = 
      'Suppl. Table 31. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(vitamin B12) serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_31

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX', 'log2_age'), 
                  include = c('aSup_B12', 'log2_age_2'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration','log2_age'),  
                 include = c('aSup_B12', 'log2_age_2'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP','log2_age'),
                   include = c('aSup_B12', 'log2_age_2'))

### model without supplementation
mod_other_cov <- rqfit(exclude=c('log2_age'), include=c('log2_age_2'))

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSup_B12')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aHCY

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aHCY_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_32 <- kbl(res, caption = 
      'Suppl. Table 32. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(homocysteine) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_32
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aMMA

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. Even though it's not perfect we will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_all_aMMA_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_33 <- kbl(res, caption = 
      'Suppl. Table 33. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(methylmalonic acid) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_33
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```

### aVIT_D

Data selection

```{r, fig.height=7, fig.width=7}

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_D)) 


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aVIT_D_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_34 <- kbl(res, caption = 
      'Suppl. Table 34. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(vitamin D) serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_34
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_D')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_D')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_D')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_D')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aFOLAT

Data selection

```{r, fig.height=7, fig.width=7}

ni = 10

column_name <- names(dat_child_all)[i+ni]
column_name 

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_FOL))


```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_FOL +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_FOL'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aFOLAT_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_35 <- kbl(res, caption = 
      'Suppl. Table 35. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of folate serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_35
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'), include = 'aSUP_FOL')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_FOL')

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'),include = 'aSUP_FOL')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'), include = 'aSUP_FOL')

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1 
```

### aIGF1

Data selection

```{r, fig.height=7, fig.width=7}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_all_aIGF1_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_36 <- kbl(res, caption = 
      'Suppl. Table 36. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(growth factor) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  add_header_above(c(' ' = 1, '(A) 20th quantile' = 4, 
                     '(B) Median' = 4, '(C) 80th quantile' = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_36
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c('GRP'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c('log2_age'))

```

Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all)

diet_child_all <- add_eff(diet_child_all, res)

i = i+1
```


### Save tables

```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_child_all.xlsx') == FALSE){
  diet_child_all <- diet_child_all[-1,]
  
  diet_child_all$VN_OM_P_adj <- NA
  diet_child_all$VG_OM_P_adj <- NA
  diet_child_all$VN_VG_P_adj <- NA
  
for (i in seq(1, nrow(diet_child_all), by = 3)) {
  padj <- p.adjust(c(
    diet_child_all$VN_OM_P[i], 
    diet_child_all$VN_OM_P[i+1],
    diet_child_all$VN_OM_P[i+2],
    
    diet_child_all$VG_OM_P[i],
    diet_child_all$VG_OM_P[i+1],
    diet_child_all$VG_OM_P[i+2],
    
    diet_child_all$VN_VG_P[i],
    diet_child_all$VN_VG_P[i+1],
    diet_child_all$VN_VG_P[i+2]), method = 'hochberg')
  
  diet_child_all$VN_OM_P_adj[i:(i+2)] <- padj[1:3]
  diet_child_all$VG_OM_P_adj[i:(i+2)] <- padj[4:6]
  diet_child_all$VN_VG_P_adj[i:(i+2)] <- padj[7:9]
}
  
  
  diet_child_all <- diet_child_all %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) %>% 
    mutate(across(.cols = c(VN_OM_P, VG_OM_P, VN_VG_P,
                            VN_OM_P_adj, VG_OM_P_adj, VN_VG_P_adj), ~ round(.x, 5)))

  write.xlsx(diet_child_all, 'gitignore/data/diet_child_all.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_child_all.xlsx') == FALSE){
  AIC_child_all <- AIC_child_all[-1,]
  write.xlsx(AIC_child_all, 'gitignore/data/AIC_child_all.xlsx')
  }

```



# Reproducibility

```{r}
sessionInfo()
```
