---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: 'Statistical report - mixed-effects models in all children'
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: 'Open code'
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: '#2D2D31'
fontcolor: '#C4C4C4'
monobackgroundcolor: '#3B3B3B'
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Analysis

## Import initiation file

```{r, warning=FALSE}
source('368_initiation.R')
```


## Mixed models

All children models will be adjusted for the effect of `log2_age` (when applicable, i.e. not for age-adjusted Anthropometric data), `SEX`, `aBreastFeed_full_stopped`, `aBreastFeed_total_stopped`, and `aBreastFeed_full_duration` (the interaction of the latter with duration of the dependence on the breastfeeding). Additional covariates (relevant supplementation for vitamins and biogenic elements levels) or birth weight (anthropometric data) will be added as covariates.

```{r}
AIC_child_all <- data.frame(outcome = NA,
                            estimand = 'mean',
                            log2_age = NA,
                            aSEX = NA,
                            Breast_Feed = NA,
                            other_cov = NA,
                            diet = NA,
                            family = NA)

diet_child_all <- data.frame(outcome = NA,
                         estimand = NA,
                         VN_OM_diff = NA, 
                         VN_OM_P = NA,
                         VG_OM_diff = NA, 
                         VG_OM_P = NA,
                         VN_VG_diff = NA, 
                         VN_VG_P = NA)

i = 1
j = 1
ni= 10
```

### aMASS_Perc

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name


```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of age-standardized percentile of body mass. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'))

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aHEIGHT_Perc

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```


Fit main model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)
  
suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects regression modelling of age-standardized percentile of body height. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'))

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'))


### model without log2_age
mod_log2_age <- NA
  # rlme(exclude = c('log2_age'), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aBMI_PERC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name


```


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of age-standardized percentile of BMI. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'))

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aM_per_H_PERC

Data selection


```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name


```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of age-standardized percentile of weight to height ratio. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'))

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aGLY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]



dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name


```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of glycemia. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aTC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of total cholesterol. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aHDL


Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of HDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aLDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of LDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aTG

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of TG cholesterol level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aCa

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Ca'), 
       remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of of serum Ca level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Ca'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Ca'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca'),
		 exclude = c('GRP'))

### model without suplementaion
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Ca'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, 
       remove_random = FALSE),
  
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum P level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aMg

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Mg))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Mg'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of of serum Mg level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Mg'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Mg'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Mg'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Mg'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Mg'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Mg'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aSe

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Se'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum Se level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Se'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Se'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Se'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Se'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Se'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Se'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```


### aZn

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn))

column_name

```
Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Zn'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum Zn level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Zn'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Zn'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Zn'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Zn'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Zn'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Zn'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum Fe level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'), 
                   remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'), 
                 exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aVKFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum ferritin Fe binding capacity. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(
  include = c('aSUP_Fe'),
  exclude = c('aBreastFeed_full_stopped',
              'aBreastFeed_total_stopped',
              'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aFERR

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(
  res, 
  caption =
    'Results of linear mixed-effects model of serum ferritin levels. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),
                   remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),
                 exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,
       include = c('aSUP_Fe'),
       remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum transferin level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(
  include = c('aSUP_Fe'),
  exclude = c('aBreastFeed_full_stopped',
		          'aBreastFeed_total_stopped',
		          'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aSATTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]



dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of transferin saturation. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aTRFINDEX

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)


## main model 
mod_main <- run(
  rlme(main = TRUE,
       include = c('aSUP_Fe'), 
       remove_random = FALSE),
  
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of TRF index. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aSTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(soluble transferin receptor level). CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aHGB

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of hemoglobin level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aMCV

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of mean corpuscular volume. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aPTH

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of parathormone level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=TRUE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aCros

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D)) 

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Ca', 'aSUP_D'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(beta cross laps). CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca', 'aSUP_D'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Ca', 'aSUP_D'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca', 'aSUP_D'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aP1NP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D)) 

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_Ca', 'aSUP_D'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of procollagen type I level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca', 'aSUP_D'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Ca', 'aSUP_D'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca', 'aSUP_D'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aUI

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]



dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of urinary iodine level . CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aUREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name),
 	log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, include = c('log2_age_2'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of urea level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('log2_age_2'),remove_random = TRUE)

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('log2_age_2'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('log2_age_2'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('log2_age_2'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without log2_age_2
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
		  include = c('log2_age_2'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aCREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(creatinine) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aUA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of uric acid level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aVIT_AKTB12

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name),
 	log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome),
	!is.na(aSup_B12))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE,  include = c('log2_age_2', 'aSup_B12'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(active vitamin B12) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('log2_age_2', 'aSup_B12'))

### model  without random effect
mod_nonran <- rlme(include = c('log2_age_2', 'aSup_B12'),
                   remove_random = TRUE)

### model without sex
mod_nsex <- rlme( include = c('log2_age_2', 'aSup_B12'),
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(
  include = c('log2_age_2', 'aSup_B12'),
  exclude = c('aBreastFeed_full_stopped',
		          'aBreastFeed_total_stopped',
              'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(
  include = c('log2_age_2', 'aSup_B12'),
  exclude = c('GRP'))

### model without other cov - log2_age_2 and supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(
  exclude = c('log2_age'),
  include = c('log2_age_2', 'aSup_B12'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aHCY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(homocysteine) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aMMA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(methylmalonic acid) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aVIT_D

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_D))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_D'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(vitamin D serum) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_D'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_D'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_D'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_D'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_D'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aFOLAT

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_FOL))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  rlme(main = TRUE,include = c('aSUP_FOL'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of folate serum level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_FOL'))

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_FOL'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_FOL'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_FOL'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_FOL'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_FOL'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)

i = i+1
```

### aIGF1

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(growth factor) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)
```


### Save tables

```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_child_all_mixeff.xlsx') == FALSE){
  diet_child_all <- diet_child_all[-1,]
  
  diet_child_all$VN_OM_P_adj <- NA
  diet_child_all$VG_OM_P_adj <- NA
  diet_child_all$VN_VG_P_adj <- NA
  
for (i in seq(1, nrow(diet_child_all))) {
  padj <- p.adjust(c(
    diet_child_all$VN_OM_P[i], 
    diet_child_all$VG_OM_P[i],
    diet_child_all$VN_VG_P[i]), 
    method = 'hochberg')
  
  diet_child_all$VN_OM_P_adj[i] <- padj[1]
  diet_child_all$VG_OM_P_adj[i] <- padj[2]
  diet_child_all$VN_VG_P_adj[i] <- padj[3]
}
  
  diet_child_all <- diet_child_all %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) %>% 
    mutate(across(.cols = c(VN_OM_P, VG_OM_P, VN_VG_P,
                            VN_OM_P_adj, VG_OM_P_adj, VN_VG_P_adj), ~ round(.x, 5)))

  write.xlsx(diet_child_all, 'gitignore/data/diet_child_all_mixeff.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_child_all_mixeff.xlsx') == FALSE){
  AIC_child_all <- AIC_child_all[-1,]
  write.xlsx(AIC_child_all, 'gitignore/data/AIC_child_all_mixeff.xlsx')
  }
```



# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
