---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: "Statistical report - data wrangling and exploration"
author: "Cahova et al."
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: "Open code"
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
fontcolor: "#C4C4C4"
monobackgroundcolor: "#3B3B3B"
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Analysis

## Import initiation file

```{r}
source('368_initiation.R')
```


## Subject characteristics table

### All children characteristics table

Comparison of clinical outcomes across diet groups in children

#### Overall

```{r, warning=FALSE, message=FALSE}

DatChar_child_all <- run(
  dat_child_all_tosum %>% 
    select(-FAM, -ID) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')
              ) %>%
    modify_caption("Supplementary Table 1. Children characteristics according to food preferences, all children") %>% 
    add_p() %>% 
    add_q(),
  
  path = 'gitignore/run/DatChar_child_all', reuse = TRUE)


DatChar_child_all

DatChar_child_all_df <- DatChar_child_all$table_body %>%
  as_tibble()
```

#### OM vs VG

```{r, warning=FALSE}

DatChar_child_all_OM_VG <- run(
  dat_child_all_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'OM' | GRP == 'VG') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    modify_caption("OM vs VG, all children") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
   path = 'gitignore/run/DatChar_child_all_OM_VG', reuse=TRUE)

DatChar_child_all_OM_VG
```


#### OM vs VG

```{r, warning=FALSE}

DatChar_child_all_OM_VN <- run(
  dat_child_all_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'OM' | GRP == 'VN') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    modify_caption("OM vs VN, only children >3 year all included") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
   path = 'gitignore/run/DatChar_child_all_OM_VN', reuse=TRUE)

DatChar_child_all_OM_VN
```

#### VG vs VN

```{r, warning=FALSE}

DatChar_child_all_VG_VN <- run(
  dat_child_all_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'VG' | GRP == 'VN') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    modify_caption("VG vs VN, only children >3 year all included") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
   path = 'gitignore/run/DatChar_child_all_VG_VN', reuse=TRUE)

DatChar_child_all_VG_VN
```

### Children >3 y.o. characteristics table

#### Overall

```{r, warning=FALSE}

DatChar_child_old <- run(
  dat_child_old_tosum %>% 
    select(-FAM, -ID) %>% 
    tbl_summary(
      by='GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
  
      modify_caption("Supplementary Table 2. Children characteristics according to food preferences, with only children >3 year old included") %>% 
    
    add_p() %>% 
    add_q(),
  
  path = 'gitignore/run/DatChar_child_old', reuse=TRUE)

DatChar_child_old

DatChar_child_old_df <- DatChar_child_old$table_body %>%
  as_tibble()
```

#### OM vs VG

```{r, warning=FALSE}

DatChar_child_old_OM_VG <- run(
  dat_child_old_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'OM' | GRP == 'VG') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    modify_caption("OM vs VG, only children >3 year old included") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
   path = 'gitignore/run/DatChar_child_old_OM_VG', reuse=TRUE)

DatChar_child_old_OM_VG
```


#### OM vs VN

```{r, warning=FALSE}

DatChar_child_old_OM_VN <- run(
  dat_child_old_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'OM' | GRP == 'VN') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    modify_caption("OM vs VN, only children >3 year old included") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
   path = 'gitignore/run/DatChar_child_old_OM_VN', reuse=TRUE)

DatChar_child_old_OM_VN
```

#### VG vs VN

```{r, warning=FALSE}

DatChar_child_old_VG_VN <- run(
  dat_child_old_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'VG' | GRP == 'VN') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    modify_caption("VG vs VN, only children >3 year old included") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
   path = 'gitignore/run/DatChar_child_old_VG_VN', reuse=TRUE)

DatChar_child_old_VG_VN
```


### Children <3 y.o. characteristics table

#### Overall

```{r, warning=FALSE}

DatChar_child_young <- run(
  dat_child_young_tosum %>%
    select(-FAM, -ID) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    
    modify_caption("Supplementary Table 3. Children characteristics according to food preferences, with only children <3 year old included") %>% 
    add_p() %>% 
    add_q(),
  path = 'gitignore/run/DatChar_child_young', reuse=TRUE)

DatChar_child_young

DatChar_child_young_df <- DatChar_child_young$table_body %>%
  as_tibble()
```


#### OM vs VG

```{r, warning=FALSE}

DatChar_child_young_OM_VG <- run(
  dat_child_young_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'OM' | GRP == 'VG') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    
    modify_caption("OM vs VG, with only children <3 year old included") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
  path = 'gitignore/run/DatChar_child_young_OM_VG', reuse=TRUE)

DatChar_child_young_OM_VG
```


#### OM vs VN

```{r, warning=FALSE}

DatChar_child_young_OM_VN <- run(
  dat_child_young_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'OM' | GRP == 'VN') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    
    modify_caption("OM vs VN, with only children <3 year old included") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
  path = 'gitignore/run/DatChar_child_young_OM_VN', reuse=TRUE)

DatChar_child_young_OM_VN
```


#### VG vs VN

```{r, warning=FALSE}

DatChar_child_young_VG_VN <- run(
  dat_child_young_tosum %>%
    select(-FAM, -ID) %>%
    filter(GRP == 'VG' | GRP == 'VN') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(
      by = 'GRP',
      type = list(
        aBreastFeed_full ~ 'continuous',
        aBreastFeed_total ~ 'continuous')) %>%
    
    modify_caption("VG vs VN, with only children <3 year old included") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
  path = 'gitignore/run/DatChar_child_young_VG_VN', reuse=TRUE)

DatChar_child_young_VG_VN
```


### Adults characteristics table

Comparison of clinical outcomes across diet groups in adults

#### Overall

```{r, collapse=TRUE}
DatChar_adult <- run(
  dat_adult %>% 
    select(-FAM, -ID) %>% 
    tbl_summary(by = 'GRP') %>%
    modify_caption("Supplementary Table 4. Adults characteristics according to food preferences") %>% 
    add_p() %>% 
    add_q(),
  
  path = 'gitignore/run/DatChar_adult', reuse=TRUE)

DatChar_adult

DatChar_adult_df <- DatChar_adult$table_body %>%
  as_tibble()
```


#### OM vs VG

```{r, collapse=TRUE}
DatChar_adult_OM_VG <- run(
  dat_adult %>% 
    select(-FAM, -ID) %>% 
    filter(GRP == 'OM' | GRP == 'VG') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(by = 'GRP') %>%
    modify_caption("OM vs VG. Adults characteristics according to food preferences") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
  
  path = 'gitignore/run/DatChar_adult_OM_VG', reuse=TRUE)

DatChar_adult_OM_VG
```


#### OM vs VN

```{r, collapse=TRUE}
DatChar_adult_OM_VN <- run(
  dat_adult %>% 
    select(-FAM, -ID) %>% 
    filter(GRP == 'OM' | GRP == 'VN') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(by = 'GRP') %>%
    modify_caption("OM vs VN. Adults characteristics according to food preferences") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
  
  path = 'gitignore/run/DatChar_adult_OM_VN', reuse=TRUE)

DatChar_adult_OM_VN
```


#### VG vs VN

```{r, collapse=TRUE}
DatChar_adult_VG_VN <- run(
  dat_adult %>% 
    select(-FAM, -ID) %>% 
    filter(GRP == 'VG' | GRP == 'VN') %>%
    mutate(GRP = factor(GRP)) %>% 
    tbl_summary(by = 'GRP') %>%
    modify_caption("VG vs VN. Adults characteristics according to food preferences") %>% 
    add_p() %>% 
    add_q() %>% 
    as_gt(),
  
  path = 'gitignore/run/DatChar_adult_VG_VN', reuse=TRUE)

DatChar_adult_VG_VN
```


## Distribution of numerical characteristics

### All children histograms

```{r, fig.height=12, fig.width=11, warning=FALSE}
## Reshaping the data to long format
dat_long <- dat_child_all

dat_long <- dat_long %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3)) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, levels = names(dat_long)))

# Creating the histogram matrix
ggplot(dat_long, aes(x = value)) +
  geom_histogram(bins = 20, fill = "skyblue2", color = "grey60") +
  facet_wrap(~ variable, scales = "free") +
  labs(x = "Value", y = "Count", title = "Histogram of Numerical Variables, all children")
```

### Young children histograms

```{r, fig.height=12, fig.width=11, warning=FALSE, collapse=TRUE}
## Reshaping the data to long format
dat_long <- dat_child_young

dat_long <- dat_long %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3)) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, levels = names(dat_long)))

# Creating the histogram matrix
ggplot(dat_long, aes(x = value)) +
  geom_histogram(bins = 20, fill = "skyblue2", color = "grey60") +
  facet_wrap(~ variable, scales = "free") +
  labs(x = "Value", y = "Count", title = "Histogram of Numerical Variables, young children")
```


### Old children histograms

```{r, fig.height=12, fig.width=11, warning=FALSE, collapse=TRUE}
## Reshaping the data to long format
dat_long <- dat_child_old

dat_long <- dat_long %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3)) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, levels = names(dat_long)))

# Creating the histogram matrix
ggplot(dat_long, aes(x = value)) +
  geom_histogram(bins = 20, fill = "skyblue2", color = "grey60") +
  facet_wrap(~ variable, scales = "free") +
  labs(x = "Value", y = "Count", title = "Histogram of Numerical Variables, old children")

```

### Adults histograms

```{r, fig.height=12, fig.width=11, warning=FALSE, collapse=TRUE}
## Reshaping the data to long format
dat_long <- dat_adult

dat_long <- dat_long %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3)) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>% 
  mutate(variable = factor(variable, levels = names(dat_long)))

# Creating the histogram matrix
ggplot(dat_long, aes(x = value)) +
  geom_histogram(bins = 20, fill = "skyblue2", color = "grey61") +
  facet_wrap(~ variable, scales = "free") +
  labs(x = "Value", y = "Count", title = "Histogram of Numerical Variables, adults ")

```

## Plot of group characteristics

### All children

```{r, fig.height=12, fig.width=12, warning=FALSE}
## define color
colo <- c('#F9FFAF', '#ACE1A3', '#329243')

## prepare data
df <- dat_child_all

tr <- DatChar_child_all_df %>% 
  filter(!is.na(q.value)) %>% 
  select(variable, q.value)

df <- df %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3) | GRP) 

## define outcomes of interest
outcomes <- data.frame(
  variable = setdiff(names(df), c(
    'GRP', 
    'log2_age', 
    'aBreastFeed_full_duration')))
  
outcomes <- outcomes %>% 
  inner_join(tr, by = 'variable')
  
## define comparison
my_comparisons <- list( c('OM', 'VG'), c('OM', 'VN'), c('VG', 'VN') )

## function to boxplot
boxplot_cond <- function(variable, q.value) {
  
  clean_data <- df %>%
    select(GRP, all_of(variable)) %>%
    drop_na()
  
  upper_limit <- max(clean_data[[variable]], na.rm = TRUE) * 1.5
  
  p <- ggboxplot(clean_data, 
                 x = 'GRP', 
                 y = variable, 
                 fill = 'GRP', 
                 tip.length = 0.15,
                 palette = colo,
                 outlier.shape = 1,
                 lwd = 0.25,
                 outlier.size = 0.8) +
    
    theme(
      plot.title = element_text(size = 10),   # Smaller title
      axis.title = element_text(size = 8),    # Smaller axis titles
      axis.text = element_text(size = 7)      # Smaller axis labels
    ) +
    
    rremove("legend") +
    
    coord_cartesian(ylim = c(0, upper_limit))
  
  if (q.value < 0.05) {
    p <- p + stat_compare_means(
      method = 'wilcox.test',
      label = 'P',
      comparisons = my_comparisons,
      size = 3,
      label.y = upper_limit * c(0.7, 0.8, 0.9))
  }
  
  return(p)
}

# Plot all outcomes
plots <- pmap(outcomes, boxplot_cond)

# Arrange plots in a matrix
plots_arranged <- ggarrange(plotlist = plots, ncol = 8, nrow = 5)
plots_arranged

```


### Young children

```{r, fig.height=12, fig.width=12, warning=FALSE}
## data
df <- dat_child_young

df <- df %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3) | GRP) 

## defining outcomes of interest
tr <- DatChar_child_young_df %>% 
  filter(!is.na(q.value)) %>% 
  select(variable, q.value)

df <- df %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3) | GRP) 

## define outcomes of interest
outcomes <- data.frame(
  variable = setdiff(names(df), c(
    'GRP', 
    'log2_age', 
    'aBreastFeed_full_duration')))
  
outcomes <- outcomes %>% 
  inner_join(tr, by = 'variable')

## plot all outcomes
plots <- pmap(outcomes, boxplot_cond)

## matrix of plot
plots_arranged <- ggarrange(plotlist = plots, ncol = 8, nrow = 5)
plots_arranged

```


### Old children

```{r, fig.height=12, fig.width=12, warning=FALSE}
## data
df <- dat_child_old

df <- df %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3) | GRP) 

## defining outcomes of interest
tr <- DatChar_child_old_df %>% 
  filter(!is.na(q.value)) %>% 
  select(variable, q.value)

df <- df %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3) | GRP) 

## define outcomes of interest
outcomes <- data.frame(
  variable = setdiff(names(df), c(
    'GRP', 
    'log2_age', 
    'aBreastFeed_full_duration')))
  
outcomes <- outcomes %>% 
  inner_join(tr, by = 'variable')

## plot all outcomes
plots <- pmap(outcomes, boxplot_cond)

## matrix of plot
plots_arranged <- ggarrange(plotlist = plots, ncol = 8, nrow = 5)
plots_arranged

```

### Adults

```{r, fig.height=13, fig.width=11, warning=FALSE}
## data
df <- dat_adult

df <- df %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3) | GRP) %>% 
  select(-aCros)

## defining outcomes of interest
tr <- DatChar_adult_df %>% 
  filter(!is.na(q.value)) %>% 
  select(variable, q.value)

df <- df %>% 
  select(where(~is.numeric(.)  && length(unique(.)) >3) | GRP) 

## define outcomes of interest
outcomes <- data.frame(
  variable = setdiff(names(df), c(
    'GRP', 
    'log2_age')))

outcomes <- outcomes %>% 
  inner_join(tr, by = 'variable')

## plot all outcomes
plots <- pmap(outcomes, boxplot_cond)

## matrix of plot
plots_arranged <- ggarrange(plotlist = plots, ncol = 7, nrow = 6)
plots_arranged

```


# Food intake summary 

```{r}
dat_food %>% summary()
```

## Summary tables

### Children all

```{r}
food_int_child_all <- run(
  dat_food %>%
    filter(Age_category != 'Adult') %>% 
    select(-Age_category) %>% 
    tbl_summary(
      by = 'GRP') %>%
    modify_caption("Nutrients intake in children (all)") %>% 
    add_p() %>% 
    add_q(),
  
  path = 'gitignore/run/food_int_child_all', reuse = TRUE)


food_int_child_all

food_int_child_all_df <- food_int_child_all$table_body %>%
  as_tibble()
```

### Children young

```{r}
food_int_child_young <- run(
  dat_food %>%
    filter(Age_category == 'Ch < 3 yrs') %>% 
    select(-Age_category) %>% 
    tbl_summary(
      by = 'GRP') %>%
    modify_caption("Nutrients intake in children < 3 years of age") %>% 
    add_p() %>% 
    add_q(),
  
  path = 'gitignore/run/food_int_child_young', reuse = TRUE)


food_int_child_young

food_int_child_young_df <- food_int_child_young$table_body %>%
  as_tibble()
```


### Children old

```{r}
food_int_child_old <- run(
  dat_food %>%
    filter(Age_category == 'Ch > 3 yrs') %>% 
    select(-Age_category) %>% 
    tbl_summary(
      by = 'GRP') %>%
    modify_caption("Nutrients intake in children of 3+ years of age") %>% 
    add_p() %>% 
    add_q(),
  
  path = 'gitignore/run/food_int_child_old', reuse = TRUE)


food_int_child_old

food_int_child_old_df <- food_int_child_old$table_body %>%
  as_tibble()
```


### Adults

```{r}
food_int_adult <- run(
  dat_food %>%
    filter(Age_category == 'Adult') %>% 
    select(-Age_category) %>% 
    tbl_summary(
      by = 'GRP') %>%
    modify_caption("Nutrients intake in adults") %>% 
    add_p() %>% 
    add_q(),
  
  path = 'gitignore/run/food_int_adult', reuse = TRUE)


food_int_adult

food_int_adult_df <- food_int_adult$table_body %>%
  as_tibble()
```

## Plots of nutrient intake

Preparation

```{r, fig.height=12, fig.width=12, warning=FALSE}
## define color
colo <- c('#329243', '#ACE1A3', '#F9FFAF')

## prepare data
df <- dat_food %>% 
  mutate(Age_category2 = recode(Age_category,
                  `Ch > 3 yrs` = 'child_old',
                  `Ch < 3 yrs` = 'child_young')) %>% 
  
  mutate(super_group = interaction(GRP, Age_category2)) %>% 
  
  mutate(super_group = fct_relevel(
    super_group, 
    'OM.child_young', 'VG.child_young', 'VN.child_young',
    'OM.child_old', 'VG.child_old', 'VN.child_old',
    'OM.adult', 'VG.adult', 'VN.adult')) %>% 
  
  mutate(GRP = fct_relevel(
    GRP, 
    'VN', 'VG', 'OM')) %>% 
  
  mutate(Age_category = fct_relevel(
    Age_category, 
    'Ch < 3 yrs', 'Ch > 3 yrs', 'adult'))
    
                              
## define outcomes of interest

outcomes <- data.frame(
  variable = df %>% 
    select(Calories.kcal.:Iodine.μg.) %>% 
    colnames())

outcomes <- outcomes %>% 
  mutate(
    title = str_extract(variable, "^[^.]+"),
    y_title = str_extract(variable, "(?<=\\.).*") %>% 
                     str_replace_all("\\.", "/day")
  )

outcomes$title[1] <- 'Energy'
outcomes$title[7] <- 'Saturate fats'
outcomes$y_title[7] <- 'g/day'
```

Boxplot

```{r, fig.height=10, fig.width=13, warning=FALSE}
## function to boxplot
boxplot_cond <- function(variable, y_title, title) {
  
  clean_data <- df %>%
    select(Age_category, GRP, super_group,  variable) %>%
    drop_na()
  
  upper_limit <- max(clean_data[[variable]]) * 1.3
  
  p <- ggboxplot(clean_data, 
                 x = 'GRP', 
                 y = variable, 
                 fill = 'GRP', 
                 tip.length = 0.15,
                 palette = colo,
                 outlier.shape = 1,
                 lwd = 0.25,
                 outlier.size = 0.8,
                 facet.by = 'Age_category',
                 title = title,
                 ylab = y_title) +
    
    theme(
      plot.title = element_text(size = 10), 
      axis.title = element_text(size = 8),  
      axis.text = element_text(size = 7),
      axis.title.x = element_blank()
    ) +
  
    coord_cartesian(ylim = c(NA, upper_limit))

  return(p)
}

# Plot all outcomes
plots <- pmap(outcomes, boxplot_cond)

# Create a matrix of plots
plots_arranged <- ggarrange(plotlist = plots, ncol = 4, nrow = 4,  common.legend = TRUE)
plots_arranged

path <- paste0('gitignore/figures/plots_arranged.pdf')

if(file.exists(path) == FALSE){
  ggsave(path, 
         plot = plots_arranged,
         width = 13, height = 10,
         device = cairo_pdf)
}

path <- paste0('gitignore/figures/plots_arranged.tiff')
if(file.exists(path) == FALSE){
  tiff(path, width = 13, height = 10, units = 'in', res = 400) 
  grid.draw(plots_arranged)
  dev.off()
}

```


# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
