---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: 'Statistical report - mixed effects models in old children'
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: 'Open code'
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: '#2D2D31'
fontcolor: '#C4C4C4'
monobackgroundcolor: '#3B3B3B'
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Analysis

## Import initiation file

```{r}
source('368_initiation.R')
```


## Mixed models

Old children models will be adjusted for the effect of `log2_age` (when applicable, i.e. not for age-adjusted Anthropometric data), `SEX`, `aBreastFeed_total_stopped`, and `aBreastFeed_full_duration` (the duration of the dependence on the breastfeeding). Additional covariates (relevant supplementation for vitamins and biogenic elements levels) or birth weight (anthropometric data) will be added as covariates.


```{r}
AIC_child_old <- data.frame(outcome = NA,
                            estimand = 'mean',
                            log2_age = NA,
                            aSEX = NA,
                            Breast_Feed = NA,
                            other_cov = NA,
                            diet = NA,
                            family = NA)

diet_child_old <- data.frame(outcome = NA,
                         estimand = NA,
                         VN_OM_diff = NA, 
                         VN_OM_P = NA,
                         VG_OM_diff = NA, 
                         VG_OM_P = NA,
                         VN_VG_diff = NA, 
                         VN_VG_P = NA)

i = 1
j = 1
ni= 10
```


### aMASS_Perc

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  rlme(main = TRUE, 
       exclude = c('log2_age'),
       include = c('aBiW'), 
       remove_random = FALSE,
       type = 'child_old'),
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on age-standardized percentile of body mass, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                 include = c('aBiW'),
                 type = 'child_old')

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'),
                    type = 'child_old', 
                    remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), 
                 include = 'aBiW',
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW',
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), 
                  include = 'aBiW',
                  type = 'child_old')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'),
                      type = 'child_old')

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```


### aHEIGHT_Perc

Data selection

```{r, fig.height=7, fig.width=7}


column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       exclude = c('log2_age'),
       include = c('aBiW'), 
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on age-standardized percentile of body height, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                 include = c('aBiW'),
                 type = 'child_old')

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), 
                    remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), 
                 include = 'aBiW',
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             
                             'aBreastFeed_full_duration'),  
                include = 'aBiW',
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), 
                  include = 'aBiW',
                  type = 'child_old')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'),
                      type = 'child_old')

### model without log2_age
mod_log2_age <- NA
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```


### aBMI_PERC

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       exclude = c('log2_age'),
       include = c('aBiW'), 
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on age-standardized percentile of body mass index, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                 include = c('aBiW'),
                 type = 'child_old')

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), 
                    remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), 
                 include = 'aBiW',
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             
                             'aBreastFeed_full_duration'),  
                include = 'aBiW',
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), 
                  include = 'aBiW',
                  type = 'child_old')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'),
                      type = 'child_old')

### model without log2_age
mod_log2_age <- NA
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aM_per_H_PERC

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       exclude = c('log2_age'),
       include = c('aBiW'), 
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on age-standardized percentile of mass to height ratio, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                 include = c('aBiW'),
                 type = 'child_old')

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), 
                    remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), 
                 include = 'aBiW',
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             
                             'aBreastFeed_full_duration'),  
                include = 'aBiW',
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), 
                  include = 'aBiW',
                  type = 'child_old')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'),
                      type = 'child_old')

### model without log2_age
mod_log2_age <- NA
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aGLY

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on glycemia level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```


### aTC

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on total cholesterol, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aHDL

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on HDL cholesterol level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aLDL

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on LDL cholesterol level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aTG

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```


Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log(TG cholesterol) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aCa

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca)) 
```


Fit main model

```{r, fig.height=5, fig.width=5}


## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Ca')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on plasma calcium level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Ca'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Ca'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Ca'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Ca'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Ca'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Ca'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_old)[i+ni]

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on plasma phosphorus level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c( 'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aMg

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Mg)) 

```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Mg')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, Mgption = 
      'The effect of diet on plasma magnesium level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Mg'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Mg'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Mg'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Mg'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Mg'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Mg'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aSe

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]


dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5}


## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Se')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on plasma selenium level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Se'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Se'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Se'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Se'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Se'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Se'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aZn

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn)) 


```

Fit main model

```{r, fig.height=5, fig.width=5}


## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Zn')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on plasma zinc level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Zn'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Zn'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Zn'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Zn'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Zn'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Zn'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aFE

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on iron level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Fe'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Fe'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Fe'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Fe'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aVKFE

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum ferritin Fe binding capacity, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Fe'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Fe'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Fe'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Fe'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aFERR

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(serum ferritin) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Fe'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Fe'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Fe'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Fe'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aTRF

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum transferrin level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Fe'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Fe'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Fe'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Fe'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aSATTRF

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on transferin saturation, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Fe'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Fe'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Fe'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Fe'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aTRFINDEX

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum log2(sTRF) index, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Fe'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Fe'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Fe'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Fe'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aSTRF

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Fe')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum log2(soluble transferin receptor) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Fe'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Fe'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Fe'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Fe'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Fe'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Fe'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aHGB

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on hemoglobin level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aMCV

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on mean corpuscular volume, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aPTH

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on parathyroid hormone level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                    type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aCros

Data selection

```{r, fig.height=7, fig.width=7}
column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D)) 
```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Ca', 'aSUP_D')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(beta-CrossLaps) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Ca', 'aSUP_D'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Ca', 'aSUP_D'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Ca', 'aSUP_D'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Ca', 'aSUP_D'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Ca', 'aSUP_D'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aP1NP

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_Ca', 'aSUP_D')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on pro-collagen type I level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_Ca', 'aSUP_D'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   include = c('aSUP_Ca', 'aSUP_D'),
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old',
                include = c('aSUP_Ca', 'aSUP_D'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_Ca', 'aSUP_D'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_Ca', 'aSUP_D'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aUI

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 


```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on urinary iodine level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aUREA

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))  
  
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on urea level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aCREA

Data selection

```{r, fig.height=7, fig.width=7}


column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(creatinine) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aUA

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}
## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on uric acid level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aVIT_AKTB12

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name),
         log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12)) 


```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSup_B12')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(vitamine B12) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSup_B12'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old',
                   include = c('aSup_B12'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSup_B12'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                include = c('aSup_B12'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old',
                  include = c('aSup_B12'))

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSup_B12'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aHCY

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(homocystein) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aMMA

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(methylmalonic acid) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aVIT_D

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_D)) 


```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_D')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(vitamine D) level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_D'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old',
                   include = c('aSUP_D'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                include = c('aSUP_D'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_D'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_D'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aFOLAT

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name 

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_FOL))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old',
       include = c('aSUP_FOL')),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on folate level, estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old',
                 include = c('aSUP_FOL'))

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old',
                   include = c('aSUP_FOL'))

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old',
                 include = c('aSUP_FOL'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                include = c('aSUP_FOL'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  include = c('aSUP_FOL'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- rlme(type = 'child_old')

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     include = c('aSUP_FOL'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

i = i+1
```

### aIGF1

Data selection

```{r, fig.height=7, fig.width=7}

column_name <- names(dat_child_old)[i+ni]
column_name

dat_mod <- dat_child_old %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

Fit main model

```{r, fig.height=5, fig.width=5}

## log2-transform the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,
       remove_random = FALSE,
       type = 'child_old'),
  
  path = paste0('gitignore/run/mod_child_old_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(inzulin like growth factor-1), estimated with a robust linear mixed-effects model in children aged over 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped', full_width = TRUE) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(type = 'child_old')

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE,
                   type = 'child_old')

### model without sex
mod_nsex <- rlme(exclude = c('SEX'), 
                 type = 'child_old')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = 
                  c(
                    'aBreastFeed_full_duration'),
                type = 'child_old')

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  type = 'child_old')

### model without other covariates
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
                     type = 'child_old')
```

Putting key results together

```{r}

## AIC

AIC_child_old <- add_AIC(AIC_child_old, mixef = TRUE)

diet_child_old <- add_eff(diet_child_old, res, mixef = TRUE)

```



### Saving tables

```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_child_old_mixeff.xlsx') == FALSE){
  diet_child_old <- diet_child_old[-1,]
  
  diet_child_old$VN_OM_P_adj <- NA
  diet_child_old$VG_OM_P_adj <- NA
  diet_child_old$VN_VG_P_adj <- NA
  
for (i in seq(1, nrow(diet_child_old))) {
  padj <- p.adjust(c(
    diet_child_old$VN_OM_P[i], 
    diet_child_old$VG_OM_P[i],
    diet_child_old$VN_VG_P[i]), 
    method = 'hochberg')
  
  diet_child_old$VN_OM_P_adj[i] <- padj[1]
  diet_child_old$VG_OM_P_adj[i] <- padj[2]
  diet_child_old$VN_VG_P_adj[i] <- padj[3]
}
  
  diet_child_old <- diet_child_old %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) %>% 
    mutate(across(.cols = c(VN_OM_P, VG_OM_P, VN_VG_P,
                            VN_OM_P_adj, VG_OM_P_adj, VN_VG_P_adj), ~ round(.x, 5)))

  write.xlsx(diet_child_old, 'gitignore/data/diet_child_old_mixeff.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_child_old_mixeff.xlsx') == FALSE){
  AIC_child_old <- AIC_child_old[-1,]
  write.xlsx(AIC_child_old, 'gitignore/data/AIC_child_old_mixeff.xlsx')
  }
```

# Reproducibility

```{r}
sessionInfo()
```
