---
title: 'Clinical data, KOMPAS'
subtitle: 'Statistical report - mixed-effects models in young children'
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: 'Open code'
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: '#2D2D31'
fontcolor: '#C4C4C4'
monobackgroundcolor: '#3B3B3B'
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Analysis

## Import initiation file

```{r}
source('368_initiation.R')
```


## Linear models

Young children models will be adjusted for the effect of `log2_age` (when applicable, i.e. not for age-adjusted Anthropometric data)), `SEX`, `aBreastFeed_full_stopped`, `aBreastFeed_total_stopped`, and `aBreastFeed_full_duration` (the interaction of the latter with duration of the dependence on the breastfeeding). Additional covariates (relevant supplementation for vitamins and biogenic elements levels) or birth weight (anthropometric data) were added as covariates.

```{r}
AIC_child_young <- data.frame(outcome = NA,
                            estimand = 'mean',
                            log2_age = NA,
                            aSEX = NA,
                            Breast_Feed = NA,
                            other_cov = NA,
                            diet = NA,
                            family = NA)

diet_child_young <- data.frame(outcome = NA,
                         estimand = NA,
                         VN_OM_diff = NA, 
                         VN_OM_P = NA,
                         VG_OM_diff = NA, 
                         VG_OM_P = NA,
                         VN_VG_diff = NA, 
                         VN_VG_P = NA)

i = 1
j = 1
ni= 10
```


### aMASS_Perc

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       exclude = c('log2_age'),
       include = c('aBiW'), 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on age-standardized percentile of body mass, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'),
                 remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), 
                 include = 'aBiW',
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                include = 'aBiW',
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'),
                  include = 'aBiW',
                  remove_random = TRUE)

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'),
                      remove_random = TRUE)

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```


### aHEIGHT_Perc

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(
  res, 
  caption = 'The effect of diet on age-standardized percentile of body height, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                 include = c('aBiW'),
                 remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                include = 'aBiW',
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), 
                  include = 'aBiW',
                  remove_random = TRUE)

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'),
                      remove_random = TRUE)

### model without log2_age
mod_log2_age <- NA
```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```


### aBMI_PERC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       exclude = c('log2_age'),
       include = c('aBiW'), 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on age-standardized percentile of BMI, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'),
                 remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), 
                 include = 'aBiW',
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                include = 'aBiW',
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'),
                  include = 'aBiW',
                  remove_random = TRUE)

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'),
                      remove_random = TRUE)

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aM_per_H_PERC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       exclude = c('log2_age'),
       include = c('aBiW'), 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on age-standardized percentile of percentile of weight to height ratio, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'),
                 remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), 
                 include = 'aBiW',
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                include = 'aBiW',
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'),
                  include = 'aBiW',
                  remove_random = TRUE)

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'),
                      remove_random = TRUE)

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aGLY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on glycemia, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aTC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]



dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on total cholesterol, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aHDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]



dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on HDL cholesterol level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aLDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]



dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on LDL cholesterol level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aTG

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]



dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on TG cholesterol level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aCa

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
	!is.na(aSUP_Ca))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Ca'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum Ca level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Ca'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca'),
		              exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		                 include = c('aSUP_Ca'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum P level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aMg 

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum Mg level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(
		exclude = c('aBreastFeed_full_stopped',
                'aBreastFeed_total_stopped',
                'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(
		 exclude = c('GRP'),
		 remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
                     remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aSe

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Se'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum Se level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Se'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Se'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Se'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Se'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Se'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aZn

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Zn'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum Zn level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Zn'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Zn'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Zn'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Zn'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Zn'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]



dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Fe'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum Fe level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Fe'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aVKFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Fe'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum ferritin Fe binding capacity, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Fe'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aFERR

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Fe'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log(serum ferritin level), estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Fe'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aTRF

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Fe'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on serum tranferin level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Fe'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aSATTRF

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Fe'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on tranferin saturation, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Fe'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aTRFINDEX

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Fe'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on sTfR index (log2-ratio), estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Fe'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aSTRF

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_Fe'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(soluble transferin receptor level), estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Fe'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aHGB

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on hemoglobin level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aMCV

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on mean corpuscular volume, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aPTH

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on parathormone level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aCros

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE,  include = c('aSUP_Ca', 'aSUP_D'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(beta cross laps), estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca', 'aSUP_D'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme( include = c('aSUP_Ca', 'aSUP_D'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme( include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(
  include = c('aSUP_Ca', 'aSUP_D'),
  exclude = c('GRP'),
  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Ca', 'aSUP_D'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aP1NP

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}


## main model 
mod_main <- run(
  
  rlme(main = TRUE,  include = c('aSUP_Ca', 'aSUP_D'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on procollagen type I level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca', 'aSUP_D'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme( include = c('aSUP_Ca', 'aSUP_D'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme( include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_Ca', 'aSUP_D'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aUI

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}


## main model 
mod_main <- run(
  
  rlme(main = TRUE,  
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on urinary iodine level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(
		exclude = c('aBreastFeed_full_stopped',
                'aBreastFeed_total_stopped',
                'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(
  exclude = c('GRP'),
  remove_random = TRUE)

### model without supplementation
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
                     remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aUREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name),
         log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome))  

column_name  
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}


## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('log2_age_2'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on urea level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('log2_age_2'),
                 remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('log2_age_2'),
                 exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('log2_age_2'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'),
		remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(
  include = c('log2_age_2'),
  exclude = c('GRP'),
  remove_random = TRUE)

mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
                     remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aCREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(creatinine) level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
                     remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aUA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]



dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on uric acid level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aVIT_AKTB12

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name),
         log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12)) 

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       include = c('log2_age_2', 'aSup_B12'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(vitamin B12) serum level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('log2_age_2', 'aSup_B12'),
                 remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme( include = c('log2_age_2', 'aSup_B12'),
                  exclude = c('SEX'),
                  remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme( include = c('log2_age_2', 'aSup_B12'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('log2_age_2', 'aSup_B12'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov - log2_age_2 and supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('log2_age_2', 'aSup_B12'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aHCY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(homocysteine) level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aMMA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(methylmalonic acid) level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
                     remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aVIT_D

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_D))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       include = c('aSUP_D'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(vitamin D) serum level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_D'),
                 remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_D'),
                 exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_D'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(
  exclude = c("log2_age"),
  include = c('aSUP_D'),
  remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aFOLAT

Data selection 

```{r, fig.height=7, fig.width=7, collapse=TRUE}

column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_FOL))

column_name

```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}


## main model 
mod_main <- run(
  
  rlme(main = TRUE, include = c('aSUP_FOL'),
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on folate serum level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_FOL'),remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(include = c('aSUP_FOL'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_FOL'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_FOL'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without supplementation
mod_other_cov <- rlme(remove_random = TRUE)

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),
		  include = c('aSUP_FOL'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)

i = i+1
```

### aIGF1

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

Fit main model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  
  rlme(main = TRUE, 
       remove_random = TRUE),
  
  path = paste0('gitignore/run/mod_child_young_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]
icc(mod_main)

res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'The effect of diet on log2(growth factor) level, estimated with a robust linear model in children < 3 years. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(remove_random = TRUE)

### model  without random effect
mod_nonran <- NA

### model without sex
mod_nsex <- rlme(exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'),
                  remove_random = TRUE)

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c("log2_age"),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young, mixef = TRUE)

diet_child_young <- add_eff(diet_child_young, res, mixef = TRUE)
```


## Saving tables


```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_child_young_mixeff.xlsx') == FALSE){
  diet_child_young <- diet_child_young[-1,]
  
  diet_child_young$VN_OM_P_adj <- NA
  diet_child_young$VG_OM_P_adj <- NA
  diet_child_young$VN_VG_P_adj <- NA
  
for (i in seq(1, nrow(diet_child_young))) {
  padj <- p.adjust(c(
    diet_child_young$VN_OM_P[i], 
    diet_child_young$VG_OM_P[i],
    diet_child_young$VN_VG_P[i]), 
    method = 'hochberg')
  
  diet_child_young$VN_OM_P_adj[i] <- padj[1]
  diet_child_young$VG_OM_P_adj[i] <- padj[2]
  diet_child_young$VN_VG_P_adj[i] <- padj[3]
}
  
  diet_child_young <- diet_child_young %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) %>% 
    mutate(across(.cols = c(VN_OM_P, VG_OM_P, VN_VG_P,
                            VN_OM_P_adj, VG_OM_P_adj, VN_VG_P_adj), ~ round(.x, 5)))

  write.xlsx(diet_child_young, 'gitignore/data/diet_child_young_mixeff.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_child_young_mixeff.xlsx') == FALSE){
  AIC_child_young <- AIC_child_young[-1,]
  write.xlsx(AIC_child_young, 'gitignore/data/AIC_child_young_mixeff.xlsx')
  }
```


# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
