---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: "Statistical report - quantile regression in young children"
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: "Open code"
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
fontcolor: "#C4C4C4"
monobackgroundcolor: "#3B3B3B"
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

{{< include README.md >}}

# Analysis

## Import initiation file

```{r}
source('368_initiation.R')
```


Define number of bootstrap simulations per model

```{r}
nsim = 21000
quantils = c(0.2, 0.5, 0.8)
```

Young children models will be adjusted for the effect of `log2_age` (when applicable, i.e. not for age-adjusted Anthropometric data)), `SEX`, `aBreastFeed_full_stopped`, `aBreastFeed_total_stopped`, and `aBreastFeed_full_duration` (the interaction of the latter with duration of the dependence on the breastfeeding). Additional covariates (relevant supplementation for vitamins and biogenic elements levels) or birth weight (anthropometric data) were added as covariates.

```{r}
AIC_child_young <- data.frame(outcome = NA,
                            estimand = NA,
                            log2_age = NA,
                            aSEX = NA,
                            Breast_Feed = NA,
                            other_cov = NA,
                            diet = NA)

diet_child_young <- data.frame(outcome = NA,
                             estimand = NA,
                             VN_OM_diff = NA, 
                             VN_OM_P = NA,
                             VG_OM_diff = NA, 
                             VG_OM_P = NA,
                             VN_VG_diff = NA, 
                             VN_VG_P = NA)

i = 1
j = 1
ni= 10
```

## Individual models

### aMASS_Perc

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_child_young)[i+ni]

AIC_child_young$outcome[i] <- column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
     SEX + 
     GRP +
     aBiW, 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aMASS_Perc_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_37 <- kbl(res, caption = 
      "Suppl. Table 37. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of body mass. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_37
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("log2_age", "SEX"), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("log2_age",
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("log2_age", "GRP"), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(exclude = c("log2_age"))

### model without log2_age
mod_log2_age <- NA
  # rqfit(exclude = c("log2_age"), include = 'aBiW')
```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aHEIGHT_Perc

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW 
    #+
    #s(log2_age)
    # s(FAM, bs="re")
  , 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aHEIGHT_Perc_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_38 <- kbl(res, caption = 
      "Suppl. Table 38. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of body height. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_38
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("log2_age", "SEX"), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("log2_age",
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("log2_age", "GRP"), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(exclude = c("log2_age"))


### model without log2_age
mod_log2_age <- NA
  # rqfit(exclude = c("log2_age"), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aBMI_PERC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW, 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aBMI_PERC_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_39 <- kbl(res, caption = 
      "Suppl. Table 39. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of BMI. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_39
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("log2_age", "SEX"), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("log2_age",
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("log2_age", "GRP"), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(exclude = c("log2_age"))

### model without log2_age
mod_log2_age <- NA
  # rqfit(exclude = c("log2_age"), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aM_per_H_PERC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))
```

GAMM

```{r, fig.height=5, fig.width=5, warning=FALSE, message=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW, 
  data = dat_mod)

summary(gamm)
anova(gamm)
#plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c('log2_age'),
                    include = c('aBiW'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aM_per_H_PERC_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_40 <- kbl(res, caption = 
      "Suppl. Table 40. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of age-standardized percentile of percentile of weight to height ratio. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_40
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("log2_age", "SEX"), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("log2_age",
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("log2_age", "GRP"), include = 'aBiW')

### model without birth weight
mod_other_cov <- rqfit(exclude = c("log2_age"))

### model without log2_age
mod_log2_age <- NA
  # rqfit(exclude = c("log2_age"), include = 'aBiW')

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aGLY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aGLY_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_41 <- kbl(res, caption = 
      "Suppl. Table 41. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of glycemia. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_41
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aTC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aTC_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_42 <- kbl(res, caption = 
      "Suppl. Table 42. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of total cholesterol. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_42
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aHDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) 
  #+
  #s(FAM, bs="re")
  , 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) 
  #+
  #s(FAM, bs="re")
  , 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aHDL_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_43 <- kbl(res, caption = 
      "Suppl. Table 43. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of HDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_43
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aLDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit, original was much better. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aLDL_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_44 <- kbl(res, caption = 
      "Suppl. Table 44. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of LDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_44
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aTG

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aTG_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_45 <- kbl(res, caption = 
      "Suppl. Table 45. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(TG cholecterol) levels. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_45
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aCa

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Ca'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aCa_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_46 <- kbl(res, caption = 
      "Suppl. Table 46. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Ca level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_46
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Ca')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Ca')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Ca')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Ca')

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aP_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_47 <- kbl(res, caption = 
      "Suppl. Table 47. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum P level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_47
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aMg

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 

```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
dat_mod <- dat_mod %>%
      mutate(across(where(is.numeric), ~ jitter(.x)))

mod_main <- rqfit(exclude = c())

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aMg_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_48 <- kbl(res, caption = 
      "Suppl. Table 48. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Mg level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_48
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without supplementation
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aSe

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]


dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Diagnostics does not show a sign of an improvement

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 

mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Se'))

## bootstrapping of main model

mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aSe_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_49 <- kbl(res, caption = 
      "Suppl. Table 49. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile serum Se level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_49

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Se')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Se')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Se')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Se')

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aZn

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Zn +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 

mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Zn'))

## bootstrapping of main model

mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aZn_boot', reuse=TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_50 <- kbl(res, caption = 
      "Suppl. Table 50. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Zn level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_50

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Zn')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Zn')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Zn')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Zn')

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aFe_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_51 <- kbl(res, caption = 
      "Suppl. Table 51. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Fe level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_51
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aVKFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aVKFE_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_52 <- kbl(res, caption = 
      "Suppl. Table 52. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum ferritin Fe binding capacity. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_52
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aFERR

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. It seems that the `aFERR` change in multiplicative, rather than additive way. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aFERR_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_53 <- kbl(res, caption = 
      "Suppl. Table 53. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(serum ferritin) levels. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_53
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_54 <- kbl(res, caption = 
      "Suppl. Table 54. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum transferin level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_54
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aSATTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aSATTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_55 <- kbl(res, caption = 
      "Suppl. Table 55. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of transferin saturation. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')

suppl_table_55
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aTRFINDEX

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) , 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aTRFINDEX_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_56 <- kbl(res, caption = 
      "Suppl. Table 56. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of sTfR index (log2-ratio). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_56
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aSTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation slightly improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Fe'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aSTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_57 <- kbl(res, caption = 
      "Suppl. Table 57. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(soluble transferin receptor level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_57
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_Fe')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_Fe')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_Fe')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_Fe')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aHGB

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aHGB_boot', reuse=TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_58 <- kbl(res, caption = 
      "Suppl. Table 58. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of hemoglobin level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_58

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aMCV

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aMVC_boot', reuse=TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_59 <- kbl(res, caption = 
      "Suppl. Table 59. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of mean corpuscular volume. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_59

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aPTH

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aPTH_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_60 <- kbl(res, caption = 
      "Suppl. Table 60. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of parathormone level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_60
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aCros

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Ca', 'aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aCros_boot', reuse=TRUE)



## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_61 <- kbl(res, caption = 
      "Suppl. Table 61. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(beta cross laps). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_61
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = c('aSUP_Ca', 'aSUP_D'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = c('aSUP_Ca', 'aSUP_D'))

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = c('aSUP_Ca', 'aSUP_D'))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aP1NP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_Ca', 'aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aP1NP_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_62 <- kbl(res, caption = 
      "Suppl. Table 62. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of procollagen type I level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_62

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = c('aSUP_Ca', 'aSUP_D'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = c('aSUP_Ca', 'aSUP_D'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = c('aSUP_Ca', 'aSUP_D'))

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = c('aSUP_Ca', 'aSUP_D'))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aUI

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c())

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aUI_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_63 <- kbl(res, caption = 
      "Suppl. Table 63. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of urinary iodine level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_63

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without supplementation
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aUREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name),
         log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome))  
  
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age),
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(include = 'log2_age_2')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aUREA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_64 <- kbl(res, caption = 
      "Suppl. Table 64. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of urea level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_64
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"),
                  include = c('log2_age_2'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),
                 include = c('log2_age_2'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),
                    include = c('log2_age_2'))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aCREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(aAGE),
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(aAGE),
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aCREA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_65 <- kbl(res, caption = 
      "Suppl. Table 65. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(creatinine) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_65
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}

## AIC

AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aUA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aUA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_66 <- kbl(res, caption = 
      "Suppl. Table 66. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of uric acid level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_66
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aVIT_AKTB12

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name),
         log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age_2),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age_2),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model ERROR

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(exclude = c("log2_age"),
                    include = c('aSup_B12', 'log2_age_2'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aVIT_AKTB12_boot', reuse=TRUE)


## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_67 <- kbl(res, caption = 
      "Suppl. Table 67. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(vitamin B12) serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_67

```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX","log2_age"), 
                  include = c('aSup_B12', 'log2_age_2'))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration',"log2_age"),  
                 include = c('aSup_B12', 'log2_age_2'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),
                   include = c('aSup_B12', 'log2_age_2'))

### model without supplementation
mod_other_cov <- rqfit(exclude="log2_age", include = 'log2_age_2')

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSup_B12')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aHCY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aHCY_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_68 <- kbl(res, caption = 
      "Suppl. Table 68. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(homocysteine) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_68
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aMMA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. Even though it's not perfect we will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter=TRUE),
  path = 'gitignore/run/mod_child_young_aMMA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_69 <- kbl(res, caption = 
      "Suppl. Table 69. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(methylmalonic acid) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_69
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```

### aVIT_D

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_D)) 


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_D +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_D +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_D'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aVIT_D_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_70 <- kbl(res, caption = 
      "Suppl. Table 70. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(vitamin D) serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_70
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_D')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_D')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_D')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_D')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aFOLAT

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name 

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_FOL))


```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_FOL +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(exclude = c(),
                    include = c('aSUP_FOL'))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aFOLAT_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_71 <- kbl(res, caption = 
      "Suppl. Table 71. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of folate serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_71
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"), include = 'aSUP_FOL')

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c(
                             "aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'),  
                 include = 'aSUP_FOL')

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"),include = 'aSUP_FOL')

### model without supplementation
mod_other_cov <- rqfit()

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"), include = 'aSUP_FOL')

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1 
```

### aIGF1

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection

ni= 10

column_name <- names(dat_child_young)[i+ni]
column_name

dat_mod <- dat_child_young %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age),
     
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit()

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_child_young_aIGF1_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)
  
suppl_table_72 <- kbl(res, caption = 
      "Suppl. Table 72. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(growth factor) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_72
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(exclude = c("SEX"))

### model without breastfeeding-related predictors
mod_nbf <- rqfit(exclude = c("aBreastFeed_full_stopped",
                             "aBreastFeed_total_stopped",
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rqfit(exclude = c("GRP"))

### model without birth weight
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rqfit(exclude = c("log2_age"))

```

Putting key results together

```{r}
AIC_child_young <- add_AIC(AIC_child_young)

diet_child_young <- add_eff(diet_child_young, res)

i = i+1
```


### Saving tables


```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_child_young.xlsx') == FALSE){
  diet_child_young <- diet_child_young[-1,]
  
  diet_child_young$VN_OM_P_adj <- NA
  diet_child_young$VG_OM_P_adj <- NA
  diet_child_young$VN_VG_P_adj <- NA
  
for (i in seq(1, nrow(diet_child_young), by = 3)) {
  padj <- p.adjust(c(
    diet_child_young$VN_OM_P[i], 
    diet_child_young$VN_OM_P[i+1],
    diet_child_young$VN_OM_P[i+2],
    
    diet_child_young$VG_OM_P[i],
    diet_child_young$VG_OM_P[i+1],
    diet_child_young$VG_OM_P[i+2],
    
    diet_child_young$VN_VG_P[i],
    diet_child_young$VN_VG_P[i+1],
    diet_child_young$VN_VG_P[i+2]), method = 'hochberg')
  
  diet_child_young$VN_OM_P_adj[i:(i+2)] <- padj[1:3]
  diet_child_young$VG_OM_P_adj[i:(i+2)] <- padj[4:6]
  diet_child_young$VN_VG_P_adj[i:(i+2)] <- padj[7:9]
}
  
  
  diet_child_young <- diet_child_young %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) %>% 
    mutate(across(.cols = c(VN_OM_P, VG_OM_P, VN_VG_P,
                            VN_OM_P_adj, VG_OM_P_adj, VN_VG_P_adj), ~ round(.x, 5)))

  write.xlsx(diet_child_young, 'gitignore/data/diet_child_young.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_child_young.xlsx') == FALSE){
  AIC_child_young <- AIC_child_young[-1,]
  write.xlsx(AIC_child_young, 'gitignore/data/AIC_child_young.xlsx')
  }
```


# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
