---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: "Statistical report - quantile regression in adults"
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: "Open code"
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
fontcolor: "#C4C4C4"
monobackgroundcolor: "#3B3B3B"
bibliography: references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.85em;
  border: 1px solid #ffffff; /* White border */
  padding: 20px; /* Add padding for better visibility */
}

code{
    color: #EEE8AA; /* Change the color value as needed */
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}

```

------------------------------------------------------------------------

{{< include README.md >}}

# Analysis

## Import initiation file

```{r}
source('368_initiation.R')
```


## Quantile regression

Define number of bootstrap simulations per model

```{r}
nsim = 21000
quantils = c(0.2, 0.5, 0.8)
```

Adults models will be adjusted for the effect of `aAGE`, `SEX`. Relevant supplementation for vitamins and biogenic elements will be added as covariates.

```{r}
AIC_adult <- data.frame(outcome = NA,
                        estimand = NA,
                        aAGE = NA,
                        aSEX = NA,
                        other_cov = NA,
                        diet = NA)

diet_adult <- data.frame(outcome = NA,
                         estimand = NA,
                         VN_OM_diff = NA, 
                         VN_OM_P = NA,
                         VG_OM_diff = NA, 
                         VG_OM_P = NA,
                         VN_VG_diff = NA, 
                         VN_VG_P = NA)

i <-  1
j <-  1
ni <-  5
```

### aBMI

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

No large difference

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aBMI_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_109 <- kbl(res, caption = 
                        "Suppl. Table 109. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of BMI. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_109
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aWHR

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aWHR_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_110 <- kbl(res, caption = 
                        "Suppl. Table 110. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of waist-to-hip ratio. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_110
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aHEIGHT

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aHEIGHT_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_111 <- kbl(res, caption = 
                        "Suppl. Table 111. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of body height. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_111
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aMASS

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

No large difference. We will keep original values for the sake of simple interpretability

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aMASS_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_112 <- kbl(res, caption = 
                        "Suppl. Table 112. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of body mass. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_112
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aHG

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aHG_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_113 <- kbl(res, caption = 
                        "Suppl. Table 113. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of hand grip. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_113
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aPFAT

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

With log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aPFAT_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1, nround=3)
res_tab_q50 <- exte(mod_boot, nquantile = 2,nround=3)
res_tab_q80 <- exte(mod_boot, nquantile = 3, nround=3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_114 <- kbl(res, caption = 
                        "Suppl. Table 114. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of percentile of body fat. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_114
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aFAT

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

With log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Looks much better after log2-transformation of the outcome variable

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aFAT_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1, nround=5)
res_tab_q50 <- exte(mod_boot, nquantile = 2, nround=5)
res_tab_q80 <- exte(mod_boot, nquantile = 3, nround=5)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_115 <- kbl(res, caption = 
                        "Suppl. Table 115. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(body fat). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_115
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aFFM

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Looks much better with log-2transformed outcome variable

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aFFM_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1, nround=3)
res_tab_q50 <- exte(mod_boot, nquantile = 2, nround=3)
res_tab_q80 <- exte(mod_boot, nquantile = 3, nround=3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_116 <- kbl(res, caption = 
                        "Suppl. Table 116. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(free fat mass) . CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_116
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aSBP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)
### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim, jitter = TRUE),
  path = 'gitignore/run/mod_adult_aSBP_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_117 <- kbl(res, caption = 
                        "Suppl. Table 117. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of systolic blood pressure. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_117
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aDBP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aDBP_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_118 <- kbl(res, caption = 
                        "Suppl. Table 118. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of diastolic blood pressure. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_118
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aGLY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformation of the outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log2 transformation did not improve the fit


Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aGLY_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_119 <- kbl(res, caption = 
                        "Suppl. Table 119. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of glycemia. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_119
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aTC

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aTC_Perc_boot', reuse = TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_120 <- kbl(res, caption = 
                        "Suppl. Table 120. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile log2(total cholesterol). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_120
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aHDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aHDL_Perc_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_121 <- kbl(res, caption = 
                        "Suppl. Table 121. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of HDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_121
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aLDL

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aLDL_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_122 <- kbl(res, caption = 
                        "Suppl. Table 122. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of LDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_122
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aTG

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aTG_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_123 <- kbl(res, caption = 
                        "Suppl. Table 123. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(TG cholesterol) level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_123
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aCa

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Ca + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Ca"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aCa_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_124 <- kbl(res, caption = 
                        "Suppl. Table 124. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Ca level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_124
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Ca"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Ca"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Ca"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aP_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_125 <- kbl(res, caption = 
                        "Suppl. Table 125. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum P level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_125
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aMg

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Mg)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Mg + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Mg"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aMg_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_126 <- kbl(res, caption = 
                        "Suppl. Table 126. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Mg level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_126
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Mg"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Mg"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',
                  include= c("aSUP_Mg"),
                  exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aSe

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Se + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Se"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aSe_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_127 <- kbl(res, caption = 
                        "Suppl. Table 127. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Se level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_127
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Se"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Se"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Se"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aZn

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Zn + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - better

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Zn + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Zn"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aZn_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_128 <- kbl(res, caption = 
                        "Suppl. Table 128. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(serum Zn level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_128
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Zn"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Zn"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Zn"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log2-transformation did not improve it

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Fe"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aFe_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_129 <- kbl(res, caption = 
                        "Suppl. Table 129. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of serum Fe level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_129
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Fe"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aVKFE

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Slightly better

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Fe"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aVKFE_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_130 <- kbl(res, caption = 
                        "Suppl. Table 130. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(serum ferritin Fe binding capacity). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_130
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Fe"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

```

### aFERR


Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - better

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Much better after outcome transformation

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE, warning=FALSE, message=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)


## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Fe"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aFERR_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_131 <- kbl(res, caption = 
                        "Suppl. Table 131. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(serum ferritin level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_131
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Fe"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - better

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Much better after the outcome transformation

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Fe"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_132 <- kbl(res, caption = 
                        "Suppl. Table 132. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(serum transferin level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_132
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Fe"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aSATTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - not better

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

The outcome transformation did not help

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Fe"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aSATTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_133 <- kbl(res, caption = 
                        "Suppl. Table 133. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of transferin saturation. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_133
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Fe"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aTRFINDEX

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - better

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Fe"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aTRFINDEX_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_134 <- kbl(res, caption = 
                        "Suppl. Table 134. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of sTfR index (log2-ratio). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_134
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', 
                  include= c("aSUP_Fe"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   include= c("aSUP_Fe"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',
                  include= c("aSUP_Fe"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aSTRF

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - not better -VYMAZAT OUTLIER?

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Fe + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

May be slightly better

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)


## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Fe"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aSTRF_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_135 <- kbl(res, caption = 
                        "Suppl. Table 135. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(soluble transferin receptor level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_135
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_Fe"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_Fe"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aHGB

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aHGB_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_136 <- kbl(res, caption = 
                        "Suppl. Table 136. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of hemoglobin level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_136
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aMCV

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aMCV_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_137 <- kbl(res, caption = 
                        "Suppl. Table 137. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of mean corpuscular volume. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_137
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aPTH

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

No substantially better

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

# dat_mod$outcome <- log2(dat_mod$outcome)
# column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aPTH_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_138 <- kbl(res, caption = 
                        "Suppl. Table 138. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of parathormone level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_138
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aCros

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca), 
         !is.na(aSUP_D)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Ca + 
    aSUP_D +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - better

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Ca + 
    aSUP_D +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Ca", "aSUP_D"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aCros_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_139 <- kbl(res, caption = 
                        "Suppl. Table 139. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(beta cross laps). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_139
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include=c("aSUP_Ca", "aSUP_D"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include=c("aSUP_Ca", "aSUP_D"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include=c("aSUP_Ca", "aSUP_D"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aP1NP

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca), 
         !is.na(aSUP_D)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_Ca + 
    aSUP_D +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - better

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_Ca + 
    aSUP_D +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_Ca", "aSUP_D"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aP1NP_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_140 <- kbl(res, caption = 
                        "Suppl. Table 140. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(procollagen type I level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_140
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include=c("aSUP_Ca", "aSUP_D"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include=c("aSUP_Ca", "aSUP_D"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include=c("aSUP_Ca", "aSUP_D"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aUI

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. Even though it is not perfect we will continue to work with original values.

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aUI_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_141 <- kbl(res, caption = 
                        "Suppl. Table 141. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(urinary iodine level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_141
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                  exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aUREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aUREA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_142 <- kbl(res, caption = 
                        "Suppl. Table 142. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(urea level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_142
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aCREA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aCREA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_143 <- kbl(res, caption = 
                        "Suppl. Table 143. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(creatinine level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_143
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aUA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aUA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_144 <- kbl(res, caption = 
                        "Suppl. Table 144. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of uric acid level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_144
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aVIT_AKTB12

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSup_B12 + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSup_B12 + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSup_B12"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aVIT_AKTB12_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_145 <- kbl(res, caption = 
                        "Suppl. Table 145. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(vitamin B12 level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_145
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSup_B12"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSup_B12"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSup_B12"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aHCY

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

log2 outcome - not better

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation slightly improved the fit. As log2 transformation was used in children category, ee will continue to work with log-transformed values.

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)
## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aHCY_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_146 <- kbl(res, caption = 
                        "Suppl. Table 146. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(homocysteine). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_146
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aMMA

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Try log2-transformation

```{r, fig.height=5, fig.width=5, collapse=TRUE}
gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Much better now

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## Log-transformation of the outcome
dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult')

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aMMA_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_147 <- kbl(res, caption = 
                        "Suppl. Table 147. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of methylmalonic acid level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_147
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult',
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',
                   exclude = c("GRP"))

### model without other
mod_other_cov <- NA

### model without age
mod_age <-  rqfit(type = 'adult',
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aVIT_D

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_D)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_D + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_D + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}


dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_D"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aVIT_D_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_148 <- kbl(res, caption = 
                        "Suppl. Table 148. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of log2(vitamin D level). CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_148
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_D"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_D"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_D"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```

### aFOLAT

Data selection

```{r, fig.height=7, fig.width=7, collapse=TRUE}

## data selection
column_name <- names(dat_adult)[i+ni]

#AIC_adult$outcome[i] <- column_name

dat_mod <- dat_adult %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_FOL)) 

column_name
```

GAMM

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  outcome ~ 
    SEX + 
    GRP +
    aSUP_FOL + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again but with log2-transformed outcome

```{r, fig.height=5, fig.width=5, collapse=TRUE}

gamm <- gam(
  log2(outcome) ~ 
    SEX + 
    GRP +
    aSUP_FOL + 
    s(aAGE) +
    s(FAM, bs="re"), 
  data = dat_mod)

summary(gamm)
anova(gamm)

plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Quantile model

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## main model 
mod_main <- rqfit(type = 'adult', include=c("aSUP_FOL"))

## bootstrapping of main model
mod_boot <- run(
  clust_boot(mod_main, seed= 16, R = nsim),
  path = 'gitignore/run/mod_adult_aFOLAT_boot', reuse=TRUE)

## extract sampled coefficients and create resulting table
res_tab_q20 <- exte(mod_boot, nquantile = 1)
res_tab_q50 <- exte(mod_boot, nquantile = 2)
res_tab_q80 <- exte(mod_boot, nquantile = 3)

## combining the results into a single table
res <- cbind(res_tab_q20,res_tab_q50, res_tab_q80)

suppl_table_149 <- kbl(res, caption = 
                        "Suppl. Table 149. Results of quantile regression, modelling (A) 20th quantile, (B) median and (C) 80th quantile of folate serum level. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (21000 simulations)") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 1, "(A) 20th quantile" = 4, 
                     "(B) Median" = 4, "(C) 80th quantile" = 4)) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table_149
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### model without sex
mod_nsex <- rqfit(type = 'adult', include= c("aSUP_FOL"),
                  exclude = c("SEX"))

### model without diet groups
mod_ndiet <- rqfit(type = 'adult',include= c("aSUP_FOL"),
                   exclude = c("GRP"))

### model without other
mod_other_cov <- rqfit(type = 'adult')

### model without age
mod_age <-  rqfit(type = 'adult',include= c("aSUP_FOL"),
                   exclude = c("aAGE"))

```

Putting key results together

```{r}
AIC_adult <- add_AIC_adult(AIC_adult)

diet_adult <- add_eff(diet_adult, res)

i = i+1
```


### Saving tables

```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_adult.xlsx') == FALSE){
  diet_adult <- diet_adult[-1,]
  
  diet_adult$VN_OM_P_adj <- NA
  diet_adult$VG_OM_P_adj <- NA
  diet_adult$VN_VG_P_adj <- NA
  
for (i in seq(1, nrow(diet_adult), by = 3)) {
  padj <- p.adjust(c(
    diet_adult$VN_OM_P[i], 
    diet_adult$VN_OM_P[i+1],
    diet_adult$VN_OM_P[i+2],
    
    diet_adult$VG_OM_P[i],
    diet_adult$VG_OM_P[i+1],
    diet_adult$VG_OM_P[i+2],
    
    diet_adult$VN_VG_P[i],
    diet_adult$VN_VG_P[i+1],
    diet_adult$VN_VG_P[i+2]), method = 'hochberg')
  
  diet_adult$VN_OM_P_adj[i:(i+2)] <- padj[1:3]
  diet_adult$VG_OM_P_adj[i:(i+2)] <- padj[4:6]
  diet_adult$VN_VG_P_adj[i:(i+2)] <- padj[7:9]
}
  
  
  diet_adult <- diet_adult %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) %>% 
    mutate(across(.cols = c(VN_OM_P, VG_OM_P, VN_VG_P,
                            VN_OM_P_adj, VG_OM_P_adj, VN_VG_P_adj), ~ round(.x, 5)))

  write.xlsx(diet_adult, 'gitignore/data/diet_adult.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_adult.xlsx') == FALSE){
  AIC_adult <- AIC_adult[-1,]
  write.xlsx(AIC_adult, 'gitignore/data/AIC_adult.xlsx')
  }
```

# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
