---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: "Statistical report - mixed models summary"
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: "Open code"
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
project:
  type: default
  output-dir: output
editor: source
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
fontcolor: "#C4C4C4"
monobackgroundcolor: "#3B3B3B"
bibliography: ../references.bib
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
knitr::opts_knit$set(root.dir = "/home/ticf/GitRepo/ticf/368_MOCA_kompas_clinical")
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.86em;
  border: 1px solid #ffffff; 
  padding: 9px; 
}

code{
    color: #EEE8AA; 
    background: #96464D
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}
```


{{< include ../README.md >}}


# Robust linear-mixed-effects models

```{r}
source('r/368_initiation.R')
```

## Children

### Diet effects

#### Unstandardized effects

```{r}
diet_child_all <- read.xlsx("gitignore/data/diet_child_all_mixeff.xlsx") %>%
  mutate(outcome = clean_outcome_names(outcome)) %>%
  mutate(outcome = case_when(
    outcome == "FOLAT" ~ "FOLATE",
    outcome == "VKFE" ~ "TIBC",
    outcome == "Cros" ~ "CTX",
    outcome == "log2_Cros" ~ "log2_CTX",
    outcome == "VIT_AKTB12" ~ "HOLOTC",
    outcome == "log2_VIT_AKTB12" ~ "log2_HOLOTC",
    outcome == "log2_Ur_Ca" ~ "log2_uCa",
    outcome == "log2_Ca_per_Krea" ~ "log2_uCCR",
    outcome == "log2_I_per_Krea" ~ "log2_uICR",
    outcome == "P_per_Krea" ~ "uPCR",
    outcome == "log2_P_per_Krea" ~ "log2_uPCR",
    TRUE ~ outcome
  ))

diet_child_all2 <- diet_child_all %>%
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))


kableExtra::kable(diet_child_all2,
  caption = "Differences in clinical outcomes (`outcome`) between diet groups in children, estimated using robust linear mixed-effects models. For each outcome, the table reports the estimated difference (`[...]_diff`), raw p-value (`[...]_P`), and FDR-corrected p-value (`[...]_P_adj`) for multiple comparisons. Comparisons include (A) vegans vs. omnivores (`VN_OM`), (B) vegetarians vs. omnivores (`VG_OM`), and (C) vegans vs. vegetarians (`VN_VG`)."
) %>%
  kable_styling("striped", full_width = T) %>%
  add_header_above(c(
    " " = 2, "(A) VN vs OM" = 3,
    "(B) VG vs OM" = 3, "(C) VN vs VG" = 3
  )) %>%
  column_spec(1, width_min = "1.5in")
```

#### Standardized effects by 1SD

```{r}
meds <- diet_child_all %>% filter(estimand == "mean")

ids <- nrow(meds)
sds <- vector("double", ids)
sds 

before_outcome_col <- which(colnames(dat_child_all) == 'aMASS_Perc')-1

sds <- vector("double", ids)

for(i in 1:ids){
  sds[i] <- ifelse(grepl("log2", diet_child_all[(i), 'outcome']),
                   sd(log2(dat_child_all[,(i + before_outcome_col)]), na.rm = TRUE),
                   sd(dat_child_all[,(i + before_outcome_col)], na.rm = TRUE))
}


diet_child_all_Z <- diet_child_all %>% 
  mutate(SD = sds) %>% 
  mutate(
    VN_OM_diff = VN_OM_diff/SD,
    VG_OM_diff = VG_OM_diff/SD,
    VN_VG_diff = VN_VG_diff/SD) %>% 
  select(-c(SD)) %>% 
  mutate(across(.cols = c(VG_OM_diff, VN_OM_diff, VN_VG_diff), ~ round(.x, 2)))


kbl(diet_child_all_Z, caption = 
      "Standardized differences in clinical outcomes (`outcome`) between diet groups in children, estimated using robust linear mixed-effects models. For each outcome, the table reports the estimated difference (`[...]_diff`), raw p-value (`[...]_P`), and FDR-corrected p-value (`[...]_P_adj`) for multiple comparisons. Comparisons include (A) vegans vs. omnivores (`VN_OM`), (B) vegetarians vs. omnivores (`VG_OM`), and (C) vegans vs. vegetarians (`VN_VG`).") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 
```

#### Vulcano plots

VN vs OM

```{r}
color_map <- c(
  "OM+" = rgb(213/255, 94/255, 0),
  "VN+" = rgb(0, 158/255, 75/255),
  "VG+" = rgb(0, 95/255, 195/255),
  "P>0.05" = "grey50"
)

plotac <- "fig19"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_child_all_Z %>%
    filter(estimand != "log(OR)") %>%
    mutate(
      pv_adj = VN_OM_P_adj,
      pv_raw = VN_OM_P,
      b_coe = VN_OM_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VN+",
          "OM+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c("OM+", "VN+", "P>0.05")
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.3,
      size = 3.1,
      seed = 17
    ) +
    labs(x = "Standardized difference", y = "-log10 (P-value)") +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VN vs. OM, all children") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}

```

VG vs OM

```{r}
#| fig.cap: 'Figure 20. Vulcano plot showing standardized differences between VG and OM across clinical outcomes in all children, based on mixed-effects models'


plotac <- "fig20"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_child_all_Z %>%
    filter(estimand != "log(OR)") %>%
    mutate(VG_OM_P = if_else(VG_OM_P < 1e-5, 1e-5, VG_OM_P)) %>%
    mutate(
      pv_adj = VG_OM_P_adj,
      pv_raw = VG_OM_P,
      b_coe = VG_OM_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VG+",
          "OM+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c("OM+", "VG+", "P>0.05")
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.3,
      size = 3.1,
      seed = 17
    ) +
    labs(x = "Standardized difference", y = "-log10 (P-value)") +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VG vs. OM, all children") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}
 
```

VN vs VG

```{r}
plotac <- "fig21"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_child_all_Z %>%
    filter(estimand != "log(OR)") %>%
    
    mutate(
      pv_adj = VN_VG_P_adj,
      pv_raw = VN_VG_P,
      b_coe = VN_VG_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VN+",
          "VG+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c(
          "VG+",
          "VN+",
          "P>0.05"
        )
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.5,
      size = 3.1,
      seed = 16
    ) +
    labs(
      x = "Standardized difference",
      y = "-log10 (P-value)"
    ) +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VN vs VG, all children") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}

```

### Covariates importance

#### Table

```{r}
AIC_child_all <- read.xlsx("gitignore/data/AIC_child_all_mixeff.xlsx") %>%
  mutate(across(where(is.numeric), ~ round(., 1)),
    outcome = clean_outcome_names(outcome)
  ) %>%
  rename(
    SEX = aSEX,
    BREASTFEED = Breast_Feed,
    `OTHER COV` = other_cov,
    FAMILY = family,
    DIET = diet,
    AGE = log2_age
  ) %>%
  mutate(outcome = case_when(
    outcome == "FOLAT" ~ "FOLATE",
    outcome == "VKFE" ~ "TIBC",
    outcome == "Cros" ~ "CTX",
    outcome == "log2_Cros" ~ "log2_CTX",
    outcome == "VIT_AKTB12" ~ "HOLOTC",
    outcome == "log2_VIT_AKTB12" ~ "log2_HOLOTC",
    
    outcome == 'log2_aUr_Ca' ~ 'log2_uCa',
    outcome == 'log2_Ca_per_Krea' ~ 'log2_uCCR',
    outcome == 'log2_I_per_Krea' ~ 'log2_uICR',
    outcome == 'P_per_Krea' ~ 'uPCR',
    outcome == 'log2_P_per_Krea' ~ 'log2_uPCR',
    
    TRUE ~ outcome
  ))

kbl(AIC_child_all,
  caption =
    "Change of the Akaike Information Criterion (AIC) after addition of a given variable to mixed effects models for children. The magnitude of the AIC change indicates the impact on out-of-sample predictive accuracy, with more negative values reflecting greater importance of the variable."
) %>%
  kable_styling("striped", full_width = T) %>%
  column_spec(1, width_min = "1.5in")
```

#### Heatmap

```{r, fig.height=6, fig.width=4}
#| fig.cap: 'Heatmap showing decrease in the Akaike Information Criterion (AIC) after the addition of a given variable to a mixed-effects model in children. The AIC change reflects the impact of the variable on out-of-sample predictive accuracy, with values bounded between -30 (high importance, shown in blue) and 0 (no or negligible importance, shown in red). Black indicates that the variable was not included in the model (e.g., inapplicable supplementation-related variables)'

heat_map(AIC_child_all, mixef = TRUE)
```

## Adults

### Diet effects

#### Unstandardized effects

```{r}
diet_adult <- read.xlsx("gitignore/data/diet_adult_mixeff.xlsx") %>%
  mutate(outcome = clean_outcome_names(outcome)) %>%
    mutate(outcome = case_when(
      outcome == "FOLAT" ~ "FOLATE",
      outcome == "log2_VKFE" ~ "log2_TIBC",
      outcome == "Cros" ~ "CTX",
      outcome == "log2_Cros" ~ "log2_CTX",
      outcome == "VIT_AKTB12" ~ "HOLOTC",
      outcome == "log2_VIT_AKTB12" ~ "log2_HOLOTC",
      
      outcome == "log2_Ur_Ca" ~ "log2_uCa",
      outcome == "log2_Ca_per_Krea" ~ "log2_uCCR",
      outcome == "log2_I_per_Krea" ~ "log2_uICR",
      outcome == "P_per_Krea" ~ "uPCR",
      outcome == "log2_P_per_Krea" ~ "log2_uPCR",
      TRUE ~ outcome
    ))

  diet_adult2 <- diet_adult %>%
    mutate(across(
      .cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff),
      ~ round(.x, 2)
    ))

  kbl(diet_adult2,
    caption =
      "Differences in clinical outcomes (`outcome`) between diet groups in adults, estimated using robust linear mixed-effects models. For each outcome, the table reports the estimated difference (`[...]_diff`), raw p-value (`[...]_P`), and FDR-corrected p-value (`[...]_P_adj`) for multiple comparisons. Comparisons include (A) vegans vs. omnivores (`VN_OM`), (B) vegetarians vs. omnivores (`VG_OM`), and (C) vegans vs. vegetarians (`VN_VG`)."
  ) %>%
    kable_styling("striped", full_width = T) %>%
    add_header_above(c(
      " " = 2, "(A) VN vs OM" = 3,
      "(B) VG vs OM" = 3, "(C) VN vs VG" = 3
    )) %>%
    column_spec(1, width_min = "1.5in")
```

#### Standardized effects by 1SD

```{r}
meds <- diet_adult %>% filter(estimand == "mean")

ids <- nrow(meds)
sds <- vector("double", ids)
sds 

before_outcome_col <- which(colnames(dat_adult) == 'aBMI')-1

for (i in 1:ids) {
  sds[i] <- ifelse(grepl("log2", diet_adult[(i), 1]),
    sd(log2(dat_adult[, (i + before_outcome_col)]), na.rm = TRUE),
    sd(     dat_adult[, (i + before_outcome_col)] , na.rm = TRUE)
  )
}

sds[(ids+1) : (ids+2)] <- 1

diet_adult_Z <- diet_adult %>%
  mutate(SD = sds) %>%
  mutate(
    VN_OM_diff = VN_OM_diff / SD,
    VG_OM_diff = VG_OM_diff / SD,
    VN_VG_diff = VN_VG_diff / SD
  ) %>%
  select(-SD) %>%
  mutate(VG_OM_P = if_else(VG_OM_P < 1e-5, 1e-5, VG_OM_P)) %>%
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))


kbl(diet_adult_Z,
  caption =
    "Standardized differences in clinical outcomes (`outcome`) between diet groups in children, estimated using robust linear mixed-effects models. For each outcome, the table reports the estimated difference (`[...]_diff`), raw p-value (`[...]_P`), and FDR-corrected p-value (`[...]_P_adj`) for multiple comparisons. Comparisons include (A) vegans vs. omnivores (`VN_OM`), (B) vegetarians vs. omnivores (`VG_OM`), and (C) vegans vs. vegetarians (`VN_VG`)."
) %>%
  kable_styling("striped", full_width = T) %>%
  add_header_above(c(
    " " = 2, "(A) VN vs OM" = 3,
    "(B) VG vs OM" = 3, "(C) VN vs VG" = 3
  )) %>%
  column_spec(1, width_min = "1.5in")
```

#### Vulcano plots

VN vs OM

```{r}

plotac <- "fig31"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_adult_Z %>%
    filter(estimand != "log(OR)") %>%
    
    mutate(
      pv_adj = VN_OM_P_adj,
      pv_raw = VN_OM_P,
      b_coe = VN_OM_diff
    ) %>%
    mutate(
      pv_adj = VN_OM_P_adj,
      pv_raw = VN_OM_P,
      b_coe = VN_OM_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VN+",
          "OM+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c("OM+", "VN+", "P>0.05")
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.7,
      size = 3.1,
      seed = 17
    ) +
    labs(x = "Standardized difference", y = "-log10 (P-value)") +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VN vs. OM, adults") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}
```


VG vs OM

```{r}
plotac <- "fig32"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_adult_Z %>%
    filter(estimand != "log(OR)") %>%
    
    mutate(
      pv_adj = VG_OM_P_adj,
      pv_raw = VG_OM_P,
      b_coe = VG_OM_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VG+",
          "OM+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c("OM+", "VG+", "P>0.05")
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.6,
      size = 3.1,
      seed = 17
    ) +
    labs(x = "Standardized difference", y = "-log10 (P-value)") +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VG vs OM, adults") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}
```

VN vs VG

```{r}

plotac <- "fig33"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_adult_Z %>%
    filter(estimand != "log(OR)") %>%
    mutate(
      pv_adj = VN_VG_P_adj,
      pv_raw = VN_VG_P,
      b_coe = VN_VG_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VN+",
          "VG+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c(
          "VG+",
          "VN+",
          "P>0.05"
        )
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.6,
      size = 3.1,
      seed = 16
    ) +
    labs(
      x = "Standardized difference",
      y = "-log10 (P-value)"
    ) +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VN vs VG, adults") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}
```

### Covariates importance

#### Table

```{r}

AIC_adult <- read.xlsx("gitignore/data/AIC_adult_mixeff.xlsx") %>%
  mutate(across(where(is.numeric), ~ round(., 1))) %>%
  mutate(outcome = clean_outcome_names(outcome)) %>%
  filter(!outcome %in% c("AL_adult", "BREAKS")) %>%
  rename(
    SEX = aSEX,
    `OTHER COV` = other_cov,
    FAMILY = family,
    DIET = diet,
    AGE = aAGE
  ) %>%
  mutate(outcome = case_when(
    outcome == "FOLAT" ~ "FOLATE",
    outcome == "VKFE" ~ "TIBC",
    outcome == "Cros" ~ "CTX",
    outcome == "log2_Cros" ~ "log2_CTX",
    outcome == "VIT_AKTB12" ~ "HOLOTC",
    outcome == "log2_VIT_AKTB12" ~ "log2_HOLOTC",
    
    outcome == 'log2_aUr_Ca' ~ 'log2_uCa',
    outcome == 'log2_Ca_per_Krea' ~ 'log2_uCCR',
    outcome == 'log2_I_per_Krea' ~ 'log2_uICR',
    outcome == 'P_per_Krea' ~ 'uPCR',
    outcome == 'log2_P_per_Krea' ~ 'log2_uPCR',
    TRUE ~ outcome
  ))

kbl(AIC_adult,
  caption =
    "Change of the Akaike Information Criterion (AIC) after addition of a given variable to mixed effects models for adults. The magnitude of the AIC change indicates the impact on out-of-sample predictive accuracy, with more negative values reflecting greater importance of the variable."
) %>%
  kable_styling("striped", full_width = T) %>%
  column_spec(1, width_min = "1.5in")
```

#### Heatmap

```{r, fig.height=6, fig.width=4}
#| fig.cap: 'Heatmap showing decrease in the Akaike Information Criterion (AIC) after the addition of a given variable to a mixed-effects model in adults. The AIC change reflects the impact of the variable on out-of-sample predictive accuracy, with values bounded between -30 (high importance, shown in blue) and 0 (no or negligible importance, shown in red). Black indicates that the variable was not included in the model (e.g., inapplicable supplementation-related variables)'
heat_map(AIC_adult, mixef = TRUE)
```

## Vulcano matrix

Prepare 

```{r}
plotac <- "fig35"
path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  fig19 <- fig19 + theme(
    legend.position = "none",
    plot.title = element_blank()
  )
  fig20 <- fig20 + theme(
    legend.position = "none",
    plot.title = element_blank()
  )
  fig21 <- fig21 + theme(
    legend.position = "none",
    plot.title = element_blank()
  )

  fig31 <- fig31 + theme(
    legend.position = "bottom",
    plot.title = element_blank()
  )
  fig32 <- fig32 + theme(
    legend.position = "bottom",
    plot.title = element_blank()
  )
  fig33 <- fig33 + theme(
    legend.position = "bottom",
    plot.title = element_blank()
  )
}
```


Create subfigures

```{r, fig.height=10, fig.width=10, warning=FALSE}

if (file.exists(path) == FALSE) {
  children_volc <- ggarrange(
    fig19 +
      theme(
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
      ),
    fig20 +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
      ),
    fig21 +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
      ),
    nrow = 1,
    ncol = 3,
    widths = c(1.1, 1, 1),
    labels = c("A", "", "")
  )

  children_volc <- annotate_figure(
    children_volc,
    top = text_grob("Children", face = "bold", size = 10)
  )


  adult_volc <- ggarrange(
    fig31,
    fig32 +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()
      ),
    fig33 +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()
      ),
    nrow = 1,
    ncol = 3,
    widths = c(1.1, 1, 1),
    labels = c("B", "", "")
  )

  adult_volc <- annotate_figure(
    adult_volc,
    top = text_grob("Adults", face = "bold", size = 10)
  )
}
```

### Print

```{r, fig.height=7, fig.width=10, warning=FALSE}
#| fig.cap: 'Vulcano plot showing standardized differences between vegan (VN) and omnivores (OM) (*left*), vegetarians (VG) vs OM (*middle*) and VN vs VG (*right*) across clinical outcomes in children (**A**, *top*) and adults (**B**, *bottom*). Estimated effects are based on robust linear mixed-effects models. P-values are not corrected for multiple comparisons to maximize sensitivity for a potential risks'

if (file.exists(path) == FALSE) {
  assign(
    plotac,
    ggarrange(
      children_volc,
      adult_volc,
      nrow = 2,
      ncol = 1,
      heights = c(1, 1.2)
    )
  )

  saveRDS(get(plotac), file = path)
  get(plotac)
} else {
  assign(plotac, readRDS(path))
  get(plotac)
}

## save svg
plotac <- "fig35"
path <- paste0("gitignore/figures/", plotac, ".svg")

if(!file.exists(path)){
  ggsave(path, get(plotac), device = 'svg', width = 10, height = 7)
}

```


## Heatmap matrix

```{r, fig.height=6, fig.width=7, warning=FALSE}
#| fig.cap: 'Heatmap showing decrease in the Akaike Information Criterion (AIC) after the addition of a given variable to a mixed-effects model, separately for children (left) and adults (right). The AIC change reflects the impact of the variable on out-of-sample predictive accuracy, with values bounded between -30 (high importance, shown in blue) and 0 (no or negligible importance, shown in red). Black indicates that the variable was not included in the model (e.g., inapplicable supplementation-related variables)'

h1 <- heat_map(AIC_child_all, mixef = TRUE, main = 'Children', listt = TRUE)
h2 <- heat_map(AIC_adult, mixef = TRUE, main = 'Adults', listt = TRUE)

grid.arrange(grobs = list(h1$gtable, h2$gtable),
             nrow = 1, ncol = 2)

plotac <- 'heatmaps_mixef_combo'
path = paste0('gitignore/figures/', plotac, '.svg')
if(file.exists(path) == FALSE){
  svg(path, width = 7, height = 6)  
  grid.arrange(grobs = list(h1$gtable, h2$gtable),
             nrow = 1, ncol = 2)
  dev.off()
}

path <- paste0('gitignore/figures/', plotac, '.pdf')
if (!file.exists(path)) {
  pdf(path, width = 7, height = 6)  
  grid.arrange(grobs = list(h1$gtable, h2$gtable),
             nrow = 1, ncol = 2)
  dev.off()
}

```


# Linear-mixed-effects models (non-robust variant)

## Children

### Diet effects

#### Unstandardized effects

```{r}
diet_child_all <- read.xlsx("gitignore/data/diet_child_all_mixeff_non_robust.xlsx") %>% 
  mutate(outcome = clean_outcome_names(outcome)) %>%
  mutate(outcome = case_when(
    outcome == 'FOLAT' ~ 'FOLATE',
    outcome == 'VKFE' ~ 'TIBC',
    outcome == 'Cros' ~ 'CTX',
    outcome == 'log2_Cros' ~ 'log2_CTX',
    outcome == 'VIT_AKTB12' ~ 'HOLOTC',
    outcome == 'log2_VIT_AKTB12' ~ 'log2_HOLOTC',
    
    outcome == 'log2_aUr_Ca' ~ 'log2_uCa',
    outcome == 'log2_Ca_per_Krea' ~ 'log2_uCCR',
    outcome == 'log2_I_per_Krea' ~ 'log2_uICR',
    outcome == 'P_per_Krea' ~ 'uPCR',
    outcome == 'log2_P_per_Krea' ~ 'log2_uPCR',
    
    TRUE ~ outcome
  ))

diet_child_all2 <- diet_child_all %>%   
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))


kableExtra::kable(diet_child_all2, 
                caption = "Differences in clinical outcomes (`outcome`) between diet groups in children, estimated using linear mixed-effects models. For each outcome, the table reports the estimated difference (`[...]_diff`), raw p-value (`[...]_P`), and FDR-corrected p-value (`[...]_P_adj`) for multiple comparisons. Comparisons include (A) vegans vs. omnivores (`VN_OM`), (B) vegetarians vs. omnivores (`VG_OM`), and (C) vegans vs. vegetarians (`VN_VG`)."
                ) %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 
```

#### Standardized effects by 1SD

```{r}
meds <- diet_child_all %>% filter(estimand == "mean")

ids <- nrow(meds)
sds <- vector("double", ids)
sds 

before_outcome_col <- which(colnames(dat_child_all) == 'aMASS_Perc')-1

sds <- vector("double", ids)

for(i in 1:ids){
  sds[i] <- ifelse(grepl("log2", diet_child_all[(i), 'outcome']),
                   sd(log2(dat_child_all[,(i + before_outcome_col)]), na.rm = TRUE),
                   sd(dat_child_all[,(i + before_outcome_col)], na.rm = TRUE))
}


diet_child_all_Z <- diet_child_all %>% 
  mutate(SD = sds) %>% 
  mutate(
    VN_OM_diff = VN_OM_diff/SD,
    VG_OM_diff = VG_OM_diff/SD,
    VN_VG_diff = VN_VG_diff/SD) %>% 
  select(-c(SD)) %>% 
  mutate(across(.cols = c(VG_OM_diff, VN_OM_diff, VN_VG_diff), ~ round(.x, 2)))


kbl(diet_child_all_Z, caption = 
      "Standardized differences in clinical outcomes (`outcome`) between diet groups in children, estimated using linear mixed-effects models. For each outcome, the table reports the estimated difference (`[...]_diff`), raw p-value (`[...]_P`), and FDR-corrected p-value (`[...]_P_adj`) for multiple comparisons. Comparisons include (A) vegans vs. omnivores (`VN_OM`), (B) vegetarians vs. omnivores (`VG_OM`), and (C) vegans vs. vegetarians (`VN_VG`).") %>% 
  kable_styling("striped",full_width = T) %>% 
  add_header_above(c(" " = 2, "(A) VN vs OM" = 3, 
                     "(B) VG vs OM" = 3, "(C) VN vs VG" =3)) %>% 
  column_spec(1, width_min = '1.5in') 
```

#### Vulcano plots

VN vs OM

```{r}

plotac <- "fig19_nr"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_child_all_Z %>%
    filter(estimand != "log(OR)") %>%
    mutate(
      pv_adj = VN_OM_P_adj,
      pv_raw = VN_OM_P,
      b_coe = VN_OM_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VN+",
          "OM+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c("OM+", "VN+", "P>0.05")
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.3,
      size = 3.1,
      seed = 17
    ) +
    labs(x = "Standardized difference", y = "-log10 (P-value)") +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VN vs. OM, all children") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}

```

VG vs OM

```{r}
plotac <- "fig20_nr"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_child_all_Z %>%
    filter(estimand != "log(OR)") %>%
    mutate(VG_OM_P = if_else(VG_OM_P < 1e-5, 1e-5, VG_OM_P)) %>%
    mutate(
      pv_adj = VG_OM_P_adj,
      pv_raw = VG_OM_P,
      b_coe = VG_OM_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VG+",
          "OM+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c("OM+", "VG+", "P>0.05")
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.3,
      size = 3.1,
      seed = 17
    ) +
    labs(x = "Standardized difference", y = "-log10 (P-value)") +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VG vs. OM, all children") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}
 
```

VN vs VG

```{r}
plotac <- "fig21_nr"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_child_all_Z %>%
    filter(estimand != "log(OR)") %>%
    
    mutate(
      pv_adj = VN_VG_P_adj,
      pv_raw = VN_VG_P,
      b_coe = VN_VG_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VN+",
          "VG+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c(
          "VG+",
          "VN+",
          "P>0.05"
        )
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.5,
      size = 3.1,
      seed = 16
    ) +
    labs(
      x = "Standardized difference",
      y = "-log10 (P-value)"
    ) +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VN vs VG, all children") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}

```

## Adults

### Diet effects

#### Unstandardized effects

```{r}
diet_adult <- read.xlsx("gitignore/data/diet_adult_non_robust_mixeff_non_robust.xlsx") %>%
  mutate(outcome = clean_outcome_names(outcome)) %>%
  mutate(outcome = case_when(
    outcome == "FOLAT" ~ "FOLATE",
    outcome == "log2_VKFE" ~ "log2_TIBC",
    outcome == "Cros" ~ "CTX",
    outcome == "log2_Cros" ~ "log2_CTX",
    outcome == "VIT_AKTB12" ~ "HOLOTC",
    outcome == "log2_VIT_AKTB12" ~ "log2_HOLOTC",
    
    outcome == 'log2_aUr_Ca' ~ 'log2_uCa',
    outcome == 'log2_Ca_per_Krea' ~ 'log2_uCCR',
    outcome == 'log2_I_per_Krea' ~ 'log2_uICR',
    outcome == 'P_per_Krea' ~ 'uPCR',
    outcome == 'log2_P_per_Krea' ~ 'log2_uPCR',
    TRUE ~ outcome
  ))

diet_adult2 <- diet_adult %>%
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))

kbl(diet_adult2,
  caption =
    "Differences in clinical outcomes (`outcome`) between diet groups in adults, estimated using linear mixed-effects models. For each outcome, the table reports the estimated difference (`[...]_diff`), raw p-value (`[...]_P`), and FDR-corrected p-value (`[...]_P_adj`) for multiple comparisons. Comparisons include (A) vegans vs. omnivores (`VN_OM`), (B) vegetarians vs. omnivores (`VG_OM`), and (C) vegans vs. vegetarians (`VN_VG`)."
) %>%
  kable_styling("striped", full_width = T) %>%
  add_header_above(c(
    " " = 2, "(A) VN vs OM" = 3,
    "(B) VG vs OM" = 3, "(C) VN vs VG" = 3
  )) %>%
  column_spec(1, width_min = "1.5in")
```

#### Standardized effects by 1SD

```{r}
meds <- diet_adult %>% filter(estimand == "mean")

ids <- nrow(meds)
sds <- vector("double", ids)
sds 

before_outcome_col <- which(colnames(dat_adult) == 'aBMI')-1

for (i in 1:ids) {
  sds[i] <- ifelse(grepl("log2", diet_adult[(i), 1]),
    sd(log2(dat_adult[, (i + before_outcome_col)]), na.rm = TRUE),
    sd(     dat_adult[, (i + before_outcome_col)] , na.rm = TRUE)
  )
}

sds[(ids+1) : (ids+2)] <- 1

diet_adult_Z <- diet_adult %>%
  mutate(SD = sds) %>%
  mutate(
    VN_OM_diff = VN_OM_diff / SD,
    VG_OM_diff = VG_OM_diff / SD,
    VN_VG_diff = VN_VG_diff / SD
  ) %>%
  select(-SD) %>%
  mutate(VG_OM_P = if_else(VG_OM_P < 1e-5, 1e-5, VG_OM_P)) %>%
  mutate(across(.cols = c(VN_OM_diff, VG_OM_diff, VN_VG_diff), ~ round(.x, 2)))


kbl(diet_adult_Z,
  caption =
    "Standardized differences in clinical outcomes (`outcome`) between diet groups in adults, estimated using linear mixed-effects models. For each outcome, the table reports the estimated difference (`[...]_diff`), raw p-value (`[...]_P`), and FDR-corrected p-value (`[...]_P_adj`) for multiple comparisons. Comparisons include (A) vegans vs. omnivores (`VN_OM`), (B) vegetarians vs. omnivores (`VG_OM`), and (C) vegans vs. vegetarians (`VN_VG`)."
) %>%
  kable_styling("striped", full_width = T) %>%
  add_header_above(c(
    " " = 2, "(A) VN vs OM" = 3,
    "(B) VG vs OM" = 3, "(C) VN vs VG" = 3
  )) %>%
  column_spec(1, width_min = "1.5in")
```

#### Vulcano plots

VN vs OM

```{r}

plotac <- "fig31_nr"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_adult_Z %>%
    filter(estimand != "log(OR)") %>%
    
    mutate(
      pv_adj = VN_OM_P_adj,
      pv_raw = VN_OM_P,
      b_coe = VN_OM_diff
    ) %>%
    mutate(
      pv_adj = VN_OM_P_adj,
      pv_raw = VN_OM_P,
      b_coe = VN_OM_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VN+",
          "OM+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c("OM+", "VN+", "P>0.05")
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.7,
      size = 3.1,
      seed = 17
    ) +
    labs(x = "Standardized difference", y = "-log10 (P-value)") +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VN vs. OM, adults") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}
```


VG vs OM

```{r}
plotac <- "fig32_nr"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_adult_Z %>%
    filter(estimand != "log(OR)") %>%
    
    mutate(
      pv_adj = VG_OM_P_adj,
      pv_raw = VG_OM_P,
      b_coe = VG_OM_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VG+",
          "OM+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c("OM+", "VG+", "P>0.05")
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.6,
      size = 3.1,
      seed = 17
    ) +
    labs(x = "Standardized difference", y = "-log10 (P-value)") +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VG vs OM, adults") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}
```

VN vs VG

```{r}
#| fig.cap: 'Figure 33. Vulcano plot showing standardized differences between VN and OM across clinical outcomes in adults.'

plotac <- "fig33_nr"

path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  assign(plotac, diet_adult_Z %>%
    filter(estimand != "log(OR)") %>%
    
    mutate(
      pv_adj = VN_VG_P_adj,
      pv_raw = VN_VG_P,
      b_coe = VN_VG_diff
    ) %>%
    mutate(pv_raw = if_else(pv_raw < 1e-5, 1e-5, pv_raw)) %>%
    mutate(
      m_ylab = -log10(pv_raw),
      m_xlab = b_coe,
      rescat = if_else(
        pv_raw >= 0.05,
        "P>0.05",
        if_else(
          b_coe > 0,
          "VN+",
          "VG+"
        )
      )
    ) %>%
    mutate(
      rescat = factor(rescat,
        levels = c(
          "VG+",
          "VN+",
          "P>0.05"
        )
      ),
      meta_labels = if_else(pv_raw < 0.05, outcome, "")
    ) %>%
    ggplot(aes(
      x = b_coe,
      y = m_ylab,
      color = rescat,
      alpha = rescat,
      label = meta_labels
    )) +
    geom_point(size = 2, shape = 16, alpha = 0.6) +
    geom_text_repel(
      aes(
        x = m_xlab,
        y = m_ylab
      ),
      show.legend = FALSE,
      alpha = 1,
      box.padding = 0.6,
      size = 3.1,
      seed = 16
    ) +
    labs(
      x = "Standardized difference",
      y = "-log10 (P-value)"
    ) +
    scale_color_manual(values = color_map, name = "") +
    ggtitle("VN vs VG, adults") +
    theme(
      legend.text = element_text(size = 11),
      axis.title = element_text(size = 12)
    ) +
    coord_cartesian(
      ylim = c(0, 5),
      xlim = c(-1.7, 1.7)
    ))

  saveRDS(get(plotac), file = path)
} else {
  assign(plotac, readRDS(path))
}
```

## Vulcano matrix

Prepare

```{r}
plotac <- "fig35_nr"
path <- paste0("gitignore/figures/", plotac, ".rds")

if (file.exists(path) == FALSE) {
  fig19_nr <- fig19_nr + theme(
    legend.position = "none",
    plot.title = element_blank()
  )
  fig20_nr <- fig20_nr + theme(
    legend.position = "none",
    plot.title = element_blank()
  )
  fig21_nr <- fig21_nr + theme(
    legend.position = "none",
    plot.title = element_blank()
  )

  fig31_nr <- fig31_nr + theme(
    legend.position = "bottom",
    plot.title = element_blank()
  )
  fig32_nr <- fig32_nr + theme(
    legend.position = "bottom",
    plot.title = element_blank()
  )
  fig33_nr <- fig33_nr + theme(
    legend.position = "bottom",
    plot.title = element_blank()
  )
}
```


Create subfigures

```{r, fig.height=10, fig.width=10, warning=FALSE}

if (file.exists(path) == FALSE) {
  children_volc <- ggarrange(
    fig19_nr +
      theme(
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
      ),
    fig20_nr +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
      ),
    fig21_nr +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
      ),
    nrow = 1,
    ncol = 3,
    widths = c(1.1, 1, 1),
    labels = c("A", "", "")
  )

  children_volc <- annotate_figure(
    children_volc,
    top = text_grob("Children", face = "bold", size = 10)
  )


  adult_volc <- ggarrange(
    fig31_nr,
    fig32_nr +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()
      ),
    fig33_nr +
      theme(
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank()
      ),
    nrow = 1,
    ncol = 3,
    widths = c(1.1, 1, 1),
    labels = c("B", "", "")
  )

  adult_volc <- annotate_figure(
    adult_volc,
    top = text_grob("Adults", face = "bold", size = 10)
  )
}
```

### Print

```{r, fig.height=7, fig.width=10, warning=FALSE}
#| fig.cap: 'Vulcano plot showing standardized differences between vegan (VN) and omnivores (OM) (*left*), vegetarians (VG) vs OM (*middle*) and VN vs VG (*right*) across clinical outcomes in children (**A**, *top*) and adults (**B**, *bottom*). Estimated effects are based on linear mixed-effects models. P-values are not corrected for multiple comparisons to maximize sensitivity for a potential risks'

if(file.exists(path) == FALSE){
  assign(plotac,
       ggarrange(
         children_volc,
         adult_volc,
         nrow = 2, 
         ncol = 1,
         heights = c(1, 1.2))
       )
  
  saveRDS(get(plotac), file = path)
  get(plotac)} else {
    assign(plotac, readRDS(path))
    get(plotac)}

## save svg
plotac <- "fig35_nr"
path <- paste0("gitignore/figures/", plotac, ".svg")

if(!file.exists(path)){
  ggsave(path, get(plotac), device = 'svg', width = 10, height = 7)
}
```


# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
