---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: 'Statistical report - mixed-effects models in all children'
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 5
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: 'Open code'
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
project:
  type: default
  output-dir: output
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: '#2D2D31'
fontcolor: '#C4C4C4'
monobackgroundcolor: '#3B3B3B'
bibliography: ../references.bib
---

------------------------------------------------------------------------


```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
knitr::opts_knit$set(root.dir = "/home/ticf/GitRepo/ticf/368_MOCA_kompas_clinical")
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.86em;
  border: 1px solid #ffffff; 
  padding: 9px; 
}

code{
    color: #EEE8AA; 
    background: #96464D
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}
```

{{< include ../README.md >}}

# Analysis

## Import initiation file

```{r}
getwd()
setwd('/home/ticf/GitRepo/ticf/368_MOCA_kompas_clinical/')
source('r/368_initiation.R')
```

## Mixed models

All children models will be adjusted for the effect of `log2_age` (when applicable, i.e. not for age-adjusted Anthropometric data), `SEX`, `aBreastFeed_full_stopped`, `aBreastFeed_total_stopped`, and `aBreastFeed_full_duration` (the interaction of the latter with duration of the dependence on the breastfeeding). Additional covariates (relevant supplementation for vitamins and biogenic elements levels) or birth weight (anthropometric data) will be added as covariates.

```{r}
AIC_child_all <- data.frame(outcome = NA,
                            estimand = 'mean',
                            log2_age = NA,
                            aSEX = NA,
                            Breast_Feed = NA,
                            other_cov = NA,
                            diet = NA,
                            family = NA)

diet_child_all <- data.frame(outcome = NA,
                         estimand = NA,
                         VN_OM_diff = NA, 
                         VN_OM_P = NA,
                         VG_OM_diff = NA, 
                         VG_OM_P = NA,
                         VN_VG_diff = NA, 
                         VN_VG_P = NA)

diet_child_all_non_robust <- data.frame(outcome = NA,
                         estimand = NA,
                         VN_OM_diff = NA, 
                         VN_OM_P = NA,
                         VG_OM_diff = NA, 
                         VG_OM_P = NA,
                         VN_VG_diff = NA, 
                         VN_VG_P = NA)

i = 1
j = 1
ni  <-  10
```

### aMASS_Perc

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
     SEX + 
     GRP +
     aBiW +
     s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of age-standardized percentile of body mass. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'))

res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC
AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE)
diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aHEIGHT_Perc

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5, collapse=TRUE}

## Data selection and diagnostic plots
ni  <-  10

column_name <- names(dat_child_all)[i+ni]
column_name

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    #s(log2_age)
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)

### Model check
pltmd(gamm)
```


Fit main model

```{r, fig.height=6, fig.width=6, collapse=TRUE, warning=FALSE, message=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)
  
suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects regression modelling of age-standardized percentile of body height. CI_L and CI_U are bounds of 95% confidence interval. Estimates are based on bootstrap (5000 simulations)') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1.5in')


suppl_table
```

Leave-one-factor lqm

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'))


### model without log2_age
mod_log2_age <- NA
  # rlme(exclude = c('log2_age'), include = 'aBiW')

```

Putting key results together

```{r}

## AIC
AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aBMI_PERC

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    #s(log2_age)
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)

### Model check
pltmd(gamm)
```


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of age-standardized percentile of BMI. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aM_per_H_PERC

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aBiW))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aBiW +
    #s(log2_age)
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of age-standardized percentile of weight to height ratio. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(exclude = c('log2_age'),
                    include = c('aBiW'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme( exclude = c('log2_age'),
                    include = c('aBiW'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('log2_age', 'SEX'), include = 'aBiW')

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('log2_age',
                             'aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                 include = 'aBiW')

### model without diet groups
mod_ndiet <- rlme(exclude = c('log2_age', 'GRP'), include = 'aBiW')

### model without birth weight
mod_other_cov <- rlme(exclude = c('log2_age'))

### model without log2_age
mod_log2_age <- NA

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aGLY

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of glycemia. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()

res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aTC

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of total cholesterol. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aHDL

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Diagnostic plot looks better now, but the difference in not huge. We will use original values to unify it with LDL analysis where transformation is unsuitable.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)

summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of HDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)


### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aLDL

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of LDL cholesterol level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aTG

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of TG cholesterol level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aCa

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, 
       remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of of serum Ca level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(,remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Ca'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aP

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, 
       remove_random = FALSE),
  
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum P level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)


i = i+1
```

### aMg

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Mg))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Mg +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Mg'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of of serum Mg level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Mg'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Mg'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Mg'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Mg'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Mg'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Mg'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)


## ICC
icc(mod_main)

i = i+1
```

### aSe

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Se))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

## ICC
icc(mod_main)

### Model check
pltmd(gamm)
```

The distribution of residuals seem a little bit better. Lets continue continue on log-scale

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Se'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(serum Se level). CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Se'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Se'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Se'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Se'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Se'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Se'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aZn

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Zn))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Zn +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

The distribution of residuals seem better. Lets continue continue on log-scale

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0("log2_", column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Zn'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum Zn level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Zn'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Zn'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Zn'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Zn'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Zn'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Zn'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aFE

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum Fe level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'), 
                   remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'), 
                 exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aVKFE

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue with the original scale.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum ferritin Fe binding capacity. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(
  include = c('aSUP_Fe'),
  exclude = c('aBreastFeed_full_stopped',
              'aBreastFeed_total_stopped',
              'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aFERR

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Se +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. It seems that the `aFERR` change in multiplicative, rather than additive way. We will continue to work with log-transformed values.


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome)
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(
  res, 
  caption =
    'Results of linear mixed-effects model of serum ferritin levels. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),
                   remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),
                 exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aTRF

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE,
       include = c('aSUP_Fe'),
       remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of serum transferin level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(
  include = c('aSUP_Fe'),
  exclude = c('aBreastFeed_full_stopped',
		          'aBreastFeed_total_stopped',
		          'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aSATTRF

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]



dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of transferin saturation. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aTRFINDEX

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation slightly improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)


## main model 
mod_main <- run(
   rlme(main = TRUE,
       include = c('aSUP_Fe'), 
       remove_random = FALSE),
  
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of TRF index. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aSTRF

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Fe))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Fe +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation slightly improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Fe'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(soluble transferin receptor level). CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Fe'))
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Fe'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Fe'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Fe'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Fe'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Fe'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aHGB

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}
gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit substantially. We will continue to work with original values.


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main <- model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of hemoglobin level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aMCV

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of mean corpuscular volume. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aPTH

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of parathormone level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=TRUE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)
i = i+1
```

### aCros

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D)) 

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Ca', 'aSUP_D'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(beta cross laps). CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca', 'aSUP_D'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Ca', 'aSUP_D'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca', 'aSUP_D'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)
i = i+1
```

### aP1NP

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSUP_Ca),
         !is.na(aSUP_D)) 

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_Ca', 'aSUP_D'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of procollagen type I level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca', 'aSUP_D'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Ca', 'aSUP_D'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca', 'aSUP_D'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Ca', 'aSUP_D'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)

i = i+1
```

### aUI

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]



dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation better


Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}
dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of urinary iodine level . CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)

i = i+1
```

### aUREA

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name),
 	log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, include = c('log2_age_2'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of urea level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('log2_age_2'),remove_random = TRUE)
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('log2_age_2'),exclude = c('SEX'),
                 remove_random = TRUE)

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('log2_age_2'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'),  
                remove_random = TRUE)

### model without diet groups
mod_ndiet <- rlme(include = c('log2_age_2'),
		 exclude = c('GRP'),
                  remove_random = TRUE)

### model without log2_age_2
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'),
		  include = c('log2_age_2'),remove_random = TRUE)

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)

i = i+1
```

### aCREA

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(aAGE) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(creatinine) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aUA

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of uric acid level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

## ICC
icc(mod_main)

i = i+1
```

### aVIT_AKTB12

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name),
 	log2_age_2 = log2_age**2) %>% 
  filter(!is.na(outcome),
	!is.na(aSup_B12))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age_2) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age_2) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE,  include = c('log2_age_2', 'aSup_B12'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(active vitamin B12) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('log2_age_2', 'aSup_B12'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(include = c('log2_age_2', 'aSup_B12'),
                   remove_random = TRUE)

### model without sex
mod_nsex <- rlme( include = c('log2_age_2', 'aSup_B12'),
                  exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(
  include = c('log2_age_2', 'aSup_B12'),
  exclude = c('aBreastFeed_full_stopped',
		          'aBreastFeed_total_stopped',
              'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(
  include = c('log2_age_2', 'aSup_B12'),
  exclude = c('GRP'))

### model without other cov - log2_age_2 and supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(
  exclude = c('log2_age'),
  include = c('log2_age_2', 'aSup_B12'))

```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)
i = i+1
```

### aHCY

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE, 
       include = c('aSup_B12'),
       remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(homocysteine) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c("aSup_B12"))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(
  include = c("aSup_B12"),
  remove_random = TRUE
)

### model without sex
mod_nsex <- rlme(
  include = c("aSup_B12"),
  exclude = c("SEX")
)

### model without breastfeeding-related predictors
mod_nbf <- rlme(
  include = c("aSup_B12"),
  exclude = c(
    "aBreastFeed_full_stopped",
    "aBreastFeed_total_stopped",
    "aBreastFeed_full_duration"
  )
)

### model without diet groups
mod_ndiet <- rlme(include = c("aSup_B12"), exclude = c("GRP"))

### model without other cov.
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(
  include = c("aSup_B12"),
  exclude = c("log2_age")
)
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)
i = i+1
```

### aMMA

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
         !is.na(aSup_B12))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSup_B12 +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. Even though it's not perfect we will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
  rlme(
    main = TRUE, 
    include = c('aSup_B12'),
    remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(methylmalonic acid) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}
### main model but non-robust
mod_main <- rlme(include = c("aSup_B12"))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(
  include = c("aSup_B12"),
  remove_random = TRUE
)

### model without sex
mod_nsex <- rlme(
  include = c("aSup_B12"),
  exclude = c("SEX")
)

### model without breastfeeding-related predictors
mod_nbf <- rlme(
  include = c("aSup_B12"),
  exclude = c(
    "aBreastFeed_full_stopped",
    "aBreastFeed_total_stopped",
    "aBreastFeed_full_duration"
  )
)

### model without diet groups
mod_ndiet <- rlme(include = c("aSup_B12"), exclude = c("GRP"))

### model without other cov.
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(
  include = c("aSup_B12"),
  exclude = c("log2_age")
)
```


Putting key results together

```{r}
AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)
i = i+1
```

### aVIT_D

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i + ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>%
  filter(
    !is.na(outcome),
    !is.na(aSUP_D)
  )

column_name

gamm <- gam(
  outcome ~
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped +
    SEX +
    GRP +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs = "re"),
  data = dat_mod
)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped +
    SEX +
    GRP +
    aSUP_D +
    s(log2_age) +
    s(FAM, bs = "re"),
  data = dat_mod
)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_D'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(vitamin D serum) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_D'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(include = c('aSUP_D'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_D'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_D'),
		exclude = c('aBreastFeed_full_stopped',
		            'aBreastFeed_total_stopped',
		            'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_D'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_D'),
		exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)
i = i+1
```

### aFOLAT

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i + ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>%
  filter(
    !is.na(outcome),
    !is.na(aSUP_FOL)
  )

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_FOL +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE,include = c('aSUP_FOL'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of folate serum level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_FOL'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(include = c('aSUP_FOL'),remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_FOL'),exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_FOL'),
		exclude = c('aBreastFeed_full_stopped',
                             'aBreastFeed_total_stopped',
                             'aBreastFeed_full_duration'))

### model without  diet groups
mod_ndiet <- rlme(include = c('aSUP_FOL'),
		 exclude = c('GRP'))

### model without supplementation
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_FOL'),
		exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)
i = i+1
```

### aIGF1

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(growth factor) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
## ICC
icc(mod_main)
i = i+1 
```

### aUr_Ca

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
	!is.na(aSUP_Ca))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca + 
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca + 
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE, include = c('aSUP_Ca'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(urinary Ca) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Ca'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca'), exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Ca'),
                exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca'), 
                  exclude = c('GRP'))

### model without other cov.
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Ca'),
                     exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

i <- i+1
```


### aCa_per_Krea

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome),
	!is.na(aSUP_Ca))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    aSUP_Ca +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE, include = c('aSUP_Ca'), remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(uCa:uCreatinie ratio) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme(include = c('aSUP_Ca'))
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(include = c('aSUP_Ca'), remove_random = TRUE)

### model without sex
mod_nsex <- rlme(include = c('aSUP_Ca'), exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(include = c('aSUP_Ca'),
                exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(include = c('aSUP_Ca'), 
                  exclude = c('GRP'))

### model without other cov.
mod_other_cov <- rlme()

### model without log2_age
mod_log2_age <- rlme(include = c('aSUP_Ca'),
                     exclude = c('log2_age'))
```

Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

i <- i+1
```

### aI_per_Krea

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation improved the fit. We will continue to work with log-transformed values.

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

dat_mod$outcome <- log2(dat_mod$outcome) 
column_name <- paste0('log2_', column_name)

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of log2(uIodine:uCreatinine ratio) level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)
### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)

i <- i+1
```

### aP_per_Krea

Data selection and diagnostic plots

```{r, fig.height=5, fig.width=5}

column_name <- names(dat_child_all)[i+ni]

dat_mod <- dat_child_all %>%
  mutate(outcome = !!sym(column_name)) %>% 
  filter(!is.na(outcome))

column_name

gamm <- gam(
  outcome ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Again with log2-transformed outcome

```{r, fig.height=5, fig.width=5}

gamm <- gam(
  log2(outcome) ~ 
    aBreastFeed_full_stopped +
    aBreastFeed_full_duration +
    aBreastFeed_total_stopped + 
    SEX + 
    GRP +
    s(log2_age) +
    s(FAM, bs='re'), 
  data = dat_mod)

summary(gamm)
anova(gamm)
plot(gamm, select = 1)

### Model check
pltmd(gamm)
```

Log-transformation did not improve the fit. We choose is original scale

Fit main model

```{r, fig.height=5, fig.width=5, warning=FALSE}

## main model 
mod_main <- run(
   rlme(main = TRUE, remove_random = FALSE),
  path = paste0('gitignore/run/mod_child_all_', column_name, '_main_mixef'),
  reuse = TRUE)


summary(mod_main)[['coefficients']]


res <- emm(mod_main)

suppl_table <- kbl(res, caption = 
      'Results of linear mixed-effects model of `uP:uCreatinine ratio` level. CI_L and CI_U are bounds of 95% confidence interval') %>% 
  kable_styling('striped',full_width = T) %>% 
  column_spec(1, width_min = '1in')

suppl_table
```

Leave-one-factor mixed models

```{r, fig.height=6, fig.width=6, warning=FALSE}

### main model but non-robust
mod_main <- rlme()
res2 <- emm(mod_main)

### model  without random effect
mod_nonran <- rlme(remove_random = TRUE)

### model without sex
mod_nsex <- rlme(exclude = c('SEX'))

### model without breastfeeding-related predictors
mod_nbf <- rlme(exclude = c('aBreastFeed_full_stopped',
                            'aBreastFeed_total_stopped',
                            'aBreastFeed_full_duration'))

### model without diet groups
mod_ndiet <- rlme(exclude = c('GRP'))

### model without other cov.
mod_other_cov <- NA

### model without log2_age
mod_log2_age <- rlme(exclude = c('log2_age'))
```


Putting key results together

```{r}

## AIC

AIC_child_all <- add_AIC(AIC_child_all, mixef = TRUE)

diet_child_all <- add_eff(diet_child_all, res, mixef = TRUE); diet_child_all_non_robust <- add_eff(diet_child_all_non_robust, res2, mixef = TRUE)
```

### Save tables

```{r}

## Between-diets differences

if(file.exists('gitignore/data/diet_child_all_mixeff.xlsx') == FALSE){
  diet_child_all <- diet_child_all[-1,]
  
  diet_child_all$VN_OM_P_adj <- p.adjust(diet_child_all$VN_OM_P, method = 'fdr')
  diet_child_all$VG_OM_P_adj <- p.adjust(diet_child_all$VG_OM_P, method = 'fdr')
  diet_child_all$VN_VG_P_adj <- p.adjust(diet_child_all$VN_VG_P, method = 'fdr')
  
# for (i in seq(1, nrow(diet_child_all))) {
#   padj <- p.adjust(c(
#     diet_child_all$VN_OM_P[i], 
#     diet_child_all$VG_OM_P[i],
#     diet_child_all$VN_VG_P[i]), 
#     method = 'hochberg')
#   
#   diet_child_all$VN_OM_P_adj[i] <- padj[1]
#   diet_child_all$VG_OM_P_adj[i] <- padj[2]
#   diet_child_all$VN_VG_P_adj[i] <- padj[3]
# }
  
  diet_child_all <- diet_child_all %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) 

  write.xlsx(diet_child_all, 'gitignore/data/diet_child_all_mixeff.xlsx')
}


if(file.exists('gitignore/data/diet_child_all_mixeff_non_robust.xlsx') == FALSE){
  diet_child_all_non_robust <- diet_child_all_non_robust[-1,]
  
  diet_child_all_non_robust$VN_OM_P_adj <- p.adjust(
    diet_child_all_non_robust$VN_OM_P, method = 'fdr')
  
  diet_child_all_non_robust$VG_OM_P_adj <- p.adjust(
    diet_child_all_non_robust$VG_OM_P, method = 'fdr')
  
  diet_child_all_non_robust$VN_VG_P_adj <- p.adjust(
    diet_child_all_non_robust$VN_VG_P, method = 'fdr')
  
# for (i in seq(1, nrow(diet_child_all_non_robust))) {
#   padj <- p.adjust(c(
#     diet_child_all_non_robust$VN_OM_P[i], 
#     diet_child_all_non_robust$VG_OM_P[i],
#     diet_child_all_non_robust$VN_VG_P[i]), 
#     method = 'hochberg')
#   
#   diet_child_all_non_robust$VN_OM_P_adj[i] <- padj[1]
#   diet_child_all_non_robust$VG_OM_P_adj[i] <- padj[2]
#   diet_child_all_non_robust$VN_VG_P_adj[i] <- padj[3]
# }
  
  diet_child_all_non_robust <- diet_child_all_non_robust %>%
    
    select(outcome, estimand, 
         VN_OM_diff, VN_OM_P, VN_OM_P_adj,
         VG_OM_diff, VG_OM_P, VG_OM_P_adj,
         VN_VG_diff, VN_VG_P, VN_VG_P_adj) %>%
    
    mutate(across(.cols = 3:11, .fns = ~as.numeric(as.character(.)))) 

  write.xlsx(diet_child_all_non_robust, 'gitignore/data/diet_child_all_mixeff_non_robust.xlsx')
}

## Importance of predictors

if(file.exists('gitignore/data/AIC_child_all_mixeff.xlsx') == FALSE){
  AIC_child_all <- AIC_child_all[-1,]
  write.xlsx(AIC_child_all, 'gitignore/data/AIC_child_all_mixeff.xlsx')
  }
```



# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
