---
title: "Dietary intake, Nutritional status, and Health outcomes among Vegan, Vegetarian and Omnivore families: results from the observational study"
subtitle: "Statistical report - diet prediction (elastic net)"
format: 
  html:  
    embed-resources: true
    keep-md: false
    toc: true
    toc-expand: 3
    toc-depth: 4
    toc-location: left
    number-sections: true
    number-depth: 4
    code-fold: show
    code-tools: true
    code-summary: "Open code"
    grid: 
      body-width: 1000px
      sidebar-width: 600px
      margin-width: 100px
editor: source
theme: darkly
highlight-style: github-dark
fontsize: 12 px
code-block-bg: "#2D2D31"
bibliography: ../references.bib
fontcolor: '#C4C4C4'
monobackgroundcolor: "#3B3B3B"
---

------------------------------------------------------------------------

```{r setup, echo=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
knitr::opts_knit$set(root.dir = "/home/ticf/GitRepo/ticf/368_MOCA_kompas_clinical")
```

```{css, echo=FALSE}
code.sourceCode {
  font-size: 0.86em;
  border: 1px solid #ffffff; 
  padding: 9px; 
}

code{
    color: #EEE8AA; 
    background: #96464D
}

.equation {
  text-align: center;
  display: block;
  margin: auto;
}

body {
  text-align: justify;
}
```

{{< include ../README.md >}}

```{r}
# Import initiation file
source('r/368_initiation.R')
```

# Data wrangling

## All children

```{r}
skimr::skim(dat_child_all)
```


### Wrangle data

```{r}

for (i in 1:ncol(dat_child_all)) {
  names(dat_child_all)[i] <- str_replace_all(
    names(dat_child_all)[i], c("^a" = "")
  )
}

dat_child_all <- dat_child_all %>%
  rename(
    FOLATE = FOLAT,
    TIBC = VKFE,
    HOLOTC = VIT_AKTB12,
    CTX = Cros,
    uCCR = Ca_per_Krea,
    uICR = I_per_Krea,
    uPCR = P_per_Krea,
    uCa = Ur_Ca
    ) %>% 
  mutate(
    log2_TG = log2(TG),
    log2_Se = log2(Se),
    log2_Zn = log2(Zn),
    log2_FERR = log2(FERR),
    log2_TRFINDEX = log2(TRFINDEX),
    log2_STRF = log2(STRF),
    log2_CTX = log2(CTX),
    log2_UI = log2(UI),
    log2_CREA = log2(CREA),
    log2_HOLOTC = log2(HOLOTC),
    log2_HCY = log2(HCY),
    log2_MMA = log2(MMA),
    log2_VIT_D = log2(VIT_D),
    log2_IGF1 = log2(IGF1),
    log2_uCa = log2(uCa),
    log2_uCCR = log2(uCCR),
    log2_uICR = log2(uICR)
    ) %>% 
  mutate(
    male = if_else(SEX == "M", 1, 0),
    GRP = factor(GRP),
    FAM = factor(FAM)
  ) %>%
  select(
    
    ## remove irrelevant variables not included to any inference and prediction
    -c(SEX, BreastFeed_full, BreastFeed_total, ID, dev_delay, BREAKS, AGE),
    
    ## remove information about supplementation
    -c(SUP_VEG1:SUP_OTH),
    
    ## remove non-log2-transformed version when log2(variable) is included
    -c(TG, Se, Zn, FERR, TRFINDEX,
       STRF, CTX, UI, CREA, HOLOTC, HCY,
       MMA, VIT_D, IGF1, uCa, uCCR, uICR
       )
    ) %>% 
  select(FAM, GRP, log2_age, male, BiW, 
         BreastFeed_full_duration, BreastFeed_full_stopped, BreastFeed_total_stopped,
         everything()
         )
```


### Missing values and standardization

```{r}
skimr::skim(dat_child_all)
```

Removing features with over 25% NA values: all variables are below this threshold, no will be excluded

#### Multiple imputation

Prepare

```{r}

dat_child_all_toimp <- dat_child_all %>% select(-FAM)

init <- mice(dat_child_all_toimp, maxit = 0)
init$method

data_imputed <- run(
  expr = mice(
    dat_child_all_toimp,
    method = init$method,
    m = 1
  ),
  path = "gitignore/run/data_child_all_imputed"
)

dat_child_all_imputed <- data.frame(
  FAM = dat_child_all$FAM,
  complete(data_imputed, 'all')[1]$`1`
  )

```

#### Rescaling

```{r}

dat_child_all_imputed <- dat_child_all_imputed %>%
  mutate(
    across(
      where(~ is.numeric(.) && length(unique(.)) > 2),
      arm::rescale
    )
  )

summary(dat_child_all_imputed)
```


## Adults

### Wrangle data

```{r}

for (i in 1:ncol(dat_adult)) {
  names(dat_adult)[i] <- str_replace_all(
    names(dat_adult)[i], c("^a" = "")
  )
}


dat_adult <- dat_adult %>%
  rename(
    FOLATE = FOLAT,
    TIBC = VKFE,
    HOLOTC = VIT_AKTB12,
    CTX = Cros,
    uCCR = Ca_per_Krea,
    uICR = I_per_Krea,
    uPCR = P_per_Krea,
    uCa = Ur_Ca
  ) %>%
  mutate(
    log2_FAT = log2(FAT),
    log2_FFM = log2(FFM),
    log2_TC = log2(TC),
    log2_TG = log2(TG),
    log2_Se = log2(Se),
    log2_Zn = log2(Zn),
    log2_TIBC = log2(TIBC),
    log2_FERR = log2(FERR),
    log2_TRF = log2(TRF),
    log2_TRFINDEX = log2(TRFINDEX),
    log2_STRF = log2(STRF),
    log2_CTX = log2(CTX),
    log2_P1NP = log2(P1NP),
    log2_UI = log2(UI),
    log2_UREA = log2(UREA),
    log2_CREA = log2(CREA),
    log2_HOLOTC = log2(HOLOTC),
    log2_HCY = log2(HCY),
    log2_MMA = log2(MMA),
    log2_VIT_D = log2(VIT_D),
    log2_uCa = log2(uCa),
    log2_uCCR = log2(uCCR),
    log2_uICR = log2(uICR)
  ) %>%
  mutate(
    male = if_else(SEX == "M", 1, 0),
    GRP = factor(GRP),
    FAM = factor(FAM)
  ) %>%
  select(

    ## remove irrelevant variables not included to any inference and prediction
    -c(SEX, ID),

    ## remove information about supplementation
    -c(SUP_VEG1:SUP_OTH),

    ## remove non-log2-transformed version when log2(variable) is included
    -c(
      FAT, FFM, TC, TG, Se, Zn, TIBC, FERR, TRF, TRFINDEX, STRF, 
      CTX, P1NP, UI, UREA, CREA, HOLOTC, HCY, MMA, VIT_D, 
      uCa, uCCR, uICR
    )
  ) %>%
  select(
    FAM, GRP, AGE, male,
    everything()
  )

summary(dat_adult)
```


### Missing vlaues and stadardization

```{r}
skimr::skim(dat_adult)
```

All features has over 3/4 of non-missing values

#### Multiple imputation

Prepare

```{r}

dat_adult_toimp <- dat_adult %>% select(-FAM)

init <- mice(dat_adult_toimp, maxit = 0)
init$method

data_imputed <- run(
  expr = mice(
    dat_adult_toimp,
    method = init$method,
    m = 1
  ),
  path = "gitignore/run/data_adult_imputed"
)

dat_adult_imputed <- data.frame(
  FAM = dat_adult$FAM,
  complete(data_imputed, 'all')[1]$`1`
  )
```

#### Rescaling

```{r}

dat_adult_imputed <- dat_adult_imputed %>%
  mutate(
    across(
      where(~ is.numeric(.) && length(unique(.)) > 2),
      arm::rescale
    )
  )

summary(dat_adult_imputed)
```


# Diet prediction

(OM, VN, VG determination)

All prediction models will account for the variable `FAM` as the grouping (block) variable, ensuring that all subject of a single family will be part of the same fold during each bootstrap iteration. 


## All children

### Baseline model

Following models will be trained to discriminate between two diets, based solely on `log2_age`, `male`, `BreastFeed_total_stopped`, `BreastFeed_full_stopped` and interaction `BreastFeed_full_duration`.


#### Prepare data

```{r}
dat_pred <- dat_child_all_imputed %>% 
  select(GRP, FAM, log2_age, male, BreastFeed_full_duration,  
         BreastFeed_full_stopped, BreastFeed_total_stopped, BiW) 

nfam <- dat_pred$FAM %>% factor() %>% levels() %>% length()

dat_features <- dat_pred %>% select(-FAM, -GRP) %>% as.matrix
colnames(dat_features)

dat_outcome <- dat_pred %>% select(GRP) %>% as.matrix
```

#### VN vs OM

```{r, warning=FALSE}
## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_all_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_all_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_child_all_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Complete model

Baseline + clinical characteristics 

#### Prepare data

```{r}

dat_pred <- dat_child_all_imputed %>% 
  select(GRP, FAM, log2_age, male, BreastFeed_full_duration,  
         BreastFeed_full_stopped, BreastFeed_total_stopped, 
         BiW,
         MASS_Perc:log2_uICR)

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_all_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_all_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_child_all_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Reduced 

Baseline + clinical characteristics not affected with vitamins supplementation

#### Prepare data

```{r}

dat_pred <- dat_child_all_imputed %>% 
  select(GRP, FAM, log2_age, male, BreastFeed_full_duration,  
         BreastFeed_full_stopped, BreastFeed_total_stopped, 
         BiW,
         MASS_Perc:Mg, 
         log2_TG:log2_Zn,
         HGB:UA,
         log2_CTX, log2_CREA, log2_IGF1
         )

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_all_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_all_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_child_all_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

## Adults

### Baseline model

Following models will be trained to discriminate between two diets, based solely on `AGE` and `SEX`. 


#### Prepare data

```{r}
dat_pred <- dat_adult_imputed %>% 
  select(GRP, FAM, AGE, male) 

nfam <- dat_pred$FAM %>% factor() %>% levels() %>% length()

dat_features <- dat_pred %>% select(-FAM, -GRP) %>% as.matrix
colnames(dat_features)

dat_outcome <- dat_pred %>% select(GRP) %>% as.matrix
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_adult_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_adult_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_baseline_adult_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Complete model

Baseline + clinical characteristics

#### Prepare data

```{r}

dat_pred <- dat_adult_imputed 

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_adult_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_adult_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)


mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complet_adult_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

### Reduced model

Baseline + clinical characteristics not affected with vitamin supplementation

#### Prepare data

```{r}

dat_pred <- dat_adult_imputed %>% 
  select(GRP, FAM, AGE, male,   
         BMI:Mg, 
         HGB:UA,
         AL_adult:log2_Zn,
         log2_CTX, log2_P1NP, 
         log2_UREA:log2_CREA
         )

dat_features <- dat_pred %>% select(-FAM, -GRP)  %>% as.matrix
colnames(dat_features)
```

#### VN vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VG') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_adult_VN_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VG vs OM

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'VN') %>% 
  mutate(outcome = if_else(GRP == 'VG', 1, 0)) %>% 
  select(-GRP)

mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_adult_VG_OM'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

#### VN vs VG

```{r, warning=FALSE}

## Prepare working data
dat_pred_temp <- dat_pred %>% 
  filter(GRP != 'OM') %>% 
  mutate(outcome = if_else(GRP == 'VN', 1, 0)) %>% 
  select(-GRP)


mean(dat_pred_temp$outcome)

## Fit and validate model
modelac <- 'pred_complex_adult_VN_VG'

assign(modelac, run(
  clustered_glmnet(
    data = dat_pred_temp,
    outcome = 'outcome',
    clust_id = 'FAM', 
    sample_method = 'atypboot',
    N = 500,
    alphas = seq(0, 1, by = 0.2),
    seed = 368),
  path = paste0('gitignore/run/', modelac), 
  reuse = TRUE))
    
## Calibration curve         
#get(modelac)$plot
             
## Model summary
t(get(modelac)$model_summary)
get(modelac)$valid_performances %>% summary

## Model coefficients
get(modelac)$betas
```

## Results summaries
### Prepare data 

```{r}
models_names <- c(
  "pred_baseline_child_all_VN_OM",
  "pred_baseline_child_all_VG_OM",
  "pred_baseline_child_all_VN_VG",
  "pred_complex_child_all_VN_OM",
  "pred_complex_child_all_VG_OM",
  "pred_complex_child_all_VN_VG",
  "pred_complet_child_all_VN_OM",
  "pred_complet_child_all_VG_OM",
  "pred_complet_child_all_VN_VG",
  "pred_baseline_adult_VN_OM",
  "pred_baseline_adult_VG_OM",
  "pred_baseline_adult_VN_VG",
  "pred_complex_adult_VN_OM",
  "pred_complex_adult_VG_OM",
  "pred_complex_adult_VN_VG",
  "pred_complet_adult_VN_OM",
  "pred_complet_adult_VG_OM",
  "pred_complet_adult_VN_VG"
)

tr <- get(models_names[1])$model_summary[
  c(
    "auc_optimism_corrected",
    "auc_optimism_corrected_CIL",
    "auc_optimism_corrected_CIU"
  )
]

for (i in 2:length(models_names)) {
  tr <- dplyr::bind_rows(tr, get(models_names[i])$model_summary[
    c(
      "auc_optimism_corrected",
      "auc_optimism_corrected_CIL",
      "auc_optimism_corrected_CIU"
    )
  ])
}

tr <- data.frame(models_names,
  y_pos = c(
    rep(0.9, 3),
    rep(0.8, 3),
    rep(0.7, 3),
    rep(0.5, 3),
    rep(0.4, 3),
    rep(0.3, 3)
  ),
  age_group = c(
    rep("children", 9),
    rep("adults", 9)
  ),
  contrast = str_sub(models_names, -5, -1),
  model = str_sub(models_names, 6, 12),
  tr
) %>%
  mutate(
    model = fct_recode(model,
      "baseline" = "baselin",
      "reduced" = "complex",
      "full" = "complet"
    )
  ) %>% 
  rename(
    AUC = auc_optimism_corrected,
    CI_L = auc_optimism_corrected_CIL,
    CI_U = auc_optimism_corrected_CIU
  ) %>% 
  select(
    age_group, model, contrast, AUC, CI_L, CI_U, models_names, y_pos
  )
```

### Models performance summary

```{r}
tr %>%
  mutate(`AUC [95% CI]` = paste0(
    round(AUC, 2),
    " [",
    round(CI_L, 2),
    ", ",
    round(CI_U, 2),
    "]"
  )) %>%
  select(age_group:contrast, `AUC [95% CI]`) %>%
  kableExtra::kable(caption = "Results of elastic net predictive models distinguishing between diet groups. `age_group` indicates the cohort (children or adults). `model` specifies the covariates included: `baseline` includes only basic patient characteristics (age, sex, breastfeeding-related covariates and birth weight for children); `reduced` adds clinical characteristics not primarily driven by supplementation; `full` includes all clinical characteristics. `contrast` denotes the pair of diet groups used for model training: `VN_OM` (vegans vs. omnivores), `VG_VN` (vegetarians vs. vegans), and `OM_VG` (omnivores vs. vegetarians). `AUC [95% CI]` represents the out-of-sample AUC estimated via clustered bootstrap, with corresponding 95% confidence intervals.")
```


### Comparison of baseline vs more complex models

```{r}

baseline <- tr %>% filter(model == "baseline")
full <- tr %>% filter(model == "full")
reduced <- tr %>% filter(model == "reduced")

compmod <- compare_predmod(
  get(baseline$models_names[1]),
  get(reduced$models_names[1])
)

comp_table <- data.frame(
  age_group = baseline$age_group[1],
  contrast = baseline$contrast[1],
  auc_gain = compmod[1],
  CI_L = compmod[2],
  CI_U = compmod[3],
  P = compmod[4],
  models = interaction(baseline$model[1], reduced$model[1])
)

for (i in 2:nrow(baseline)) {
  compmod <- compare_predmod(
    get(baseline$models_names[i]),
    get(reduced$models_names[i])
  )

  comp_table_tmp <- data.frame(
    age_group = baseline$age_group[i],
    contrast = baseline$contrast[i],
    auc_gain = compmod[1],
    CI_L = compmod[2],
    CI_U = compmod[3],
    P = compmod[4],
    models = interaction(baseline$model[i], reduced$model[i])
  )

  comp_table <- dplyr::bind_rows(comp_table, comp_table_tmp)

  i <- i + 1
}

comp_table


dim1 <- nrow(comp_table)

for (i in (dim1 + 1):(dim1 + nrow(baseline))) {
  compmod <- compare_predmod(
    get(baseline$models_names[i - dim1]),
    get(full$models_names[i - dim1])
  )

  comp_table_tmp <- data.frame(
    age_group = baseline$age_group[i - dim1],
    contrast = baseline$contrast[i - dim1],
    auc_gain = compmod[1],
    CI_L = compmod[2],
    CI_U = compmod[3],
    P = compmod[4],
    models = interaction(baseline$model[i - dim1], full$model[i - dim1])
  )

  comp_table <- dplyr::bind_rows(comp_table, comp_table_tmp)
}

comp_table %>%
  mutate(
    `AUC gain [95% CI]` = paste0(
      round(auc_gain, 2), " [", round(CI_L, 2), ", ", round(CI_U, 2), "]"
    ),
    models = fct_recode(models,
      "reduced vs baseline" = "baseline.reduced",
      "full vs baseline" = "baseline.full"
    )
  ) %>%
  select(
    models, age_group, contrast, `AUC gain [95% CI]`, P
  ) %>%
  kableExtra::kable(
  caption = "Comparison of elastic net predictive models evaluating the gain in discriminative performance when including additional clinical characteristics. The `models` column compares either `reduced vs baseline` (adding clinical characteristics not primarily driven by supplementation) or `full vs baseline` (adding all clinical characteristics). `age_group` indicates the cohort (children or adults). `contrast` specifies the diet groups used for model training: `VN_OM` (vegans vs. omnivores), `VG_OM` (vegetarians vs. omnivores), and `VN_VG` (vegans vs. vegetarians). `AUC gain [95% CI]` represents the estimated improvement in out-of-sample AUC with a more complex model, with clustered bootstrap providing corresponding 95% confidence intervals. `P` indicates the p-value assessing the statistical significance of the AUC gain."
)
```


### Visualize

```{r, fig.width=6, fig.height=5}
#| fig.cap: 'Results of elastic net predictive models distinguishing between diet groups, shown separately for adults (top) and children (bottom). Comparisons include vegans vs. omnivores (`VN vs OM`, left), vegetarians vs. omnivores (`VG vs OM`, middle), and vegans vs. vegetarians (`VN vs VG`, right). Models include `baseline` (only basic patient characteristics: age, sex, breastfeeding-related covariates and birth weight for children), `reduced` (adding clinical characteristics not primarily driven by supplementation), and `full` (including all clinical characteristics). Points represent out-of-sample AUC estimates, indicating the ability of models to discriminate between diet groups, with lines showing 95% confidence intervals estimated via clustered bootstrap.'

p1 <- tr %>%
  mutate(
    contrast = factor(contrast, levels = c("VN_OM", "VG_OM", "VN_VG")),
    model = factor(model, levels = c("baseline", "reduced", "full"))
  ) %>%
  ggplot(aes(x = AUC, y = model, color = model)) +
  geom_point(size = 5, shape = 18) +
  geom_segment(
    aes(
      x = CI_L, xend = CI_U,
      y = model, yend = model
    ),
    linewidth = 1.1
  ) +
  coord_cartesian(xlim = c(0.1, 1)) +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  facet_wrap(~ age_group + contrast,
    labeller = labeller(
      contrast = c(
        "VN_OM" = "VN vs OM",
        "VG_OM" = "VG vs OM",
        "VN_VG" = "VN vs VG"
      )
    )
  ) +
  theme(
    axis.title.y = element_blank(),
    legend.position = "bottom"
  ) +
  labs(
    x = "Out-of-sample AUC",
    color = "Model"
  ) +
  scale_color_manual(values = c(
    "baseline" = "grey50",
    "full" = "red",
    "reduced" = "purple"
  ))

p1

```



# Reproducibility

```{r, collapse=TRUE}
sessionInfo()
```
